## [DRAFT] Carpentries Pre- and Post-Workshop Assessment Results
June 2018

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(srvyr)
library(beeswarm)
library(NPS)
library(broom)
library(assertr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
opts_chunk$set(fig.path='figures/') #puts all figures in figures folder
```

```{r}
# Function that makes a table of counts and percentages
tally_and_perc <- function(df, colname, na.rm = FALSE){
  quo_colname <- enquo(colname)

  df %>% 
    group_by(!!quo_colname) %>% 
    tally() %>% 
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>% 
    mutate(`%` = round(n / sum(n) * 100, 1)) 
}
```

The Carpentries Assessment Team releases short and long-term assessment results twice per year in June and January. The following results include analyses from both Data Carpentry and Software Carpentry's pre- and post-workshop surveys.

### Data Carpentry

```{r}
# Load DC pre and post-workshop data
# Data Carpentry Pre-Workshop Data
dcpredata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/180118_dcpre.csv")

# Data Carpentry Post-Workshop Data
dcpostdata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/180108_dcpost.csv")
```

# Pre-Workshop Survey Demographics: Workshop Location

Data Carpentry learners are asked what country their workshop is held.

```{r}
# Tally Data Carpentry's pre-workshop respondents by Country
dcpredata_country_tally <-
dcpredata %>%
  group_by(Country) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(Country)) %>%
  arrange(desc(n))
```

```{r dc_respondents_by_country}
# Plot Data Carpentry's respondents by Country
ggplot(dcpredata_country_tally,
       aes(reorder(Country, perc),
           perc)) +
  geom_bar(stat = "identity", fill = "maroon") +
  theme_classic() +
  xlab("") +
  ylab("Percentage of Respondents") +
  coord_flip() +
  ggtitle("Breakdown of Data Carpentry's Survey \nRespondents by Country") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw(base_size = 14)
#kable(data_country_tally, format='markdown')
```

# Pre-Workshop Survey Demographics: Domain of Research/Work/Study

```{r}
# Tally Data Carpentry's pre-workshop respondents by Discipline
# Responses are in columns 'Discipline' through 'Column13'
dcdiscipline <-
 dcpredata %>%
 select(Discipline:Column13) %>%
 gather(col, dcdiscipline) %>%
 group_by(dcdiscipline) %>%
 tally_and_perc(dcdiscipline, na.rm = TRUE) %>%
 filter(!is.na(dcdiscipline)) %>%
 arrange(desc(n)) %>%
 rename(`Discipline` = dcdiscipline)

kable(dcdiscipline, format = 'markdown', row.names = NA, col.names = c ("Data Carpentry's Respondents by Discipline", "n", "%"))
```

# Pre-Workshop Survey Demographics: Respondents Position

```{r }
# Data Carpentry Respondents by Status
# Responses are in columns 'Status' through 'Column22'
ordered_status = c("Undergraduate Student", "Graduate Student", "Postdoctoral Researcher", "Faculty", "Industry Employee", "Government Employee", "Research Staff", "Management/Administrator", "Retired/Not Employed", "Other (please specify)")

dcpredata_status_tally <-
 dcpredata %>%
 select(`Status`:Column22) %>%
 gather(col, dcpredata_status_tally) %>%
 group_by(dcpredata_status_tally) %>%
 tally_and_perc(dcpredata_status_tally) %>%
 filter(!is.na(dcpredata_status_tally)) %>%
 arrange(desc(n)) %>%
 rename(`Status` = dcpredata_status_tally)

kable(dcpredata_status_tally, format = 'markdown', row.names = NA, col.names = c ("Data Carpentry's Respondents by Position", "n", "%"))
```

```{r dc_learners_status}
# This plot is not working

dcpredata_status_tally <- 
dcpredata %>% 
  mutate(Status_ord = fct_relevel(Status, 
                                  ordered_status)) %>% 
  tally_and_perc(Status_ord, na.rm = TRUE)

ggplot(dcpredata_status_tally, 
       aes(Status_ord,
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill = "darkcyan") +
  geom_text(aes(label = n), 
            size= 4,
            nudge_y = 3) + ## This moves the numbers up a bit so they're easier to read. 
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("Position") +
  ylab("% Respondents") +
  ggtitle("Data Carpentry Respondents by Position") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14) 
```

# Pre-Workshop Survey Questions: Operating System 

Learners are asked what operating system is on the computer they are bringing to the workshop.

```{r}
# Operating System
OS <- 
dcpredata %>%
  select(OS) %>% 
  gather(col, 
         OS) %>% 
  tally_and_perc(OS, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Operating System` = OS)

# Table
kable(OS)

```
## Programming Usage

How often do you currently use any of the following?

```{r}
Programming <- 
dcpredata %>%
  select(`CurrentProgramming`) %>% 
  gather(col, 
         Programming) %>% 
  tally_and_perc(Programming, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Current Programming Usage` = Programming)

# Table
kable(Programming)
```

## Satisfaction

```{r}
# Please rate your level of satisfaction with your current data management and analysis workflow.

levels = c("Very unsatisfied", "Unsatisfied", "Neutral", "Satisfied", "Very satisfied", "Not sure", "Not applicable")

Satisfaction <- 
dcpredata %>%
  select(`CurrentSatisfaction`) %>% 
  gather(col, 
         Satisfaction) %>% 
  tally_and_perc(Satisfaction, 
                 na.rm = TRUE) %>% 
  rename(`CurrentSatisfaction` = Satisfaction)

kable(Satisfaction, format = 'markdown', row.names = NA, col.names = c ("Satisfaction with current data management practices", "n", "%"))

# I want these to show in Likert order, not alpha-order
```

## Why Are You Attending

Why are you attending this workshop?

```{r}
# Responses are in columns 'WhyAttending' through 'Column29'

WhyAttending <- 
dcpredata %>%
  select(`WhyAttending`:`Column29`) %>% 
  gather(col, 
         WhyAttending) %>% 
  tally_and_perc(WhyAttending, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Why are you attending? Check all that apply.` = WhyAttending)

kable(WhyAttending, format = 'markdown', row.names = NA, col.names = c ("Why are you attending this workshop?", "n", "%"))
```

## Workshop Exposure

How did you find out about this workshop?

```{r}
# Responses are in columns 'Exposure-Workshop' through 'Column31'

Exposure <- 
dcpredata %>%
  select(`Exposure`:`Column35`) %>% 
  gather(col, 
         Exposure) %>% 
  tally_and_perc(Exposure, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Exposure` = Exposure)

kable(Exposure, format = 'markdown', row.names = NA, col.names = c ("How did you find out about this workshop?", "n", "%"))
```

## Programming Language Covered

Which programming language is being covered?

```{r}
ProgrammingLanguage <- 
dcpredata %>%
  select(`ProgrammingLanguageCovered`) %>% 
  gather(col, 
         ProgrammingLanguage) %>% 
  tally_and_perc(ProgrammingLanguage, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Which language is being covered?` = ProgrammingLanguage)

kable(ProgrammingLanguage, format = 'markdown', row.names = NA, col.names = c ("Which language is being covered?", "n", "%"))
```

## Pre/Post Comparison

Learners were asked to rate their level of agreement with the following statements related to Data Carpentry's workshop goals and learning objectives. The figure below provides a visual representation of their responses, comparing them before the workshop and after the workshop. Axis labels and the corresponding question are as follows:  

+ __AnalysesEasier__: Using a programming language (like R or Python) can make my analyses easier to reproduce. 
+ __OvercomeProblem__: While working on a programming project, if I get stuck, I can find ways of overcoming the problem. 
+ __ProgrammingSoftware__: I am confident in my ability to make use of programming software to work with data.
+ __RawData__: Having access to the original, raw data is important to be able to repeat an analysis.
+ __SearchOnline__: I know how to search for answers to my technical questions online.
+ __WriteScript__: I can write a small program/script/macro to solve a problem in my own work.  

```{r}
# Ability to perform various computing tasks before and after completing the workshop
impact_pre <-
    c("Strongly disagree",
    "Disagree",
    "Neutral",
    "Agree",
    "Strongly agree")

impact_post <- 
  c("Strongly disagree",
    "Disagree",
    "Neutral",
    "Agree",
    "Strongly agree")

# How do I tell R that I want the factors in this order always?
```


```{r}
# Pre-Workshop
# Compute for all tools.

# Before the workshop
pre_computing <- 
dcpredata %>%
  select(`RawData`:`AnalysesEasier`) %>% 
  gather() %>% 
  filter(value %in% impact_pre) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value))) %>% 
  unnest(tallies)
#kable(pre_computing, format = 'markdown', row.names = NA, col.names = c ("Statement", "Level of Agreement", "n", "%"))
```


```{r}
# Post-Workshop
post_computing <- 
dcpostdata %>%
  select(`RawData`:`AnalysesEasier`) %>% 
  gather() %>% 
  filter(value %in% impact_post) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value)))  %>% 
  unnest(tallies) 
#kable(post_computing, format = 'markdown', row.names = NA, col.names = c ("Statement", "Level of Agreement", "n", "%"))
```

```{r}
# Plot before a grouped bar plot, then combine.

computing_before <- 
   ggplot(pre_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             impact_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Respondent Ability Pre-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 10) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) 
```

```{r}
# Plot after a grouped bar plot, then combine.
computing_after <- 
   ggplot(post_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (impact_post))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Confidence Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 10) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())  
# + guides(fill = guide_legend(nrow = 2)) # wraps legend
```          

```{r change_in_confidence} 
# Put the two plots together
library(gridExtra)
grid.arrange(computing_before, 
             computing_after,
             ncol = 1)

# Why are the levels showing in a different order on the grid?
```

```{r agreement_pre}
   ggplot(pre_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             impact_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Agreement Pre-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
```

```{r agreement_post}
ggplot(post_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (impact_post))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Agreement Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
# Why does strongly agree appear first in this plot but last in the plot above?
```

## Paired Analyses Table
```{r}

prep_paired_data <- . %>%
    select(UniqueID, `RawData`:`AnalysesEasier`) %>%
    filter(!is.na(UniqueID)) %>%
    gather(skill, feeling, -UniqueID) %>%
    mutate(feeling_score = case_when(
               feeling == "Strongly disagree" ~ 1,
               feeling == "Disagree"          ~ 2,
               feeling == "Neutral"           ~ 3,
               feeling == "Agree"             ~ 4, 
               feeling == "Strongly agree"    ~ 5,
               is.na(feeling)                 ~ NA_real_, 
               TRUE                           ~ 999
           )) %>%
    assert(in_set(NA, 1, 2, 3, 4, 5), feeling_score)


pre_paired <- dcpredata %>%
    prep_paired_data %>%
    rename_at(vars(-UniqueID, -skill), ~ paste0("pre_", .))
    
post_paired <- dcpostdata %>%
    prep_paired_data %>%
    rename_at(vars(-UniqueID, -skill), ~ paste0("post_", .))

paired_data <- inner_join(pre_paired, post_paired, by = c("UniqueID", "skill"))


t_test_results <- paired_data %>%
    group_by(skill) %>%
    nest() %>% 
    mutate(t_test_res = purrr::map(data, function(x) {
        t.test(x$pre_feeling_score, x$post_feeling_score, paired = TRUE,
               alt = "less") %>%
            broom::tidy()
    })) %>%
    unnest(t_test_res)

t_test <- paired_data %>%
    group_by(skill) %>%
    summarize(
        mean_pre_feeling = mean(pre_feeling_score, na.rm = TRUE),
        n_pre = sum(!is.na(pre_feeling_score)),
        sd_pre_feeling = sd(pre_feeling_score, na.rm = TRUE),
        mean_post_feeling = mean(post_feeling_score, na.rm = TRUE),
        n_post = sum(!is.na(post_feeling_score)),
        sd_post_feeling = sd(post_feeling_score, na.rm = TRUE)
    ) %>%
    left_join(t_test_results, by = "skill")

kable(select(t_test, skill, ends_with("feeling"), starts_with("n"), 
             p.value))
 
```

# Demographic Data for U.S. Participants

With what gender do you most identify?

```{r}
gender = c("Female", "Male", "I prefer not to say")
gender = factor(gender)

round2data$Gender = factor(round2data$Gender, levels = gender)

round2data_gender_tally <-
  round2data %>%
  group_by(Gender) %>%
  tally() %>%
  filter(!is.na(Gender)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(round2data_gender_tally)
```

# Recommending Data Carpentry Workshops
Learners were asked how likely they are to recommend this workshop to a friend or colleague using the [Net Promoter Score](https://en.wikipedia.org/wiki/Net_Promoter). The scoring for this question based on a 0 to 100 scale. Respondents scoring from 0 to 64 are labeled *Detractors*, and are believed to be less likely to recommend a workshop. Those who respond with a score of 85 to 100 are called *Promoters*, and are considered likely to recommend a workshop. Respondents between 65 and 84 are labeled *Passives*, and their behavior falls in the middle of Promoters and Detractors. 

```{r}
postdata$`LikelyToRecommend` %>%
    npc(breaks = list(0:64, 65:84, 85:100)) %>%
    data.frame(category = .) %>%
    filter(!is.na(category)) %>%
    count(category) %>%
    mutate("%" = (n / sum(n))*100) %>%
    kable(, format = 'markdown', row.names = NA, col.names = c ("Promoter Score", "n", "%"))
```








### Software Carpentry

```{r}
# Load SWC pre and post-workshop data
# Software Carpentry Pre-Workshop Data
swcpredata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/171231_swcpre.csv")

# Software Carpentry Post-Workshop Data
swcpostdata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/171231_swcpost.csv")
```

# Pre-Workshop Survey Demographics: Workshop Location
In Software Carpentry's pre-workshop survey, respondents are asked whether or not their workshop takes place in the United States.

```{r}
# Tally Software Carpentry's pre-workshop respondents by Country
swcpredata_country_tally <-
swcpredata %>%
  group_by(USWorkshop) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(USWorkshop)) %>%
  arrange(desc(n))
kable(swcpredata_country_tally, format='markdown', col.names = c("SWC Workshops in US", "n", "%"))
```

# Pre-Workshop Survey Demographics: Domain of Research/Work/Study

```{r}
# Tally Software Carpentry's pre-workshop respondents by Discipline
# Responses are in columns 'Domain' through 'Column61'
swcdiscipline <-
 swcpredata %>%
 select(Domain:Column61) %>%
 gather(col, swcdiscipline) %>%
 group_by(swcdiscipline) %>%
 tally_and_perc(swcdiscipline,na.rm = TRUE) %>%
 filter(!is.na(swcdiscipline)) %>%
 arrange(desc(n)) %>%
 rename(`Domain` = swcdiscipline)

kable(swcdiscipline, format = 'markdown', row.names = NA, col.names = c ("Software Carpentry's Respondents by Discipline", "n", "%"))
```




```{r }
# Software Carpentry Respondents by Position
ordered_status <- c(    
    "Undergraduate Student",
    "Graduate Student",
    "Post-doctoral researcher",
    "Faculty",
    "Research staff (including research programmer)",
    "Support staff (including technical support)",
    "Librarian/archivist",
    "Commercial software developer",
    "Other (please specify)"
  )

swcpredata_status_tally <- 
swcpredata %>% 
  mutate(Status_ord = fct_relevel(Status, 
                                  ordered_status)) %>% 
  tally_and_perc(Status_ord, na.rm = TRUE) 
```

```{r swc_learners_status}
ggplot(swcpredata_status_tally, 
       aes(Status_ord,
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill = "darkcyan") +
  geom_text(aes(label = n), 
            size= 4,
            nudge_y = 3) + ## This moves the numbers up a bit so they're easier to read. 
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("Status") +
  ylab("% Respondents") +
  ggtitle("Software Carpentry Respondents by Position") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14) 
```