## [DRAFT] Carpentries Pre- and Post-Workshop Assessment Results
June 2018

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(srvyr)
library(beeswarm)
library(NPS)
library(broom)
library(assertr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
opts_chunk$set(fig.path='figures/') #puts all figures in figures folder
```

```{r}
# Function that makes a table of counts and percentages
tally_and_perc <- function(df, colname, na.rm = FALSE){
  quo_colname <- enquo(colname)

  df %>% 
    group_by(!!quo_colname) %>% 
    tally() %>% 
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>% 
    mutate(`%` = round(n / sum(n) * 100, 1)) 
}
```

The Carpentries Assessment Team releases short and long-term assessment results twice per year in June and January. The following results include analyses from both Data Carpentry and Software Carpentry's pre- and post-workshop surveys.

### Data Carpentry (Pre-Workshop)

```{r}
# Load DC pre and post-workshop data
# Data Carpentry Pre-Workshop Data
dcpredata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/180118_dcpre.csv")

# Data Carpentry Post-Workshop Data
dcpostdata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/180108_dcpost.csv")
```

# Demographics: Workshop Location

Data Carpentry learners are asked what country their workshop is held.

```{r}
# Tally Data Carpentry's pre-workshop respondents by Country
dcpredata_country_tally <-
dcpredata %>%
  group_by(Country) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(Country)) %>%
  arrange(desc(n))
```

```{r dc_respondents_by_country}
# Plot Data Carpentry's respondents by Country
ggplot(dcpredata_country_tally,
       aes(reorder(Country, perc),
           perc)) +
  geom_bar(stat = "identity", fill = "maroon") +
  theme_classic() +
  xlab("") +
  ylab("Percentage of Respondents") +
  coord_flip() +
  ggtitle("Breakdown of Data Carpentry's Survey \nRespondents by Country") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw(base_size = 14)
#kable(data_country_tally, format='markdown')
```

# Demographics: Domain of Research/Work/Study

```{r}
# Tally Data Carpentry's pre-workshop respondents by Discipline
# Responses are in columns 'Discipline' through 'Column13'
dcdiscipline <-
 dcpredata %>%
 select(Discipline:Column13) %>%
 gather(col, dcdiscipline) %>%
 group_by(dcdiscipline) %>%
 tally_and_perc(dcdiscipline, na.rm = TRUE) %>%
 filter(!is.na(dcdiscipline)) %>%
 arrange(desc(n)) %>%
 rename(`Discipline` = dcdiscipline)

kable(dcdiscipline, format = 'markdown', row.names = NA, col.names = c ("Data Carpentry's Respondents by Discipline", "n", "%"))
```

# Demographics: Respondents' Position

```{r }
# Data Carpentry Respondents by Status
# Responses are in columns 'Status' through 'Column22'
ordered_status = c("Undergraduate Student", "Graduate Student", "Postdoctoral Researcher", "Faculty", "Industry Employee", "Government Employee", "Research Staff", "Management/Administrator", "Retired/Not Employed", "Other (please specify)")

dcpredata_status_tally <-
 dcpredata %>%
 select(`Status`:Column22) %>%
 gather(col, dcpredata_status_tally) %>%
 group_by(dcpredata_status_tally) %>%
 tally_and_perc(dcpredata_status_tally) %>%
 filter(!is.na(dcpredata_status_tally)) %>%
 arrange(desc(n)) %>%
 rename(`Status` = dcpredata_status_tally)

kable(dcpredata_status_tally, format = 'markdown', row.names = NA, col.names = c ("Data Carpentry's Respondents by Position", "n", "%"))
```

```{r dc_learners_status}
# This plot is not working

dcpredata_status_tally <- 
dcpredata %>% 
  mutate(Status_ord = fct_relevel(Status, 
                                  ordered_status)) %>% 
  tally_and_perc(Status_ord, na.rm = TRUE)

ggplot(dcpredata_status_tally, 
       aes(Status_ord,
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill = "darkcyan") +
  geom_text(aes(label = n), 
            size= 4,
            nudge_y = 3) + ## This moves the numbers up a bit so they're easier to read. 
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("Position") +
  ylab("% Respondents") +
  ggtitle("Data Carpentry Respondents by Position") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14) 
```

# Demographics: Operating System 

Learners are asked what operating system is on the computer they are bringing to the workshop.

```{r}
# Operating System
OS <- 
dcpredata %>%
  select(OS) %>% 
  gather(col, 
         OS) %>% 
  tally_and_perc(OS, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Operating System` = OS)

# Table
kable(OS)

```

# Respondents' Programming Usage

How often do you currently use any of the following?

```{r}
Programming <- 
dcpredata %>%
  select(`CurrentProgramming`) %>% 
  gather(col, 
         Programming) %>% 
  tally_and_perc(Programming, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Current Programming Usage` = Programming)

# Table
kable(Programming)
```

# Respondents' Satisfaction with Current Data Management Practices

```{r}
# Please rate your level of satisfaction with your current data management and analysis workflow.

levels = c("Very unsatisfied", "Unsatisfied", "Neutral", "Satisfied", "Very satisfied", "Not sure", "Not applicable")

Satisfaction <- 
dcpredata %>%
  select(`CurrentSatisfaction`) %>% 
  gather(col, 
         Satisfaction) %>% 
  tally_and_perc(Satisfaction, 
                 na.rm = TRUE) %>% 
  rename(`CurrentSatisfaction` = Satisfaction)

kable(Satisfaction, format = 'markdown', row.names = NA, col.names = c ("Satisfaction with current data management practices", "n", "%"))

# I want these to show in Likert order, not alpha-order
```

# Why did respondents attend a Data Carpentry Workshop?

Why are you attending this workshop?

```{r}
# Responses are in columns 'WhyAttending' through 'Column29'

WhyAttending <- 
dcpredata %>%
  select(`WhyAttending`:`Column29`) %>% 
  gather(col, 
         WhyAttending) %>% 
  tally_and_perc(WhyAttending, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Why are you attending? Check all that apply.` = WhyAttending)

kable(WhyAttending, format = 'markdown', row.names = NA, col.names = c ("Why are you attending this workshop?", "n", "%"))
```

# How were Respondents' exposed to their Data Carpentry Workshop?

How did you find out about this workshop?

```{r}
# Responses are in columns 'Exposure-Workshop' through 'Column31'

Exposure <- 
dcpredata %>%
  select(`Exposure`:`Column35`) %>% 
  gather(col, 
         Exposure) %>% 
  tally_and_perc(Exposure, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Exposure` = Exposure)

kable(Exposure, format = 'markdown', row.names = NA, col.names = c ("How did you find out about this workshop?", "n", "%"))
```

# Programming Language Covered in Workshop

Which programming language is being covered?

```{r}
ProgrammingLanguage <- 
dcpredata %>%
  select(`ProgrammingLanguageCovered`) %>% 
  gather(col, 
         ProgrammingLanguage) %>% 
  tally_and_perc(ProgrammingLanguage, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Which language is being covered?` = ProgrammingLanguage)

kable(ProgrammingLanguage, format = 'markdown', row.names = NA, col.names = c ("Which language is being covered?", "n", "%"))
```

# Pre/Post Comparison for Data Carpentry's Workshop Outcomeds

Learners were asked to rate their level of agreement with the following statements related to Data Carpentry's workshop goals and learning objectives. The figure below provides a visual representation of their responses, comparing them before the workshop and after the workshop. Axis labels and the corresponding question are as follows:  

+ __AnalysesEasier__: Using a programming language (like R or Python) can make my analyses easier to reproduce. 
+ __OvercomeProblem__: While working on a programming project, if I get stuck, I can find ways of overcoming the problem. 
+ __ProgrammingSoftware__: I am confident in my ability to make use of programming software to work with data.
+ __RawData__: Having access to the original, raw data is important to be able to repeat an analysis.
+ __SearchOnline__: I know how to search for answers to my technical questions online.
+ __WriteScript__: I can write a small program/script/macro to solve a problem in my own work.  

```{r}
# Ability to perform various computing tasks before and after completing the workshop
impact_pre <-
    c("Strongly disagree",
    "Disagree",
    "Neutral",
    "Agree",
    "Strongly agree")

impact_post <- 
  c("Strongly disagree",
    "Disagree",
    "Neutral",
    "Agree",
    "Strongly agree")

# How do I tell R that I want the factors in this order always?
```


```{r}
# Pre-Workshop
# Compute for all tools.

# Before the workshop
pre_computing <- 
dcpredata %>%
  select(`RawData`:`AnalysesEasier`) %>% 
  gather() %>% 
  filter(value %in% impact_pre) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value))) %>% 
  unnest(tallies)
#kable(pre_computing, format = 'markdown', row.names = NA, col.names = c ("Statement", "Level of Agreement", "n", "%"))
```


```{r}
# Post-Workshop
post_computing <- 
dcpostdata %>%
  select(`RawData`:`AnalysesEasier`) %>% 
  gather() %>% 
  filter(value %in% impact_post) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value)))  %>% 
  unnest(tallies) 
#kable(post_computing, format = 'markdown', row.names = NA, col.names = c ("Statement", "Level of Agreement", "n", "%"))
```

```{r}
# Plot before a grouped bar plot, then combine.

computing_before <- 
   ggplot(pre_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             impact_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Respondent Ability Pre-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 10) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) 
```

```{r}
# Plot after a grouped bar plot, then combine.
computing_after <- 
   ggplot(post_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (impact_post))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Confidence Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 10) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())  
# + guides(fill = guide_legend(nrow = 2)) # wraps legend
```          

```{r change_in_confidence} 
# Put the two plots together
library(gridExtra)
grid.arrange(computing_before, 
             computing_after,
             ncol = 1)

# Why are the levels showing in a different order on the grid?
```

```{r agreement_pre}
   ggplot(pre_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             impact_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Agreement Pre-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
```

```{r agreement_post}
ggplot(post_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (impact_post))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Agreement Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
# Why does strongly agree appear first in this plot but last in the plot above?
```

## Paired Analyses Table
```{r}

prep_paired_data <- . %>%
    select(UniqueID, `RawData`:`AnalysesEasier`) %>%
    filter(!is.na(UniqueID)) %>%
    gather(skill, feeling, -UniqueID) %>%
    mutate(feeling_score = case_when(
               feeling == "Strongly disagree" ~ 1,
               feeling == "Disagree"          ~ 2,
               feeling == "Neutral"           ~ 3,
               feeling == "Agree"             ~ 4, 
               feeling == "Strongly agree"    ~ 5,
               is.na(feeling)                 ~ NA_real_, 
               TRUE                           ~ 999
           )) %>%
    assert(in_set(NA, 1, 2, 3, 4, 5), feeling_score)


pre_paired <- dcpredata %>%
    prep_paired_data %>%
    rename_at(vars(-UniqueID, -skill), ~ paste0("pre_", .))
    
post_paired <- dcpostdata %>%
    prep_paired_data %>%
    rename_at(vars(-UniqueID, -skill), ~ paste0("post_", .))

paired_data <- inner_join(pre_paired, post_paired, by = c("UniqueID", "skill"))


t_test_results <- paired_data %>%
    group_by(skill) %>%
    nest() %>% 
    mutate(t_test_res = purrr::map(data, function(x) {
        t.test(x$pre_feeling_score, x$post_feeling_score, paired = TRUE,
               alt = "less") %>%
            broom::tidy()
    })) %>%
    unnest(t_test_res)

t_test <- paired_data %>%
    group_by(skill) %>%
    summarize(
        mean_pre_feeling = mean(pre_feeling_score, na.rm = TRUE),
        n_pre = sum(!is.na(pre_feeling_score)),
        sd_pre_feeling = sd(pre_feeling_score, na.rm = TRUE),
        mean_post_feeling = mean(post_feeling_score, na.rm = TRUE),
        n_post = sum(!is.na(post_feeling_score)),
        sd_post_feeling = sd(post_feeling_score, na.rm = TRUE)
    ) %>%
    left_join(t_test_results, by = "skill")

kable(select(t_test, skill, ends_with("feeling"), starts_with("n"), 
             p.value))
 
```

# Demographic Data for U.S. Participants

With what gender do you most identify?

```{r}
gender = c("Female", "Male", "Transgender female", "Transgender male", "Gender variant/non-conforming", "Prefer not to answer", "Not listed (please specify")
gender = factor(gender)

dcpredata$Gender = factor(dcpredata$Gender, levels = gender)

dcpredata_gender_tally <-
  dcpredata %>%
  group_by(Gender) %>%
  tally() %>%
  filter(!is.na(Gender)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(dcpredata_gender_tally, format = 'markdown', row.names = NA, col.names = c ("Gender Identity", "n", "%"))
```

```{r}
# function to compute number of non-NA responses to a question

n_responses_to_the_question <- function(df, from_colname, to_colname) {

  quo_from_colname <- enquo(from_colname)
  quo_to_colname <- enquo(to_colname)

  rowsums <-
df %>%
  select(UQ(quo_from_colname):UQ(quo_to_colname)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all behaviors
idx <- ifelse(rowsums == 0, FALSE, TRUE)
sum(idx)
}
```

How would you describe yourself?

```{r}
# Responses are in columns 'Race' through 'Column48'
n_responses_race <-
  n_responses_to_the_question(dcpredata,
                              from_colname = Race,
                              to_colname = Column48)

race_perc <-
  dcpredata %>%
    select(Race:Column48) %>%
    gather(col, race_perc) %>%
    group_by(race_perc) %>%
    tally_and_perc(race_perc,
                 na.rm = TRUE,
                 question_n = n_responses_race) %>%
  filter(!is.na(race_perc)) %>%
  arrange(desc(n)) %>%
  rename(Race = race_perc)

kable(race_perc, format = 'markdown', row.names = NA, col.names = c ("Racial/Ethnic Identity", "n", "%"))
```

### Data Carpentry (Post-Workshop)

Respondents were asked which workshop they attended: Ecology, Genomics, Geospatial, Reproducible Research, or Social Sciences. The majority of respondents (`r Workshop_Attended[1]`%) attended an Ecology workshop.

```{r}
#Which workshop did you attend?
workshop = c("Ecology", "Genomics", "Geospatial", "Reproducible Research", "Social Sciences", "I don't know.")
workshop = factor(workshop)

dcpostdata$Workshop = factor(dcpostdata$Workshop, levels = workshop)

dcpostdata_workshop_tally <- 
  dcpostdata %>% 
  group_by(Workshop) %>% 
  tally() %>%
  filter(!is.na(Workshop)) 
```

```{r dc_post_workshop_attended}
ggplot(dcpostdata_workshop_tally, 
       aes(`Workshop`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="purple") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Workshop Attended") +
  ylab("% Respondents") +
  ggtitle("Percentage of Respondents by Data Carpentry Workshop") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```


# Perception of Workshop Atmosphere

I felt comfortbale learning in this workshop environment.

```{r}

comfortable = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")
comfortable = factor(comfortable)

dcpostdata$Comfortable = factor(dcpostdata$Comfortable, levels = comfortable)

dcpostdata_comfortable_tally <- 
  dcpostdata %>% 
  group_by(Comfortable) %>% 
  tally() %>%
  filter(!is.na(Comfortable)) 
```

```{r dc_post_workshop_comfortable_environment}
ggplot(dcpostdata_comfortable_tally, 
       aes(`Comfortable`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="purple") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Level of Agreement") +
  ylab("% Respondents") +
  ggtitle("I felt comfortable learning in this workshop environment") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

I can immediately apply what I learned at this workshop

```{r}
apply = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")
apply = factor(apply)

dcpostdata$ImmediatelyApply = factor(dcpostdata$ImmediatelyApply, levels = apply)

dcpostdata_apply_tally <- 
  dcpostdata %>% 
  group_by(ImmediatelyApply) %>% 
  tally() %>%
  filter(!is.na(ImmediatelyApply)) 
```

```{r dc_post_workshop_immediately_apply}
ggplot(dcpostdata_apply_tally, 
       aes(`ImmediatelyApply`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="purple") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Level of Agreement") +
  ylab("% Respondents") +
  ggtitle("I can immediately apply what I learned at this workshop") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

Were there any accessibility issues that affected your ability to participate in this workshop?

```{r}
issues <- 
dcpostdata %>%
  select(AccessibilityIssues) %>% 
  gather(col, 
         AccessibilityIssues) %>% 
  tally_and_perc(AccessibilityIssues, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Accessibility Issues` = AccessibilityIssues)

# Table
kable(issues)
```

# Perception of Instructors and Helpers

Respondents were asked to rate their level of agreement with several statements regarding their instructor's knowledge, instructional method, and enthusiasm. Their responses are in the figure below, and axis labels corresponding to the statements are as follows:

+ __InstructorsKnowledge__: The instructors were knowledgeable about the material being taught.
+ __InstructorsEnthusiastic__: The instructors were enthusiastic about the workshop.
+ __InstructorsComfortable__: I felt comfortable interacting with the instructors. 
+ __InstructorsClear__: I was able to get clear answers to my questions from the instructors.  

```{r}
# Please rate your level of agreement with the following statements:
#Subsetting a portion of the Likert items from InstructorsClearAnswers to InstructorsKnowledgeable
myvars <- c("InstructorsClearAnswers", "InstructorsEnthusiastic", "InstructorsInteracting", "InstructorsKnowledgeable")
newdata <- dcpostdata[myvars]

cols_with_Agree <- map_lgl(newdata, ~`%in%`("Agree", .x))
newdata_agree <-  newdata[ , cols_with_Agree]

levels = c("Strongly disagree",
   "Disagree",
   "Neutral",
   "Agree",
   "Strongly agree")

 factorfunction <- function(newdata, factlevel){
  factor(newdata, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(newdata, 
              levels=factlevel)}

newdata_agree_likert <- likert(data.frame(lapply(newdata_agree, factor, levels, ordered=TRUE)))
```

```{r dcpost_perception_instructors_heat}
#Heatmap
title <- "Perception of Data Carpentry Instructors"
plot(newdata_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)

# Is there a way to add spaces to the words in the legend?
```

# Recommending Data Carpentry Workshops
Learners were asked how likely they are to recommend this workshop to a friend or colleague using the [Net Promoter Score](https://en.wikipedia.org/wiki/Net_Promoter). The scoring for this question based on a 0 to 100 scale. Respondents scoring from 0 to 64 are labeled *Detractors*, and are believed to be less likely to recommend a workshop. Those who respond with a score of 85 to 100 are called *Promoters*, and are considered likely to recommend a workshop. Respondents between 65 and 84 are labeled *Passives*, and their behavior falls in the middle of Promoters and Detractors. 

```{r}
dcpostdata$`LikelyToRecommend` %>%
    npc(breaks = list(0:64, 65:84, 85:100)) %>%
    data.frame(category = .) %>%
    filter(!is.na(category)) %>%
    count(category) %>%
    mutate("%" = (n / sum(n))*100) %>%
    kable(, format = 'markdown', row.names = NA, col.names = c ("Promoter Score", "n", "%"))
```








### Software Carpentry

```{r}
# Load SWC pre and post-workshop data
# Software Carpentry Pre-Workshop Data
swcpredata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/171231_swcpre.csv")

# Software Carpentry Post-Workshop Data
swcpostdata <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/data/171231_swcpost.csv")
```

# Pre-Workshop Survey Demographics: Workshop Location
In Software Carpentry's pre-workshop survey, respondents are asked whether or not their workshop takes place in the United States.

```{r}
# Tally Software Carpentry's pre-workshop respondents by Country
swcpredata_country_tally <-
swcpredata %>%
  group_by(USWorkshop) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(USWorkshop)) %>%
  arrange(desc(n))
kable(swcpredata_country_tally, format='markdown', col.names = c("SWC Workshops in US", "n", "%"))
```

# Pre-Workshop Survey Demographics: Domain of Research/Work/Study

```{r}
# Tally Software Carpentry's pre-workshop respondents by Discipline
# Responses are in columns 'Domain' through 'Column61'
swcdiscipline <-
 swcpredata %>%
 select(Domain:Column61) %>%
 gather(col, swcdiscipline) %>%
 group_by(swcdiscipline) %>%
 tally_and_perc(swcdiscipline,na.rm = TRUE) %>%
 filter(!is.na(swcdiscipline)) %>%
 arrange(desc(n)) %>%
 rename(`Domain` = swcdiscipline)

kable(swcdiscipline, format = 'markdown', row.names = NA, col.names = c ("Software Carpentry's Respondents by Discipline", "n", "%"))
```




```{r }
# Software Carpentry Respondents by Position
ordered_status <- c(    
    "Undergraduate Student",
    "Graduate Student",
    "Post-doctoral researcher",
    "Faculty",
    "Research staff (including research programmer)",
    "Support staff (including technical support)",
    "Librarian/archivist",
    "Commercial software developer",
    "Other (please specify)"
  )

swcpredata_status_tally <- 
swcpredata %>% 
  mutate(Status_ord = fct_relevel(Status, 
                                  ordered_status)) %>% 
  tally_and_perc(Status_ord, na.rm = TRUE) 
```

```{r swc_learners_status}
ggplot(swcpredata_status_tally, 
       aes(Status_ord,
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill = "darkcyan") +
  geom_text(aes(label = n), 
            size= 4,
            nudge_y = 3) + ## This moves the numbers up a bit so they're easier to read. 
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("Status") +
  ylab("% Respondents") +
  ggtitle("Software Carpentry Respondents by Position") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14) 
```