# Analysis of The Carpentries Long-Term Impact Survey
### Author: [Kari L. Jordan](twitter.com/drkariljordan)
### 17-July 2018 

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(likert)
library(srvyr)
library(NPS)
library(broom)
library(assertr)
library(viridis)
library(patchwork)
library(scales)
library(ggalt)

opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
## puts all figures in figures folder
opts_chunk$set(fig.path='figures/', fig.width = 10,  fig.retina = 2)
```

```{r load-long-term-data}
# Data archived 2018-07-11
impactdata <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/learner-assessment/data/180711_longterm.csv",
                             col_types = cols(
                                 Date =  col_datetime(
                                     format = "%m/%d/%y %H:%M"
                                 ),
                                 .default = "c")
                             )
```

```{r}
# Function that makes a table of counts and percentages
# question_n is set by default to the number of respondents in the survey. This value may have to be set by question.
question_n <- nrow(impactdata)

tally_and_perc <- function(df, colname, na.rm = FALSE, question_n){
  quo_colname <- enquo(colname)

  df %>%
    group_by(!!quo_colname) %>%
    tally() %>%
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>%
    mutate(`%` = round(n / question_n * 100, 1))
}

# function to compute number of non-NA responses to a question

n_responses_to_the_question <- function(df, from_colname, to_colname) {

  quo_from_colname <- enquo(from_colname)
  quo_to_colname <- enquo(to_colname)

  rowsums <-
df %>%
  select(UQ(quo_from_colname):UQ(quo_to_colname)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all behaviors
idx <- ifelse(rowsums == 0, FALSE, TRUE)
sum(idx)
}
```

```{r overview-inline-stats}
## number of learners
n_learners <- nrow(impactdata)

## time period covered
dates <- range(impactdata$Date)
```

## Overview

To date, `r n_learners` learners have completed the Carpentries Long-Term Impact Survey between `r format(min(dates), format="%B %d, %Y")` and `r format(max(dates), format="%B %d, %Y")`. The average amount of time spent completing this survey is six minutes, and it carries an 80% completion rate. The survey was created in March 2017, and data is collected bi-annually. The results of this analysis are cumulative. We invite the community to run their own analyses. All of the data and source code are available on [GitHub](https://github.com/carpentries/assessment/tree/master/learner-assessment).

A special thanks to [Ben Markwick](https://twitter.com/benmarwick), [François Michonneau](https://twitter.com/fmic_) and others who helped write the code used in this report.

### Demographics
This section includes demographics for survey respondents broken down by:

+ Country
+ Field and Career Stage
+ Gender and Racial/Ethnic Identity

#### Breakdown of Respondents by Country

```{r}
# Plot includes Ben's tip to add a percent column to the data_country_tally data frame
# before it goes into the ggplot() function to use reorder on that column name in the ggplot() function
impactdata_country_tally <-
impactdata %>%
  group_by(Country) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(Country)) %>%
  arrange(desc(n))
```

```{r longterm_percent_by_country}
ggplot(impactdata_country_tally,
       aes(reorder(Country, perc),
           perc)) +
  geom_bar(stat = "identity", fill = "darkcyan") +
  theme_classic() +
  xlab("Country") +
  ylab("% Respondents") +
  coord_flip() +
  ggtitle("Percentage of Respondents by Country") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw(base_size = 14)

# There are only a few responses to this question because it was omitted during the second round
# of the survey
```

#### Breakdown of Respondents by Field and Career Stage 

```{r}
# Field of work, research, or study. Responses are in columns 'Field' through 'Column12'

n_responses_to_field_question <-
  n_responses_to_the_question(impactdata,
                              from_colname = Field,
                              to_colname = Column12)

field_perc <-
impactdata %>%
  select(Field:Column12) %>%
  gather(col, field_perc) %>%
  group_by(field_perc) %>%
  tally_and_perc(field_perc,
                 na.rm = TRUE,
                 question_n = n_responses_to_field_question) %>%
  filter(!is.na(field_perc)) %>%
  arrange(desc(n)) %>%
  rename(Field = field_perc)

kable(field_perc,
      format = "markdown",
      digits = getOption("digits"),
      row.names = NA,
      col.names = c("Respondents Field of Research/Work/Study", "n", "%"),
    caption = NULL,
    escape = TRUE)
```

```{r}
# Status of Respondents
status = c("Undergraduate Student", "Graduate Student", "Postdoc", "Faculty", "Industry", "Academic Research Staff", "Other Academic Staff", "Other (please specify)")
status = factor(status)

impactdata$Status = factor(impactdata$Status, levels = status)

impactdata_status_tally <-
  impactdata %>%
  group_by(Status) %>%
  tally() %>%
  filter(!is.na(Status)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))
```

```{r longterm_status}
ggplot(impactdata_status_tally,
       aes(Status, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="darkcyan") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Career Stage") +
  ylab("% Respondents") +
  ggtitle("Marjority Respondents are Graduate Students") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

Provided below is a table of participant counts in each category. Multiple selection was possible.

```{r include=FALSE}
# Table of participant counts in each category (multiple selection was possible)
table_of_status_by_field <- impactdata %>%
  select(Status, Field:FieldOther) %>%
  gather(key = "Field",
         value = "value",
         -Status,
         na.rm = TRUE) %>%
  select(-Field) %>%
  table() %>%
  t()

top_12_fields <- table_of_status_by_field  %>%
  as_tibble() %>%
  group_by(value) %>%
  summarize(sum_by_field = sum(n)) %>%
  arrange(desc(sum_by_field)) %>%
  head(12) %>%
  pull(value)


table_of_status_by_field %>%
  as_tibble() %>%
  filter(value %in% top_12_fields) %>%
  spread(Status, n) %>%
  kable()
```


```{r longterm_respondents_by_field}
# Plot of participant counts in each category (multiple selection was possible)
table_of_status_by_field %>%
  as_tibble() %>%
  filter(value %in% top_12_fields) %>%
  ggplot(aes(x = Status,
             y = value,
             fill = n)) +
    geom_tile() +
    geom_text(aes(label = round(n, 0))) +
    scale_fill_gradient("n",
                        low = "white",
                        high = "blue") +
    labs(title = "Number of Respondants by Field and Career Stage \n(top 12 most common)",
         subtitle = "Note: Multiple selections possible per person",
         y = "Field",
         x = "Career Stage/Status") +
    theme(axis.text.x = element_text(angle = 45,
                                     hjust = 1),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_blank(),
          panel.background = element_blank())

```

#### Breakdown of Respondents by Gender and Racial/Ethnic Identity
Gender Identity and Racial/Ethnic Identity was added to the survey during the second round of data collection, so these numbers do not reflect the cumulative amount of respondents.

```{r}
# What is your gender?
# Gender was added to the survey during the second round of data collection. 
gender = c("Female", "Male", "I prefer not to say")
gender = factor(gender)

impactdata$Gender = factor(impactdata$Gender, levels = gender)

impactdata_gender_tally <-
 impactdata %>%
  group_by(Gender) %>%
  tally() %>%
  filter(!is.na(Gender)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(impactdata_gender_tally, format = 'markdown', row.names = NA, col.names = c("Gender Identity", "n", "%"))

```

```{r}
# How would you describe yourself?
# Responses are in columns 'Race' through 'Column50'
n_responses_race <-
  n_responses_to_the_question(impactdata,
                              from_colname = Race,
                              to_colname = Column50)

race_perc <-
  impactdata %>%
    select(Race:Column50) %>%
    gather(col, race_perc) %>%
    group_by(race_perc) %>%
    tally() %>%
    filter(!is.na(race_perc)) %>%
    mutate(perc = round(n/sum(n) * 100, 0)) %>%
    rename(Race = race_perc)

kable(race_perc, format = 'markdown', row.names = NA, col.names = c("Racial/Ethnic Identity", "n", "%"))
```

### Respondent Engagement in Workshops and Surveys

This section includes the following:

+ Number of Workshops Attended
+ Time Since Attending a Workshop
+ Last Carpentries Workshop Attended
+ Survey Engagement

#### Number of Workshops Attended
```{r}
# Number of workshops attended
impactdata_workshops_tally <-
  impactdata %>%
  group_by(NumWorkshops) %>%
  tally() %>%
  filter(!is.na(NumWorkshops)) %>%
   mutate(perc = round(n/sum(n) * 100, 0))

# Use the code below to include a table of the number of workshops respondents attended
# kable(impactdata_workshops_tally, format = "markdown", row.names = FALSE, col.names = c("Number of Workshops Respondents Attended", "n", "%"))
```

```{r longterm_number_workshops_attended}
ggplot(impactdata_workshops_tally,
       aes(NumWorkshops, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="darkcyan") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Number of Workshops Attended") +
  ylab("% Respondents") +
  ggtitle("Some respondents attend multiple workshops") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

```{r}
# Table of number of workshops that participants have attended
# numworkshops = c("1", "2", "3+")
# numworkshops = factor(numworkshops)
# 
# impactdata$NumWorkshops = factor(impactdata$NumWorkshops, levels = numworkshops)
# 
# impactdata_numworkshops_tally <-
#  impactdata %>%
#   group_by(NumWorkshops) %>%
#   tally() %>%
#   filter(!is.na(NumWorkshops)) %>%
#   mutate(perc = round(n/sum(n) * 100, 0))
# 
# kable(impactdata_numworkshops_tally, format = 'markdown', row.names = NA, col.names = c("Number of Workshops Respondents Attended", "n", "%"))
```

#### Time Since Attending a Workshop

```{r}
# Table of time since workshop attendance
timesinceworkshop = c("0-6 months ago", "6 months - 1 year ago", "More than 1 year ago")
timesinceworkshop = factor(timesinceworkshop)

impactdata$TimeSinceWorkshop = factor(impactdata$TimeSinceWorkshop, levels = timesinceworkshop)

impactdata_timesinceworkshop_tally <-
 impactdata %>%
  group_by(TimeSinceWorkshop) %>%
  tally() %>%
  filter(!is.na(TimeSinceWorkshop)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

# kable(impactdata_timesinceworkshop_tally, format = 'markdown', row.names = NA, col.names = c("Time Since Attending a Workshop", "n", "%"))
```

```{r longterm_time_since_attending_workshop}
ggplot(impactdata_timesinceworkshop_tally,
       aes(TimeSinceWorkshop, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="darkcyan") +
  geom_text(aes(label=n), size= 4 , vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Time Since Attending Carpentry Workshop") +
  ylab("% Respondents") +
  ggtitle("Majority Respondents Attended a Workshop One Year Ago") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

#### Last Carpentries Workshop Attended
```{r}
# Last Carpentries workshop attended
workshop_attended = c("Data Carpentry", "Library Carpentry", "Software Carpentry", "I don't know.")
workshop_attended = factor(workshop_attended)

impactdata$WhichCarpentry = factor(impactdata$WhichCarpentry, levels = workshop_attended)

impactdata_workshop_attended_tally <-
  impactdata %>%
  group_by(WhichCarpentry) %>%
  tally() %>%
  filter(!is.na(WhichCarpentry)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(impactdata_workshop_attended_tally,format = "markdown", row.names = FALSE, col.names = c("Workshop Respondents Attended", "n", "%"))
```

#### Survey Engagement
```{r}
# Is this your first time completing this survey?
first_time = c("Yes", "No", "I don't know.")
first_time = factor(first_time)

impactdata$FirstSurvey = factor(impactdata$FirstSurvey, levels = first_time)

impactdata_firsttime_tally <-
  impactdata %>%
  group_by(FirstSurvey) %>%
  tally() %>%
  filter(!is.na(FirstSurvey)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(impactdata_firsttime_tally, format = 'markdown', row.names = NA, col.names = c ("Learners Taking Survey for First Time", "n", "%"))
```

# Workshop Content
Learners were asked to check all that applies to indicate what content was covered at the last Carpentries workshop they completed. The tables below provide this information, and combinations of tools covered most often.

```{r}
# What content was covered
# Responses are in columns 'ContentCovered' through 'Column23'
workshop_tools <-
 impactdata %>%
 select(ContentCovered:Column23) %>%
 gather(col, workshop_tools) %>%
 group_by(workshop_tools) %>%
 tally() %>%
 filter(!is.na(workshop_tools)) %>%
 mutate(perc = round(n/sum(n) * 100, 0)) %>%
 arrange(desc(n)) %>%
 rename(`ContentCovered` = workshop_tools)

# Use the line below to provide a table of the tools covered.
# Respondents were asked to check all that apply.
kable(workshop_tools, format = "markdown", row.names = FALSE, col.names = c("Content Covered in Respondents Workshops", "n", "%"))

# Ben's tip to use in-line text
# This code produces results to use in the text of the report
Git <- workshop_tools[workshop_tools$Content == 'Git', ]$n
Python <- workshop_tools[workshop_tools$Content == 'Python', ]$n
Unix_Shell <- workshop_tools[workshop_tools$Content == 'Unix Shell', ]$n
R <- workshop_tools[workshop_tools$Content == 'R', ]$n
SQL <- workshop_tools[workshop_tools$Content == 'SQL', ]$n
OpenRefine <- workshop_tools[workshop_tools$Content == 'OpenRefine', ]$n
Spreadsheets <- workshop_tools[workshop_tools$Content == 'Spreadsheets', ]$n
Cloud_Computing <- workshop_tools[workshop_tools$Content == 'Cloud Computing', ]$n
MATLAB <-  workshop_tools[workshop_tools$Content == 'MATLAB', ]$n
Mercurial <-  workshop_tools[workshop_tools$Content == 'Mercurial', ]$n
```


```{r}
# The code segment below from Ben Marwick will show the most combinations of tools covered in our workshops.

n_responses_to_tools_question <-
  n_responses_to_the_question(impactdata,
                              from_colname = ContentCovered,
                              to_colname = Column23)

tools_cols <-
impactdata %>%
  select(ContentCovered:Column23)

list_of_tools_per_person <- list()
for(i in seq_len(nrow(tools_cols))) {
  ii <- quo(i)

  list_of_tools_per_person[[i]] <-
  tools_cols %>%
    slice(!!ii) %>%
          c(., recursive=TRUE) %>%
          unname %>%
    na.omit() %>%
    as.vector()
}

# The code segment below from Ben Marwick will get the tally of combinations of tools and produce a table.
tool_combs <-
purrr::map_chr(list_of_tools_per_person,
               ~paste0(.x, collapse = " "))

tool_combs_df <-
tool_combs %>%
  as_data_frame() %>%
  group_by(value) %>%
  tally() %>%
  mutate(`%` = round(n / sum(n) * 100, 1)) %>%
  arrange(desc(n)) %>%
  filter(value != "")

# Top combinations as entered by respondants
colnames <- c("Frequency of Tools Covered", "n", "%")
kable(tool_combs_df[1:10, ], row.names = NA, col.names = colnames, caption = "")
```

# Workshop Impact
We are interested in knowing what behaviors learners adopt as a result of completing a Carpentries workshop. Respondents were asked to check all that apply.

```{r}
# Code for behaviors adopted
# Responses are in columns 'Behaviors' through 'Column32'

# How many responses do we have to this question?

responses_to_behaviours <-
  n_responses_to_the_question(impactdata,
                              from_colname = Behaviors,
                              to_colname = Column32)


# Use 'gather' to go from wide to long format
Behaviors <-
impactdata %>%
  select(Behaviors:Column32) %>%
  gather(col, Behaviors) %>%
  group_by(Behaviors) %>%
  tally_and_perc(Behaviors,
                 na.rm = TRUE,
                 question_n = responses_to_behaviours) %>%
  filter(!is.na(Behaviors)) %>%
  arrange(desc(n))

#  how many rate either of these three?
#- data management and project organization practices : Behaviors-Adopted
#- used programming languages for automation : Column28
#- used version control to manage code : Column30

relevant_cols <- c("Behaviors-Adopted", "Column28", "Column30")

rowsums <-
  impactdata %>%
  select(one_of(relevant_cols)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# how many of these rows don't sum to zero?
idx <- ifelse(rowsums == 0, FALSE, TRUE)
number_that_adopted_any_of_those_three <- sum(idx)
```

```{r}
# Respondents were asked to check all that apply.
kable(Behaviors,
      format = "markdown",
      digits = getOption("digits"),
      row.names = NA,
      col.names = c("Behaviors Respondents Adopted", "n", "%"),
      caption = NULL,
      format.args = list(),
      escape = TRUE)
```

The table below provides behaviors adopted by career stage..

```{r}
# Need the count of responses in each Status grouping in order to caluclate
# percentages in the next step
respondant_counts_by_group <- impactdata %>%
  group_by(Status) %>%
  tally() %>%
  rename(group_sum = n)

# Calulate summary of numer of respondants selecting each bahavior by group
# Uses a join to the respondant_counts_by_group tibble in order to calulate
# persentages
behaviors_adopted_by_group <- impactdata %>%
  select(Status, Behaviors:Column32) %>%
  gather(col, Behaviors, -Status) %>%
  group_by(Behaviors, Status) %>%
  select(-col) %>%
  na.omit() %>%
  table() %>%
  as_tibble() %>%
  left_join(respondant_counts_by_group) %>%
  mutate(Percent = (n / group_sum) * 100) %>%
  select(Status, Behaviors, Percent)

# Make a table but remove "Other" column beacuse it's full of NAs
behaviors_adopted_by_group %>%
  spread(Status, Percent) %>%
  select(-(starts_with("Other"))) %>%
  kable(format = "markdown",
        digits = 1,
        row.names = NA,
        col.names = NA,
        caption = NULL,
        format.args = list(),
        escape = TRUE)
```

# Programming Usage Pre- and Post-Workshop
Compared to before completing a Carpentries workshop, we want to know how often respondents used programming languages (R, Python, etc.), databases (Access, SQL, etc.), version control software and/or the shell. Below we compare pre/post programming usage.

```{r}
# The code below can be used to get a table and plot of the number of respondents for programming usage pre workshop
impactdata_paired_plot <- impactdata
levels(impactdata$`ProgrammingBefore`)[2] <- "I have not been using tools like these."

# Programming Usage Pre-Carpentry Workshop [Absolute Plot]
programming = c("I had not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
programming = factor(programming)

  impactdata_usage_tally <-
   impactdata %>%
   group_by(ProgrammingBefore) %>%
   tally() %>%
   mutate(`%` = round(n / sum(n) * 100, 1)) %>%
   filter(!is.na(ProgrammingBefore))
```


```{r include=FALSE}
# The code below is for pre-workshop programming usage reported as a percentage.
impactdata %>%
  select(ProgrammingBefore) %>%
   group_by(ProgrammingBefore) %>%
   tally() %>%
   filter(!is.na(ProgrammingBefore)) %>%
   mutate(ProgrammingBefore =     factor(ProgrammingBefore, levels = programming)) %>%
   ggplot(aes(x = `ProgrammingBefore`, y = 100 * (n/sum(n)))) +
     geom_bar(stat = "identity", position = "dodge", fill = "darkcyan") +
     geom_text(aes(label=n), size= 4, vjust=-0.25) +
     scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                          width = 10,
                                                          simplify = FALSE),
                                                  paste,
                                                  collapse = "\n")) +
     theme_classic() +
     xlab("Timeframe") +
     ylab("% respondents") +
     ggtitle("Respondents Programming Usage Pre-Workshop") +
     theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
```

```{r}
# The code below is for post-workshop programming usage (count)
# Programming Usage Post-Carpentry Workshop [Absolute Plot]
  programming = c("I have not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
  programming = factor(programming)

 impactdata$ProgrammingSince = factor(impactdata$ProgrammingSince, levels = programming)

  impactdata_usage_tally <-
   impactdata %>%
   group_by(ProgrammingSince) %>%
   tally() %>%
   mutate(`%` = round(n / sum(n) * 100, 1)) %>%
   filter(!is.na(ProgrammingSince))
```

```{r include=FALSE}
# The code below is for post-workshop programming usage as a percent
impactdata %>%
select(ProgrammingSince) %>%
group_by(ProgrammingSince) %>%
tally() %>%
filter(!is.na(ProgrammingSince)) %>%
mutate(ProgrammingSince = factor(ProgrammingSince, levels = programming)) %>%

ggplot(aes(x = ProgrammingSince, y = 100 * (n/sum(n)))) +
geom_bar(stat = "identity", position = "dodge", fill = "darkcyan", na.rm = TRUE ) +
geom_text(aes(label=n), size= 4, vjust=-0.25) + # Adds count to top of bar
scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("Timeframe") +
    ylab("% respondents") +
    ggtitle("Respondents Programming Usage Since Attending a Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
```

```{r}
# The code below is for Pre/Post plots of programming usage
# It includes tips from Ben and Naupaka
# Make the unique values the same
impactdata$ProgrammingBefore <-
  gsub("I had not been using tools like these.",
       "I have not been using tools like these.",
       impactdata$ProgrammingBefore)

impactdata$ProgrammingBefore <-
  factor(impactdata$ProgrammingBefore,
         levels = programming)

pre_and_post_usage <-
impactdata %>%
  select(ProgrammingBefore,
          ProgrammingSince) %>%
  gather() %>%
  group_by(key, value) %>%
  tally() %>%
  mutate( perc = round(100 * (n/sum(n)), 1)) %>%
  transform(key = factor(
    key,
    levels = c("ProgrammingBefore", "ProgrammingSince"),
    labels = c("Pre", "Post")
  )) %>%
  filter(!is.na(key),
         !is.na(value))
```

```{r slope_in_programming_usage}
source("https://raw.githubusercontent.com/katrinleinweber/r-slopegraph/patches/slopegraph.r")
  
build_slopegraph(pre_and_post_usage,
                 x = "key",
                 y = "perc",
                 group = "value") %>% 
  plot_slopegraph(font_size = 4,
                  slope_col = "darkcyan") +
    ggtitle("Respondents' Programming Usage Pre and Post Workshop (in %)") +
    theme(text = element_text(size = 16))
```

# Workshop Impact
The statements below reflect ways in which completing a Carpentries may impact learners. We asked respondents to rate level of agreement with these statements:

+ __Reproducible__: I have made my analyses more reproducible as a result of completing the workshop.
+ __Recognition__: I have received professional recognition for my work as a result of using the tools I learned at the workshop.
+ __Productivity__: My research productivity has improved as a result of completing the workshop.
+ __Motivation__: I have been motivated to seek more knowledge about the tools I learned at the workshop.
+ __Confidence__: I have gained confidence in working with data as a result of completing the workshop.
+ __Coding__: I have improved my coding practices as a result of completing the workshop.
+ __Career__: I have used skills I learned at the workshop to advance my career.

The heatmap below provides a breakdown of responses.
```{r}
# Jonah's fix to include the correct levels. Variable was renamed to 'levels'
# because 'order' is the name of a function in R.

cols_with_Agree <- map_lgl(impactdata, ~`%in%`("Agree", .x))
data_agree <-  impactdata[ , cols_with_Agree]

levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

# Beth's tip to both order the factors based on levels and unify the factors
 factorfunction <- function(mydata, factlevel){
  factor(impactdata,
         levels=factlevel,
         ordered = TRUE)
    fct_unify(mydata,
              levels=factlevel)}
 # End tip

 # Adjusting names of y axis labels
 names(data_agree) <-
  c("Coding",
    "Confidence",
    "Career",
    "Motivation",
    "Reproducible",
    "Productivity",
    "Recognition")

data_agree_likert <- likert(data.frame(lapply(data_agree, factor, levels, ordered=TRUE)))

agree_or_strongly_agree_improved_3_things <-
  data_agree %>%
  select(Coding, Reproducible, Productivity) %>%
  filter(Coding       %in% c("Agree", "Strongly agree") | # or
         Reproducible %in% c("Agree", "Strongly agree") |
         Productivity %in% c("Agree", "Strongly agree"))

perc_agree_or_strongly_agree_improved_3_things <-
  round(nrow(agree_or_strongly_agree_improved_3_things) / nrow(data_agree) * 100, 0)

received_professional_recognition <-
  data_agree_likert$results %>%
  filter(Item == "Recognition") %>%
  select(Agree, `Strongly agree`) %>%
  sum() %>%
  round(0)
```

```{r longterm_workshop_impact_heatmap}
title <- "Respondents Perception of Workshop Impact"
plot(data_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
```

We are also interested in understanding what impact our workshops have on respondents long-term. This includes the following:

+ Change in Confidence
+ Usage of Tools for Research and/or Work
+ Contributions to Academic Writing
+ Involvement in the Carpentries
+ Continuous Learning

#### Change in Confidence
We asked respondents to rate their change in confidence in the tools that were covered during their Carpentries workshops compared to before the workshop. The figure below provides a synopsis.

```{r}
# Code for change in confidence
confidence <-
  c("I am less confident now.",
    "I am equally confident now.",
    "I am more confident now.")
confidence = factor(confidence)

impactdata$ChangeInConfidence = factor(impactdata$ChangeInConfidence, levels = confidence)

impactdata_change_in_confidence_tally <-
  impactdata %>%
  group_by(ChangeInConfidence) %>%
  tally() %>%
  mutate(`%` = round(n / sum(n) * 100, 1)) %>%
  filter(!is.na(ChangeInConfidence))
```

```{r longterm_change_in_confidence}
ggplot(impactdata_change_in_confidence_tally,
       aes(ChangeInConfidence, y = 100 * (n/sum(n)),
           n)) +
   geom_bar(stat = "identity", fill = "darkcyan") +
   geom_text(aes(label=n), size= 4, vjust=-0.25) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Change in Confidence") +
   ylab("% Respondents") +
   ggtitle("Respondents Change in Confidence 6 or More \nMonths After a Workshop") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_bw(base_size = 14)
```

```{r}
# status <- unique(impactdata$Status)
# status <- factor(status[!is.na(status)])
```

```{r include=FALSE}
# # What is your position?
# status <- factor(status, levels(status)[c(7, 3, 6, 2, 1, 5, 4)])
# # Display ordering.
# print(levels(status))
# 
# impactdata$Position <-
#   factor(impactdata$Status, levels = levels(status))
# 
# change_in_confidence_by_status <- impactdata %>%
#   group_by(ChangeInConfidence, Position) %>%
#   tally() %>%
#   filter(!is.na(ChangeInConfidence)) %>%
#   group_by(Position) %>%
#   mutate(n_status = sum(n)) %>%
#   filter(!is.na(Position)) %>%
#   mutate(perc = n / n_status * 100)
# 
# # Check that percentage total is 100 for each status (Position).
# test_output <- change_in_confidence_by_status %>%
#   group_by(Position) %>%
#   summarize(total = sum(perc))
# expect_equal(test_output$total, rep(100, length(status)))
```

```{r longterm_change_in_confidence_by_status}
# ggplot(data = change_in_confidence_by_status,
#        aes(x = ChangeInConfidence, y = Position)) +
#   geom_tile(aes(fill = perc), colour = "white") +
#   geom_text(aes(label = paste0(round(perc, 1), "%"))) +
#   scale_fill_gradient("Percent",
#                       low = "white",
#                       high = "blue",
#                       limits = c(0, 100)) +
#   xlab("Change in Confidence with Tools by Position") +
#   theme(
#     axis.text.x = element_text(angle = 30, hjust = 1),
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     axis.ticks = element_blank(),
#     panel.background = element_blank()
#   )
```


#### Usage of Tools for Research and/or Work

If respondents are using the tools they learned in a Carpentries workshop, we want to know how they are helping. Respondents were asked to check all that apply.

```{r longterm_change_in_conf_eng_by_status}
# Data are in columns 'How-Tools-Learned-Help' through 'Column37'

# how many responses do we have to this question?

n_reponses_tools_learned_help <-
    n_responses_to_the_question(impactdata,
                              from_colname = HowToolsHelped,
                              to_colname = Column37)

# How many responded to either of these?
# They are improving my overall efficienct : How.Tools.Learned.Helped
# They are improving my ability to analyze data. : Column34
# They are improving my ability to manage data. : Column35

relevant_cols <- c("HowToolsHelped", "Column34", "Column35")

rowsums <-
  impactdata %>%
  select(one_of(relevant_cols)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

idx <- ifelse(rowsums == 0, FALSE, TRUE)
number_that_tools_helped <- sum(idx)

how_help <-
impactdata %>%
  select(HowToolsHelped:Column37) %>%
  gather(col, how_help) %>%
  group_by(how_help) %>%
  tally() %>%
  filter(!is.na(how_help)) %>%
  arrange(desc(n)) %>%
  rename(`HowToolsHelped` = how_help)

tools_helped <-
impactdata %>%
  select(HowToolsHelped:Column37) %>%
  gather(col, tools_helped) %>%
  group_by(tools_helped) %>%
  tally_and_perc(tools_helped, na.rm = TRUE, question_n = n_reponses_tools_learned_help) %>%
  filter(!is.na(tools_helped)) %>%
  arrange(desc(n)) %>%
  rename(`How Tools Covered Have Helped` = tools_helped)

kable(tools_helped, format = "markdown", row.names = FALSE, col.names = c("How Tools Covered Help Respondents", "n", "%"))
```

#### Contributions to Academic Writing
We are also interested in knowing whether completing a Carpentries workshop contributed to writing of a research article, thesis, dissertation, or grant proposal. 

```{r}
# Code chunk for contributions to academic writing

# how many responded to this question?
rowsums <-
impactdata %>%
  select(Writing) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all writing responses
idx <- ifelse(rowsums == 0, FALSE, TRUE)
n_responsed_to_writing <-  sum(idx)

# table about writing
impactdata %>%
  tally_and_perc(Writing,
                 na.rm = TRUE,
                 question_n = n_responsed_to_writing) %>%
  
  kable(,format = 'markdown', row.names = NA, col.names = c("Have Tools Contributed to Respondents' Writing?", "n", "%"))


writing = c("No.", "Not sure.", "Yes.")
writing = factor(writing)

impactdata$Writing = factor(impactdata$Writing, levels = writing)
Contributed_Writing <- round(prop.table(table(impactdata$Writing)) * 100)
```
#### Involvement with the Carpentries
We asked respondents to indicate their involvement in the Carpentries community since completing a Carpentry workshop. Respondents were asked to check all that apply.
```{r}
# Code for involvement (rows Involvement through Column57)
# I want to use the tally_and_perc function, but don't know where to put the question_n
Carpentry_Involvement <-
impactdata %>%
  select(Involvement:Column57) %>%
  gather(col, Carpentry_Involvement) %>%
  group_by(Carpentry_Involvement) %>%
  tally() %>%
  filter(!is.na(Carpentry_Involvement)) %>%
  mutate(perc = round(n/sum(n) * 100, 0)) %>%
  arrange(desc(n)) %>%
  rename(`Involvement Since Attending a Carpentry Workshop` = Carpentry_Involvement)

kable(Carpentry_Involvement, format = 'markdown', col.names = c("Respondents Involvement with The Carpentries", "n", "%"))
```

#### Continuous Learning
Which of the following learning activities (for data management and analysis) have you participated in since completing a Carpentry workshop? Check all that apply.
```{r}
# Code chunk for continuous learning

Learning_Activities <-
impactdata %>%
  select(ContinuousLearning:Column63) %>%
  gather(col, Learning_Activities) %>%
  group_by(Learning_Activities) %>%
  tally() %>%
  filter(!is.na(Learning_Activities)) %>%
  mutate(`%` =round(n / sum(n) * 100, 0) ) %>%
  arrange(desc(n)) %>%
  rename(`Continuous Learning Post-Workshop` = Learning_Activities)

# Code chunk for table of continuous learning activities
kable(Learning_Activities,
      format = "markdown",
      row.names = FALSE,
      col.names = c("Respondents' Continuous Learning Activities", "n", "%"))
```


# Recommending Carpentries Workshops
Have respondents recommended a Carpentry workshop to a friend or colleague? Responses provided below.
```{r}
# Code chunk for whether respondents recommended a workshop
recommended <-
impactdata %>%
  select(Recommended) %>%
  gather(col, Recommended) %>%
  group_by(Recommended) %>%
  tally() %>%
  filter(!is.na(Recommended)) %>%
  mutate(`%` =round(n / sum(n) * 100, 0) ) %>%
  arrange(desc(n)) %>%
  rename(`Recommended a Workshop?` = Recommended)

# Table for responses of recommendations
kable(recommended, format = 'markdown', col.names = c("Respondents who Recommended a Workshop", "n", "%"))
```

# Call to Action
How can we improve this analysis? Submit an [issue](https://github.com/carpentries/assessment/issues) or [pull request](https://github.com/carpentries/assessment/pulls)!