# Data Carpentry's Pilot Pre-Workshop Survey 
### Summary of Current Responses
__Lead__: [Kari L. Jordan](https://github.com/kariljordan)   
__Revised__: 2017-10-20

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
library(tidyverse)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(srvyr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
opts_chunk$set(fig.path='figures/') #puts all figures in figures folder
```
Data Carpentry is piloting a pre/post workshop survey that includes skills-based questions. A [PDF](https://github.com/carpentries/assessment/blob/master/learner-assessment/data-carpentry/preworkshop/2017-pilot/presurvey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the Data Carpentry [assessment](https://github.com/carpentries/assessment/tree/master/learner-assessment/data-carpentry/preworkshop/2017-pilot) repo on GitHub. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.

The following is a summary of the responses that have been collected since March 2017. As of 2017-10-20, 261 responses have been collected for the [pre-workshop survey](https://github.com/carpentries/assessment/blob/master/learner-assessment/data-carpentry/preworkshop/2017-pilot/presurvey.pdf).

```{r echo=FALSE}
data <- readr::read_csv("https://raw.githubusercontent.com/kariljordan/assessment-fork/master/learner-assessment/archives/2017/data/20171020_data.csv")
```

```{r}
# Function that makes a table of counts and percentages
tally_and_perc <- function(df, colname, na.rm = FALSE){
  quo_colname <- enquo(colname)

  df %>% 
    group_by(!!quo_colname) %>% 
    tally() %>% 
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>% 
    mutate(`%` = round(n / sum(n) * 100, 1)) 
}
```

# Demographics

### Domain
```{r}
# Use 'gather' to go from wide to long format
# Responses are in columns 'Domain' through 'Column13'

Research_Domain <- 
data %>%
  select(`Domain`:`Column13`) %>% 
  gather(col, 
         Research_Domain) %>% 
  tally_and_perc(Research_Domain, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Domain (Check all that apply)` = Research_Domain)

kable(Research_Domain)
```

### Status
```{r}
# Use 'gather' to go from wide to long format
# Responses are in columns 'Status' through 'Column21'

Respondent_Status <- 
data %>%
  select(`Status`:`Column21`) %>% 
  gather(col, 
         Respondent_Status) %>% 
  tally_and_perc(Respondent_Status, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Status (Check all that apply)` = Respondent_Status)

# Table
kable(Respondent_Status)
```

### Operating System
```{r}
# Operating System
OS <- 
data %>%
  select(OS) %>% 
  gather(col, 
         OS) %>% 
  tally_and_perc(OS, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Operating System` = OS)

# Table
kable(OS)
```

### Programming Usage
How often do you currently use programming languages (R, Python, etc.) databases (Access, SQL, etc.) version control software or the Unix shell?

```{r}
# How often do you currently use programming languages (R, Python, etc.) databases (Access, SQL, etc.) version control software or the Unix shell?

Programming <- 
data %>%
  select(`Programming-Usage`) %>% 
  gather(col, 
         Programming) %>% 
  tally_and_perc(Programming, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Current Programming Usage` = Programming)

# Table
kable(Programming)
```

### Satisfaction with Data 
Please rate your level of satisfaction with your current data management and analysis workflow.

```{r}
# Please rate your level of satisfaction with your current data management and analysis workflow.

levels = c("Very unsatisfied", "Unsatisfied", "Neutral", "Satisfied", "Very satisfied", "Not sure", "Not applicable")

Satisfaction <- 
data %>%
  select(`Data-Satisfaction`) %>% 
  gather(col, 
         Satisfaction) %>% 
  tally_and_perc(Satisfaction, 
                 na.rm = TRUE) %>% 
  arrange() %>% 
  rename(`Satisfaction` = Satisfaction)

# Table
kable(Satisfaction)
```

### Perception of Attendance 
Why are you attending this workshop?

```{r}
# Why are you attending this workshop?
# Responses are in columns 'Why-Attending' through 'Column25'

Why_Attending <- 
data %>%
  select(`Why-Attending`:`Column25`) %>% 
  gather(col, 
         Why_Attending) %>% 
  tally_and_perc(Why_Attending, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Why are you attending? Check all that apply.` = Why_Attending)

# Table
kable(Why_Attending)
```

### Workshop Exposure
How did you find out about this workshop?

```{r}
# How did you find out about this workshop?
# Responses are in columns 'Exposure-Workshop' through 'Column31'

Exposure <- 
data %>%
  select(`Exposure-Workshop`:`Column31`) %>% 
  gather(col, 
         Exposure) %>% 
  tally_and_perc(Exposure, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Exposure` = Exposure)

# Table
kable(Exposure)
```

### Programming Language Covered 
Which programming language is being covered?

```{r}
# Which programming language is being covered?

Programming_Language <- 
data %>%
  select(`Language-Covered`) %>% 
  gather(col, 
         Programming_Language) %>% 
  tally_and_perc(Programming_Language, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Which language is being covered?` = Programming_Language)

# Table
kable(Programming_Language)
```

# Skills Based Questions

### Question 1 
Which of the following are fundamental rules for producing well formatted spreadsheet tables? Check all that apply.

*Objective*: Describe best practices for data entry and formatting in spreadsheets. 

The answers they should've checked are:

+ Put each variable (e.g. ‘weight’ or ‘temperature’) in its own column.
+ Put each observation in its own row.
+ Leave the raw data raw and make edits to a copy of the data.

The majority of the respondents selected these three options.

```{r}
# Which of the following are fundamental rules for producing well formatted spreadsheet tables? Check all that apply.

Formatting <- 
data %>%
  select(`Spreadsheet-Rules-R`:`Column36`) %>% 
  gather(col, 
         Formatting) %>% 
  tally_and_perc(Formatting, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Fundamental Rules for Spreadsheets` = Formatting)

# Table
kable(Formatting)
```

```{r}
# Code for matrix of formatting spreadsheet tables
# Combinations of responses
formatting_cols <- 
data %>%
  select(`Spreadsheet-Rules-R`:`Column36`)

# Matrix 
m <- as.matrix(formatting_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
formatting_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(formatting_co_occurences, row.names = TRUE, caption = "Matrix of Fundamental Formatting Rules")
```

### Question 2 
*Objective*: Apply best practices to arrange variables and observations in a spreadsheet.

The following spreadsheet table shows data from a survey of teenagers' favorite fruit. Multiple researchers have entered data into the spreadsheet keeping track of date collected, school code, age, sex, and favorite fruit.

| Date Collected   | School Code  | Age-Sex  | Favorite Fruit  |
|---|---|---|---|---|
| 1/19/17  |01   |15-M   | orange  |
| 1/19/17  |01   |17-F  | apple  |   
| 1/19/17  |01  |18-F   | grapes  |   
| 1/20/17  |01   |16-F   | banana  |
| 1/20/17  |02  | 14-M  | pear  |  
| 1/20/17  |02   | 17-F  | mango  |   
| 3/13/17  |02   |15-F   | kiwi  |   
| 3/13/17  |02  |18-F   |peach   |   
| 3/13/17  |02   |16-F   | strawberries  |

We want to know if respondents understand how to structure data in a spreadsheet. We asked which table most improves the structure of this data.

The correct answser is B, which is a spreadsheet table that separates the variables as follows:

| Year   | Month  | Day  | School Code  | Age | Sex | Favorite Fruit |

The majority of respondents selected B, with about a third selecting C. C separated the variables as follows:

| Date collected  | School Code  | Age | Sex | Favorite Fruit |

```{r}
# Which of the following tables most improves the structure of this data?

Data_Structure_R <- 
data %>%
  select(`Data-Structure-R`) %>% 
  gather(col, 
         Data_Structure_R) %>% 
  tally_and_perc(Data_Structure_R, 
                 na.rm = TRUE) %>% 
  arrange() %>% 
  rename(`Which improves data structure?` = Data_Structure_R)

# Table
kable(Data_Structure_R)
```

### Question 3 
*Objective*: Load external data from a csv file into a dataframe in R.

You collected data in a spreadsheet program and would now like to read your data into R. First, you export the data to a file named "data.txt". The file is shown below.

How can you read this data into R, creating the dataframe 'contacts', so that you can work with the data in R?
```{r}
# How can you read this data into R, creating the dataframe 'contacts', 
# so that you can work with the data in R?

Read_Data_R <- 
data %>%
  select(`Read-Data-R`) %>% 
  gather(col, 
         Read_Data_R) %>% 
  tally_and_perc(Read_Data_R, 
                 na.rm = TRUE) %>% 
  arrange() %>% 
  rename(`Reading in data` = Read_Data_R)

# Table
kable(Read_Data_R)
```

### Question 4
*Objective*: Load external data from a csv file into a dataframe in R.

Which of the following options complete the blanks in the statement below to make a true statement. Check all that apply.

Answer A in the previous question ____, because ___.

***This is a check all that apply question, but in the current survey version it's only single select***
```{r}
# Answer A in the previous question ____, because ___.

Read_Data_Reasoning_R <- 
data %>%
  select(`Read-Data-Reasoning-R`) %>% 
  gather(col, 
         Read_Data_Reasoning_R) %>% 
  tally_and_perc(Read_Data_Reasoning_R, 
                 na.rm = TRUE) %>% 
  arrange() %>% 
  rename(`Which improves data structure?` = Read_Data_Reasoning_R)

# Table
kable(Read_Data_Reasoning_R)
```

### Question 5
*Objective*: Checking integrity of loaded data in R

After you load data into a dataframe, what are some things you can do to check that it was imported correctly? Check all that apply.

Of the options, respondents should've selected:

+ Type the name of the data frame to display the whole dataset.
+ Use the str() function to see information about the data.
+ Use the dim() function to see the number of rows and columns in the dataset.

The head() function gives you the first few lines, not the last.
```{r}
# After you load data into a dataframe, what are some things you can do to check that it was imported correctly? Check all that apply.

Check_Data_R <- 
data %>%
  select(`Check-Data-R`:`Column39`) %>% 
  gather(col, 
         Check_Data_R) %>% 
  tally_and_perc(Check_Data_R, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Checking data imported correctly` = Check_Data_R)

# Table
kable(Check_Data_R)
```

```{r}
# Code for checking if data imported correctly
checking_data_cols <- 
data %>%
  select(`Check-Data-R`:`Column39`)

# Matrix 
m <- as.matrix(checking_data_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
checking_data_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(checking_data_co_occurences, row.names = TRUE, caption = "Matrix of Checking Data Import")
```

### Question 6 
*Objective*: Produce a simple plot in R using ggplot.

If 'df' is your dataframe and has columns x and y, which of the follwing lines of code will produce a plot of x versus y?

```{r}
# If 'df' is your dataframe and has columns x and y, which of the follwing lines of code will produce a plot of x versus y?

Plotting_R <- 
data %>%
  select(`Plotting-R`) %>% 
  gather(col, 
         Plotting_R) %>% 
  tally_and_perc(Plotting_R, 
                 na.rm = TRUE) %>% 
  arrange() %>% 
  rename(`Which produces plot x vs. y?` = Plotting_R)

# Table
kable(Plotting_R)
```

### Question 7 
Which of the following options complete the blanks in the statement below to make a true statement. Check all that apply.

Answer C in the previous question ____, because ___.
```{r}
Plotting_Reasoning_R <- 
data %>%
  select(`Plotting-Reasoning-R`:`Column42`) %>% 
  gather(col, 
         Plotting_Reasoning_R) %>% 
  tally_and_perc(Plotting_Reasoning_R, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Reasoning` = Plotting_Reasoning_R)

# Table
kable(Plotting_Reasoning_R)
```

```{r}
# Code for checking if data imported correctly
plotting_reasoning_r_cols <- 
data %>%
  select(`Plotting-Reasoning-R`:`Column42`)

# Matrix 
m <- as.matrix(plotting_reasoning_r_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
plotting_reasoning_r_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(plotting_reasoning_r_co_occurences, row.names = TRUE, caption = "Matrix of Plotting Reasoning Question")
```

# Perception of Confidence, Motivation, and Tools
Respondents were asked to rate their level of agreement (1-Strongly disagree to 5-Strongly agree) with the statements below. The following heat map and Likert plot shows respondents' answers. The x-axis labels for the figure are in bold, and correspond to the statement following.

+ __WriteProgram__: I can write a small program/script/macro to solve a problem in my own work. 
+ __SearchAnswers__: I know how to search for answers to my technical questions online. 
+ __Reproducible__: Using a programming language (like R or Python) can make my analyses easier to reproduce.
+ __RawData__: Having access to the original, raw data is important to be able to repeat an analysis. 
+ __Overcoming__: While workng on a programming project, if I get stuck, I can find ways of overcoming the problem.
+ __Confidence__: I am confident in my ability to make use of programming languages to work with data. 

```{r}
#Likert

cols_with_Agree <- map_lgl(data, ~`%in%`("Agree", .x))
data_agree <-  data[ , cols_with_Agree]

levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

# Beth's tip to both order the factors based on levels and unify the factors
 factorfunction <- function(mydata, factlevel){
  factor(mydata, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(mydata, 
              levels=factlevel)}
 # End tip 
 
 # Adjusting names of y axis labels
 names(data_agree) <- 
  c("WriteProgram",
    "SearchAnswers",
    "RawData",
    "Reproducible",
    "Confidence",
    "Overcoming")

data_agree_likert <- likert(data.frame(lapply(data_agree, factor, levels, ordered=TRUE)))
```

```{r workshop_impact_heatmap}
title <- "Perception of Confidence, Motivation, and Tools"		
plot(data_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
```

```{r workshop_impact_likert}
title <- "Perception of Confidence, Motivation, and Tools"
 theme_update(plot.title = element_text(hjust = 0.5))
plot(data_agree_likert) + ggtitle(title) 

#print(class(data_agree))
 data_agree <- map_if(data_agree,
                     is.character,
                     as.factor)
 # The plot works, but the labels are not in the correct order.
```
```
