---
## To build this report, run:
## `source("build_reports.Rmd");
## build_2020_longterm_report()`
## in the directory one level above
title: Analysis of The Carpentries Long-Term Surveys
author:
  - François Michonneau^[http://orcid.org/0000-0002-9092-966X]
  - Kari L. Jordan^[https://orcid.org/0000-0003-4121-2432]
date: April 1, 2020
output:
  html_document:
    self_contained: no
    toc: true
    toc_float: true
    lib_dir: "../reports/libs"
  pdf_document:
    toc: true
    highlight: zenburn
    df_print: kable
---

```{r setup, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(ggalt)

if (knitr::opts_knit$get("rmarkdown.pandoc.to") == "latex") {
    figout <- "\\maxwidth"
} else {
    figout <- NULL   
}

## puts all figures in figures folder
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.path='../figures/2020-01-longterm-',
  fig.width = 10,
  fig.retina = 2,
  out.width = figout
)

source("../code/2020-longterm-survey/plots.R")

## We combine the datasets into a single one but note that each of these
## datasets is in a randomized order and therefore you can't assume that
## each row corresponds to an individual
base_path <- "../data/2020-longterm-survey"
lt_data <- bind_cols(
  read_csv(
    file.path(
      base_path,
      "20200326-longterm-professional_profile-no-open.csv"
    ),
    col_types = cols(.default = "c")
  ),
  read_csv(
    file.path(
      base_path,
      "20200326-longterm-other_questions-no-open.csv"
    ),
    col_types = cols(.default = "c")
  ),
  read_csv(
    file.path(
      base_path,
      "20200326-longterm-demographics-no-open.csv"
    ),
    col_types = cols(.default = "c")
  )
)
```

In the fourth quarter of 2019 The Carpentries collected feedback from community
members who took a Carpentries workshop within six months. Find more information
about this data collection period [on our
blog](https://carpentries.org/blog/2019/11/long-term-impact-survey/). We are
excited to release the results of our long-term survey, and invite community
members to use this data to champion The Carpentries far and near.

We released [our first long-term
survey results](https://datacarpentry.org/blog/2017/10/long-term-survey-results)
in October 2017. You can find [the report](https://github.com/carpentries/assessment/blob/master/learner-assessment/archives/2017/reports/longtermreport_October2017.pdf) and [its source](https://github.com/carpentries/assessment/blob/master/learner-assessment/archives/2017/code/longtermreport_October2017.rmd) in the [assessment GitHub repository](https://github.com/carpentries/assessment/blob/master/learner-assessment/).

The results included in this report only cover the data collected in 2019 (between November 1st, 2019 and January 2nd, 2020). This report includes the analysis of `r nrow(lt_data)` responses but most questions are optional and specific questions have less answers.

## Respondents Career Stage

The majority of long-term survey respondents are graduate students. "Other
academic staff" includes Librarians, Research Software Engineers, IT Staff, and
Government Research Staff.

```{r occupation, fig.height=6}
plot_multi(
  lt_data,
  var = occupation
)
```

## Respondents Field of Research, Work, or Study

```{r domain, fig.height=8}
plot_multi(
  lt_data,
  var = domain
)

```

## Number of Carpentries Workshops Completed

```{r workshop_attended_amount}
plot_single(
  lt_data,
  var = workshop_attended_amount
)
```

## Time Since Completing a Carpentries Workshop

```{r workshop_attended_age}
plot_single(
  lt_data,
  var = workshop_attended_age
)
```

## Last Carpentries Workshop Attended

```{r workshop_attended_type}
plot_single(
  lt_data,
  var = workshop_attended_type,
  label_levels = rev(c(
    "Data Carpentry",
    "Software Carpentry",
    "Library Carpentry",
    "I don't know"
  ))
)
```

## Content Covered at Last Carpentries Workshop 

```{r workshop_attended_content}
plot_multi(
  lt_data,
  var = workshop_attended_content,
  wrap_width = 14
)
```

## Behaviors Adopted 

```{r behavior_adopted, fig.height=10}
plot_multi(
  lt_data,
  var = behavior_adopted
)
```

## Comparison of Programming Usage Pre- and Post-Carpentries Workshop

```{r change_usage_frequency}

lt_data %>%
  select(frequency_usage_before, frequency_usage_after) %>%
  drop_na() %>%
  pivot_longer(
    everything(),
    names_to = "before_after",
    names_prefix = "frequency_usage_",
    values_to = "programming_usage"
  ) %>%
  mutate(
    programming_usage = case_when(
      grepl("tools", programming_usage) ~ "I don't use these tools",
      TRUE ~ programming_usage
    ),
    before_after = case_when(
      before_after == "before" ~ "Before attending workshop",
      before_after == "after" ~ "After attending workshop"
    )
  ) %>%
  count(before_after, programming_usage) %>%
  group_by(before_after) %>%
  mutate(
    percent = n / sum(n)
  ) %>%
  ungroup() %>%
  ggplot() +
  geom_col(
    aes(y = factor(
      programming_usage,
      levels = c(
        "I don't use these tools",
        "Less than once per year",
        "Several times per year",
        "Monthly",
        "Weekly",
        "Daily"
      )),
      x = percent,
      fill = factor(before_after,
        levels = c(
          "Before attending workshop",
          "After attending workshop"
        ))),
    position = "dodge"
  ) +
  scale_x_continuous(
    expand=c(0, 0), labels = scales::percent,
    breaks=seq(0, 1, by = 0.2), limits = c(0, 1.1)
  ) +
  scale_fill_viridis_d(end = .7) +
  theme_minimal(base_size = 16) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor  = element_blank(),
    panel.spacing.x = unit(30, "pt"),
    axis.line.y = element_line(color="#2b2b2b"),
    plot.margin = unit(c(5, 30, 10, 30), "pt"),
    plot.title = element_text(margin = margin(r = 100, b = 10),
      face="bold"),
    plot.subtitle = element_text(margin = margin(b = 10)),
    plot.caption = element_text(size = 10, margin = margin(t = 10)),
    legend.title = element_blank(),
    legend.position = "top"
  ) +
  labs(
    title = "How has the frequency of usage of programming languages, databases, version control and/or the shell changed before and after the workshop?",
    x = "% Respondents",
    y = ""
  )

```

## Change in Confidence in Tools Covered at Workshop

```{r change_confidence}
plot_single(
  lt_data,
  var = change_confidence,
  label_levels = rev(c(
    "I'm more confident now",
    "I'm equally confident now", 
    "I'm less confident now"
  ))
)
```

## How Tools Help Respondents 

```{r how_tools_help, fig.height=8}
plot_multi(
  lt_data,
  var = how_tools_help
)
```

## Carpentries Workshop Contributing to Research

```{r workshop_contributed_academics}
plot_single(
  lt_data,
  var = workshop_contributed_academics,
  label_levels = rev(c(
    "Yes",
    "Not Sure",
    "No"
  ))
)
```

## Potential Impact on Carpentries Respondents 

```{r workshop_impact, fig.height=15}
lt_data %>%
  mutate_at(
    .vars = vars(starts_with("impact_"), -ends_with("open")),
    ~ as.character(match(., c(
      "Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")
    ))
  ) %>% 
  plot_group(
  prefix = "impact",
  y_levels = as.character(1:5),
  title = " "
  ) +
  labs(subtitle = "(1: Strongly disagree, 3: Neutral, 5: Strongly agree)")
```


## Involvement in Carpentries Community Post-Workshop

```{r community_involvement, fig.height=8}
plot_multi(
  lt_data,
  var = community_involvement
)
```

## Respondents Participating in Learning Activities 

```{r other_activities, fig.height=8}
plot_multi(
  lt_data,
  var = other_activities
)
```

## Respondents Who Recommended a Carpentries Workshop 

```{r has_recommended}
plot_single(
  lt_data,
  var = has_recommended
)
```

## Recommendation and Net Promoter Scores

```{r recommendation_score}
plot_single(
  lt_data,
  var = recommendation_score,
  label_levels = as.character(0:10)
)
```

```{r nps_score}
nps_score <- nps(lt_data)
```


```{r nps, fig.height = 1.5}
nps_plot(nps_score) +
  labs(
    title = "Net Promoter Score"
  )
```

The [Net Promoter Score](https://en.wikipedia.org/wiki/Net_Promoter) (NPS) for
our workshops according to the long-term survey is `r nps_score`. The NPS varies
between -100 and +100. It is calculated by substracting the percentage of
respondents who are considered "Promoters" (rating of 9 or 10) and the
percentage of respondents who are considered "Detractors" (rating equal or below
6). A positive NPS is deemed good, a NPS above 50 is deemed excellent, and an
NPS above 70 is exceptional.


## Respondents' Gender Identity

Note: Gender identity responses apply to U.S. survey respondents only.

```{r demographics_gender}
plot_single(
  lt_data,
  var = demographics_gender
)
```

## Respondents' Racial/Ethnic Identity 

Note: Racial/ethnic identity responses apply to U.S. survey respondents only.

```{r demographics_ethnicity, fig.height=14}
plot_multi(
  lt_data,
  var = demographics_ethnicity 
)
```
