---
## To build this report, run:
## `source("build_reports.Rmd");
## build_2020_12_longterm_report()`
## in the directory one level above
title: Analysis of The Carpentries Long-Term Surveys
author:
  - Kelly Barnes^[https://orcid.org/0000-0001-5797-5181]
  - François Michonneau^[https://orcid.org/0000-0002-9092-966X]
  - Kari L. Jordan^[https://orcid.org/0000-0003-4121-2432]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    self_contained: false
    toc: true
    toc_float: true
    lib_dir: "../reports/libs"
  pdf_document:
    toc: true
    highlight: zenburn
    df_print: kable
    includes:
      in_header: 2020-12-longterm-header.tex
---


```{r setup, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(ggalt)
library(ggstance)
library(kableExtra)

if (knitr::opts_knit$get("rmarkdown.pandoc.to") == "latex") {
  figout <- "\\maxwidth"
  col_width <- "7cm"
  table_format <- "latex"
} else {
  figout <- NULL
  col_width <- "70%"
  table_format <- "html"
}

## puts all figures in figures folder
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.path = "../figures/2020-12-longterm-",
  fig.width = 10,
  fig.retina = 2,
  out.width = figout
)

source("../code/2020-12-longterm-survey/plots.R")

## We combine the datasets into a single one but note that each of these
## datasets is in a randomized order and therefore you can't assume that
## each row corresponds to an individual
base_path_2020 <- "../data/2020-12-longterm-survey"
csv_files_2020 <- list.files(
  path = base_path_2020, pattern = "-no-open\\.csv$",
  full.names = TRUE
)
lt_2020 <- map_dfc(
  csv_files_2020,
  ~ read_csv(., col_types = cols(.default = "c"))
)

## get the old data so we can compare
base_path_2019 <- "../data/2020-longterm-survey"
csv_files_2019 <- list.files(
  path = base_path_2019, pattern = "-no-open\\.csv$",
  full.names = TRUE
)
lt_2019 <- map_dfc(
  csv_files_2019,
  ~ read_csv(., col_types = cols(.default = "c"))
) %>%
  mutate(
    across(
      starts_with("impact"),
      function(.x) {
        match(.x, c(
        "Strongly disagree",
        "Disagree",
        "Neutral",
        "Agree",
        "Strongly agree"
        )) %>%
          as.character()
      }
    )
  )

## transform data in 2019 to match levels in 2020_12
lt_data  <- lt_2019 %>%
  rename(
    gender = demographics_gender,
    ethnicity = demographics_ethnicity,
    first_time = first_survey_take
  ) %>%
  mutate(year = "2019") %>% 
  bind_rows(
    lt_2020 %>%
      mutate(year = "2020")
  ) %>%
  select(year, everything()) %>% 
  mutate(workshop_contributed_academics = case_when(
    workshop_contributed_academics == "Not sure" ~ "I am not sure",
    TRUE ~ workshop_contributed_academics
  )) %>% 
  mutate(ethnicity = gsub("([a-zA-Z\\)])\\(A", "\\1 (A", ethnicity))
```

In the fourth quarter of 2020 The Carpentries collected feedback from community
members who took a Carpentries workshop within six months. Find more information
about this data collection period [on our
blog](https://carpentries.org/blog/2020/09/long-term-survey-is-now-open/). We
are excited to release the results of our long-term survey, and invite community
members to use this data to champion The Carpentries far and near.

We released [our first long-term survey
results](https://datacarpentry.org/blog/2017/10/long-term-survey-results) in
October 2017. You can find [the
report](https://github.com/carpentries/assessment/blob/master/learner-assessment/archives/2017/reports/longtermreport_October2017.pdf)
and [its
source](https://github.com/carpentries/assessment/blob/master/learner-assessment/archives/2017/code/longtermreport_October2017.rmd)
in the [assessment GitHub
repository](https://github.com/carpentries/assessment/blob/master/learner-assessment/).

We released our latest long-term survey results in April 2020. You can find [the
report](https://github.com/carpentries/assessment/blob/master/learner-assessment/reports/2020-01-long-term-report.pdf)
and [its
source](https://github.com/carpentries/assessment/blob/master/learner-assessment/reports-src/2020-01-long-term-survey.Rmd)
in the [assessment GitHub
repository](https://github.com/carpentries/assessment/blob/master/learner-assessment/).

The results included in this report only cover the data collected in 2020
(between September 28th, 2020 and November 1st, 2020). This report includes the
analysis of `r nrow(lt_data)` responses but most questions are optional and
specific questions have less answers.

## Respondents Career Stage

The majority of long-term survey respondents are graduate students. "Other
academic staff" includes Librarians, Research Software Engineers, IT Staff, and
Government Research Staff.

```{r occupation, fig.height=9}
plot_multi(
  lt_data,
  var = occupation,
  year = "2020"
)
```

## Respondents Field of Research, Work, or Study

The largest percentages of long-term survey respondents were from the Life
Sciences (19%) followed by Library and Information Science (17%).

```{r domain, fig.height=15}
plot_multi(
  lt_data,
  var = domain,
  year = "2020"
)
```

## Number of Carpentries Workshops Completed

The majority of long-term survey respondents have completed just one Carpentries
(Software, Data, or Library) workshop. The percentage of those who have
completed only one workshop is up from the previous year.

```{r workshop_attended_amount}
plot_single(
  lt_data,
  var = workshop_attended_amount
)
```

## Time Since Completing a Carpentries Workshop

The majority of long-term survey respondents last completed a Carpentries
workshop between 0 and 6 months ago. In 2019, there was a higher percentage of
responses from those who had completed a workshop more than a year ago.

```{r workshop_attended_age}
plot_single(
  lt_data,
  var = workshop_attended_age
)
```

## Last Carpentries Workshop Attended

Long-term survey respondents were almost evenly split on whether their last
Carpentries workshop was a Data or Software Carpentry workshop with Software
Carpentry being slightly more common than Data Carpentry. A much smaller
percentage of respondents said their last Carpentries workshop was a Library
Carpentry workshop.

```{r workshop_attended_type}
plot_single(
  lt_data,
  var = workshop_attended_type,
  label_levels = rev(c(
    "Data Carpentry",
    "Software Carpentry",
    "Library Carpentry",
    "I don't know"
  ))
)
```

## Content Covered at Last Carpentries Workshop

In 2020, the most common content taught (as reported by long-term survey
respondents) was Git followed by the Unix Shell and Python. A much lower
percentage of respondents reported their workshop covered R compared with 2019.

```{r workshop_attended_content, fig.height=8}
plot_multi(
  lt_data,
  var = workshop_attended_content,
  wrap_width = 14
)
```

## Behaviors Adopted

Long-term survey respondents reported that they were most likely to adopt _using
version control to manage code_ followed by _Other_ behaviors.

```{r behavior_adopted, fig.height=12}
clean_labels <- structure(
  c(
    "Developing a data management and analysis plan",
    "Reusing code",
    "Sharing code or data publicly on places like GitHub or FigShare",
    "Using programming languages like R or Python, or the command line to automate repetitive tasks",
    "Improving data management and project organization",
    "Transforming step-by-step workflows into scripts or functions",
    "Other",
    "Using version control to manage code.",
    "Using databases, scripts and queries to manage large data sets"
  ),
  .Names = c(
    "Developing a data management and analysis plan",
    "Reusing code",
    "Sharing code or data publicly on places like GitHub or FigShare",
    "Using programming languages like R or Python, or the command line to automate repetitive tasks",
    "Improving data management and project organization",
    "Transforming step-by-step workflows into scripts or functions",
    "Other",
    "Using version control to manage code.Using version control to collaborate online (in public or private repositories)",
    "Using databases, scripts and queries to manage large data sets"
  )
) %>%
  stringr::str_wrap(width = 20)
plot_multi(
  lt_data,
  var = behavior_adopted,
  year = "2020"
) +
  scale_y_discrete(
    labels = clean_labels
  )
```

## Comparison of Programming Usage Pre- and Post-Carpentries Workshop

Long-term survey respondents reported using programming languages, databases,
version control and/or the shell more frequently after taking a Carpentries
workshop. Of particular note is the increase in people who now use these tools
daily or weekly as well as the drastic decrease in those reporting they don't
use these tools.

```{r change_usage_frequency, fig.height=6}

lt_data %>%
  select(year, frequency_usage_before, frequency_usage_after) %>%
  drop_na() %>%
  pivot_longer(
    -year,
    names_to = "before_after",
    names_prefix = "frequency_usage_",
    values_to = "programming_usage"
  ) %>%
  mutate(
    programming_usage = case_when(
      grepl("tools", programming_usage) ~ "I don't use these tools",
      TRUE ~ programming_usage
    ),
    before_after = case_when(
      before_after == "before" ~ "Before attending workshop",
      before_after == "after" ~ "After attending workshop"
    )
  ) %>%
  count(year, before_after, programming_usage) %>%
  group_by(year, before_after) %>%
  mutate(
    percent = n / sum(n)
  ) %>%
  ungroup() %>%
  ggplot() +
  geom_col(
    aes(
      y = factor(
        programming_usage,
        levels = c(
          "I don't use these tools",
          "Less than once per year",
          "Several times per year",
          "Monthly",
          "Weekly",
          "Daily"
        )
      ),
      x = percent,
      fill = factor(before_after,
        levels = c(
          "Before attending workshop",
          "After attending workshop"
        )
      )
    ),
    position = "dodge"
  ) +
  scale_x_continuous(
    expand = c(0, 0), labels = scales::percent,
    breaks = seq(0, 1, by = 0.2), limits = c(0, 1.1)
  ) + 
  facet_grid(~ year ) +
  scale_fill_viridis_d(end = .7) +
  theme_minimal(base_size = 16) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(30, "pt"),
    axis.line.y = element_line(color = "#2b2b2b"),
    plot.margin = unit(c(5, 30, 10, 30), "pt"),
    plot.title = element_text(
      margin = margin(r = 100, b = 10),
      face = "bold"
    ),
    plot.subtitle = element_text(margin = margin(b = 10)),
    plot.caption = element_text(size = 10, margin = margin(t = 10)),
    legend.title = element_blank(),
    legend.position = "top"
  ) +
  labs(
    title = str_wrap("How has the frequency of usage of programming languages, databases, version control and/or the shell, changed before and after the workshop?", 55),
    x = "% Respondents",
    y = ""
  )
```

## Change in Confidence in Tools Covered at Workshop

The vast majority of long-term survey respondents reported that they are more
confident using tools covered in the workshop after compared to before.

```{r change_confidence}
plot_single(
  lt_data,
  var = change_confidence,
  label_levels = rev(c(
    "I'm more confident now",
    "I'm equally confident now",
    "I'm less confident now",
    "Other"
  ))
)
```

## How Tools Help Respondents

Long-term survey respondents report that using the tools they learned in a
Carpentries workshop are improving their overall efficiency as well as their
ability to analyze and manage data.

```{r how_tools_help, fig.height=8}
plot_multi(
  lt_data,
  var = how_tools_help
)
```

## Carpentries Workshop Contributing to Research

For about a quarter of long-term survey respondents, attending a Carpentries
workshop has contributed to their writing of a research article, thesis,
dissertation, or grant proposal.

```{r workshop_contributed_academics}

plot_single(
  lt_data,
  var = workshop_contributed_academics,
  label_levels = rev(c(
    "Yes",
    "No",
    "I am not sure"
  ))
)
```

## Potential Impact on Respondents

As a result of taking a Carpentries workshop, the majority of long-term survey
respondents agree that they:

* have used skills learned at the workshop to advance their career; 
* improved their coding practices;
* have gained confidence in working with data;
* made their analyses more reproducible; and 
* been motivated to seek more knowledge about the tools learned.

```{r workshop_impact, fig.height=17}
lt_data %>%
  plot_group(
    prefix = "impact",
    y_levels = as.character(1:5),
    title = " "
  ) +
  labs(subtitle = "(1: Strongly disagree, 3: Neutral, 5: Strongly agree)")
```


## Involvement in Carpentries Community Post-Workshop

Following the workshop, the majority of long-term survey respondents have
subscribed to the Carpentries newsletter. Smaller numbers of respondents have
gotten involved in the Carpentries community in other ways, include attending a
community discussion, engaging on Twitter, and becoming a workshop helper.

```{r community_involvement, fig.height=8}
plot_multi(
  lt_data,
  var = community_involvement,
  year = "2020"
)
```

## Respondents Participating in Learning Activities

Many long-term survey respondents have continued learning after taking a
Carpentries workshop. The most common ways they continued learning were by using
both Carpentries and non-Carpentries self-guided lesson material. Smaller
numbers participated in additional courses (e.g., online short courses,
in-person short courses, or semester-long courses).

```{r other_activities, fig.height=8}
plot_multi(
  lt_data,
  var = other_activities,
  year = "2020"
)
```

## Respondents Who Recommended a Carpentries Workshop

The vast majority of long-term survey respondents reported that they have recommended a Carpentries workshop to a friend or colleague. 

```{r has_recommended}
plot_single(
  lt_data,
  var = has_recommended
)
```

## Recommendation and Net Promoter Scores

```{r recommendation_score, fig.height=8}
plot_single(
  lt_data,
  var = recommendation_score,
  label_levels = as.character(0:10)
)
```

```{r nps_score}
nps_score <- nps(lt_2020)
```


```{r nps, fig.height = 1.5}
nps_plot(nps_score) +
  labs(
    title = "Net Promoter Score"
  )
```

The [Net Promoter Score](https://en.wikipedia.org/wiki/Net_Promoter) (NPS) for
our workshops according to the long-term survey is `r nps_score`. The NPS varies
between -100 and +100. It is calculated by substracting the percentage of
respondents who are considered "Promoters" (rating of 9 or 10) and the
percentage of respondents who are considered "Detractors" (rating equal or below
6). A positive NPS is deemed good, a NPS above 50 is deemed excellent, and an
NPS above 70 is exceptional.


## Respondents' Gender Identity

Note: Gender identity responses apply to U.S. survey respondents only.

A higher percentage of US-based long-term survey respondents are females
compared with males or those who are gender variant/non-conforming.

```{r demographics_gender}
plot_single(
  lt_data,
  var = gender,
  label_levels = rev(
    c(
      "Female",
      "Gender variant/non-conforming",
      "Male",
      "Prefer not to answer"
    )
  )
)
```

## Respondents' Racial/Ethnic Identity

Note: Racial/ethnic identity responses apply to U.S. survey respondents only.

The highest percentage of US-based long-term survey respondents self-identify as
White with smaller percentages identifying as Hispanic or Latino/a, Black or
African American, and Asian.


```{r demographics_ethnicity, warning = FALSE}

ethnicity_short <- tibble::tribble(
  ~short, ~full_name,
  "American Indian or Alaska Native", "American Indian or Alaska Native (Having origins in any of the original peoples of North and South America (including Central America), and who maintains a tribal affiliation or community attachment.)",
  "Asian", "Asian (Having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent including, for example, Cambodia, China, India, Japan, Korea, Malaysia, Pakistan, Indonesia, the Philippine Islands, Thailand, and Vietnam.)",
  "Black or African American", "Black or African American (Having origins in any of the Black racial groups of Africa – includes Caribbean Islanders and others of African origin.)",
  "Hispanic or Latino/a", "Hispanic or Latino(a) (A person of Spanish-speaking origin or ancestry and/or Latin American origin or ancestry – includes Portuguese and Brazilians.)",
  "Pacific Islander", "Native Hawaiian or Other Pacific Islander (Having origins in any of the original peoples of Hawaii, Guam, Samoa, or other Pacific Islands.)",
  "White", "White (Having origins in any of the original peoples of Europe, the Middle East, or North Africa.)",
  "I prefer not to say", "I prefer not to say"
)
ethnicity_short <- ethnicity_short[rev(seq_len(nrow(ethnicity_short))), ]

plot_multi(
  lt_data,
  var = ethnicity,
  label_levels = ethnicity_short,
  year = "2020"
)
```

```{r full_legend}
ethnicity_short %>%
  rename(
    "Label on Plot" = short,
    "Description in Survey" = full_name
  ) %>%
  knitr::kable(format = table_format, booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "striped") %>%
  kableExtra::column_spec(2, width = col_width)
```
