---
output:
  html_document: default
  pdf_document: default
---
# Analysis of Software Carpentry's Post-Workshop Surveys
__Contributors__: [Kari L. Jordan](https://github.com/kariljordan), [Ben Marwick](https://github.com/benmarwick), [Naupaka Zimmerman](https://github.com/naupaka), [Erin Becker](https://github.com/ErinBecker), and [Jonah Duckles](https://github.com/jduckles)  
__July 2017__

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(forcats)
```
For nearly 20 years, Software Carpentry has developed material and trained instructors to teach computing skills to researchers in science, medicine, engineering, and other disciplines. This report is an analysis of the post-workshop survey responses collected for Software Carpentry's workshops from March 2015 through July 2017. In this two year period, nearly 4,000 responses were collected.

A [PDF](https://github.com/carpentries/assessment/blob/master/software-carpentry/postsurvey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the [assessment](https://github.com/carpentries/assessment) repo on GitHub. Special thank you to Ben Marwick, Naupaka Zimmerman, Erin Becker, and Jonah Duckles. These individuals made valuable contributions to the code that was used to create the figures in this report.

Community members are invited to contribute code to this analysis. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.

```{r include=FALSE}
data <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/software-carpentry/postworkshop/2017-July/data.csv")
```
### Respondent Demographics
A host of initiatives have been developed and implemented globally to address gender disparities in computing. Software Carpentry's volunteer instructors have hosted hundreds of workshops since 1998, and the post-workshop survey data shows __parity__ in attendance of males compared to females.
```{r}
# This code chunk was provided by Ben Marwick
# Since we do this operation often in this document let's write a function to save typing later. 
# Here's a function that makes a table of counts and percentages
tally_and_perc <- function(df, colname, na.rm = FALSE){
  quo_colname <- enquo(colname)

  df %>% 
    group_by(!!quo_colname) %>% 
    tally() %>% 
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>% 
    mutate(`%` = round(n / sum(n) * 100, 1)) 
}

# Table with n and percentages
data %>% 
  tally_and_perc(Gender, na.rm = TRUE) %>%  # our custom function!
  kable()
```

A breakdown of Software Carpentry's learners by __status__ is provided below.
```{r echo=FALSE}
# Code chunk for Status of Respondents
# Ben suggested using the forcats pkg to handle factors because it works well with dplyr.
ordered_status <- c(
    "Undergraduate Student",
    "Graduate Student",
    "Post-doctoral researcher",
    "Faculty",
    "Research staff (including research programmer)",
    "Support staff (including technical support)",
    "Librarian/archivist",
    "Commercial software developer",
    "Other (please specify)"
  )

data_status_tally <- 
data %>% 
  mutate(Status_ord = fct_relevel(Status, 
                                  ordered_status)) %>% 
  tally_and_perc(Status_ord, na.rm = TRUE) 

ggplot(data_status_tally, 
       aes(Status_ord,
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill = "darkcyan") +
  geom_text(aes(label = n), 
            size= 4,
            nudge_y = 3) + ## This moves the numbers up a bit so they're easier to read. 
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("Status") +
  ylab("% Respondents") +
  ggtitle("Majority of Respondents were Graduate Students") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/status.png")
```

```{r include=FALSE}
# Code chunk to include data in markdown report
# Using the dplyr method per Ben's suggestion
Status <- round(prop.table(table(data$Status)) * 100)
Status

data_status_tally %>% 
  setNames(c("Status", "n", "%")) %>% 
  kable
```

`r Status[3]`% of Software Carpentry's post-workshop survey respondents are __Graduate Students__. 

A breakdown of respondents by research domain/field of work or study is provided below. Respondents were asked to check all that apply. The majority of Software Carpentry learners work in __Life Sciences__.
```{r}
# Code chunk for breakdown by domain of research/work/study.
# Data in columns `Research-Domain-1` through `Research-Domain-16`
Research_Domain <- 
data %>%
  select(`Research-Domain-1`:`Research-Domain-16`) %>% 
  gather(col, 
         Research_Domain) %>% 
  tally_and_perc(Research_Domain, 
                 na.rm = TRUE) %>% 
  arrange(desc(n)) %>% 
  rename(`Research Domain` = Research_Domain)

kable(Research_Domain)
```

### Respondent Perception of Workshop Content and Atmosphere
Software Carpentry has developed an interactive instructional approach that includes direct instruction (i.e. explicit teaching and demonstrations), indirect instruction (i.e. problem solving and discovery), and experiential learning. Respondents have mixed feelings about the pace of the workshop they attended, as outlined below.

```{r}
# Code chunk for workshop pace.
# Uses the function we created above and removes NAs
data %>% 
  tally_and_perc(Pace,              
                 na.rm = TRUE) %>%  
  kable()
```

Respondents were asked to indicate their perception of the balance of lecture to hands-on work in the workshop. A breakdown of their responses is provided below.

```{r}
# Code chunk for balance of lecture to hands-on work.
ordered_balance <- c("Too much lecture", "Slightly too much lecture", "Balanced (lecture/hands-on)","Slightly too much hands-on", "Too much hands-on")

balance_tally <- 
data %>% 
  mutate(balance_ordered = fct_relevel(Balance,
                                       ordered_balance)) %>% 
  tally_and_perc(balance_ordered,
                 na.rm = TRUE)   # our custom function! 

kable(balance_tally, 
      col.names = c("Balance: Lecture to Hands-On Work", "n", "%"))

# get a value to use in the text
balanced <-
  balance_tally %>% 
  filter(balance_ordered == "Balanced (lecture/hands-on)") %>% 
  pull(`%`)
```

`r balanced`% of respondents felt the workshop they attended was well balanced between lecture and hands-on learning.

Learners were asked to rate their level of agreement on a scale of 1 (Strongly Disagree) to 5 (Strongly Agree) for the following statements regarding the atmosphere and content of the workshop they attended:

* __Atmosphere__: The overall atmosphere of the workshop was welcoming.     
* __Material__: The material presented matched the workshop description.
* __Recommend__: I would recommend this workshop to a friend/colleague.     
* __Skills__: I learned skills that I will be able to use in my research/work.     
* __Worth__: The workshop was worth my time.     
* __Information__: The amount of information covered at the workshop was reasonable for allotted time.   

The following Likert chart is an analysis of learner responses to the statements above. 
```{r}
# Code chunk for Likert plot (perception of workshop atmosphere).
# We used the Likert package (http://jason.bryer.org/likert/). 
ordered_agree <-
   c("Strongly Disagree",
   "Disagree",
   "Neither Agree nor Disagree",
   "Agree",
   "Strongly Agree")

likert_cols <- 
 data %>% 
   select(which(map_lgl(data, ~`%in%`("Agree", .x)))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_agree))) %>% 
  filter_all(all_vars(!is.na(.)))

lc <- likert(data.frame(likert_cols))

# This is how you change the column names for the y-axis labels.
# Can't seem to do anything about the periods between the words

names(likert_cols) <- 
  c("Information",
    "Atmosphere",
    "Skills",
    "Material",
    "Recommend",
    "Worth"
    )

lc <- likert(data.frame(likert_cols))
title <- "Perception of Workshop Atmosphere & Content"
 theme_update(plot.title = element_text(hjust = 0.5))
plot(lc) + ggtitle(title)

# Double check the plot with a table:
xx <- 
likert_cols %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_agree,
              value))
ggsave("figures/content_perception.png")
``` 

The data strongly suggests that Software Carpentry provides a welcoming environment for its learners where the material not only matches the workshop description, but is worth the time learners spend learning it. Learners acquire skills they are able to apply to their research and/or job function in the time allotted over the two-day period. Lastly, learners feel impressed to recommend the workshop to a friend or colleague.

### Respondent Perception of Workshop Instructors and Helpers
A strength of Software Carpentry's ecosystem is its instructors and helpers. Learners who responded to Software Carpentry's post-workshop survey were asked to rate how they felt instructors and helpers worked as a team based on the following criteria:  

* __Considerate__: Instructors/Helpers were considerate.
* __Enthusiastic__: Instructors/Helpers were enthusiastic. 
* __Communicators__: Instructors/Helpers were good communicators.    
* __Clear.Answers__: Instructors/Helpers gave clear answers to your questions.   

The two Likert plots below provide an analysis of respondent answers.
   
```{r echo=FALSE}
# Code chunk for likert plot (perception of workshop instructors/helpers)
ordered_often <-
  c("Never", "Rarely", "Sometimes", "Often", "All of the time")

# Instructors
likert_cols_often_Inst <- 
 data %>% 
   select(grep("Instructors-", names(.))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_often))) %>% 
   filter_all(all_vars(!is.na(.))) 
   
names(likert_cols_often_Inst) <- 
  gsub("Instructors-", "", names(likert_cols_often_Inst))
  
lc_often_inst <- likert(data.frame(likert_cols_often_Inst))

plot(lc_often_inst) +
  ggtitle("Perception of Workshop Instructors")
ggsave("figures/instructors_perception.png")

# To relabel the y-axis, see the previous chunk

# Double check the plot with a table:
xx <- 
likert_cols_often_Inst %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_often,
              value))

# Helpers
likert_cols_often_h <- 
 data %>% 
   select(grep("Helpers-", names(.))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_often))) %>% 
   filter_all(all_vars(!is.na(.))) 
   
names(likert_cols_often_h) <- 
  gsub("Helpers-", "", names(likert_cols_often_h))
  
lc_often_h <- likert(data.frame(likert_cols_often_h))

plot(lc_often_h) +
  ggtitle("Perception of Workshop Helpers")
ggsave("figures/helpers_perception.png")

# To relabel the y-axis, see the previous chunk

# let's double check the plot with a table:
xx <- 
likert_cols_often_h %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_often,
              value))
```

Software Carpentry's workshop instructors and helpers create an environment where learners are able to receive clear answers to their questions. Additionally, instructors and helpers communicate clearly with learners and are both enthusiastic about the material being taught and considerate of Software Carpentry learners.

```{r include=FALSE}
# Code chunk to include data in markdown report
Enough_Helpers <- 
data %>% 
  tally_and_perc(`Enough-Helpers`, 
               na.rm = TRUE) %>% 
  filter(`Enough-Helpers` == "Yes") %>% 
  pull(`%`)
```

Additionally, `r Enough_Helpers`% of respondents felt there were enough helpers in the workshop they attended.

### Respondent Self-Reported Knowledge of Tools Covered
Software Carpentry seeks to know more about learners' experience with the tools covered in their workshop before attending, and after attending the workshop. A series of questions were developed around learners' prior knowledge and perception of the tools they learned. Workshops are self-organized, and each workshop includes the following __core topics__:  

* Automating tasks using the Unix shell;  
* Structured programming in Python, R, or MATLAB; and  
* Version control using Git or Mercurial.  

Learners were asked to indicate their level of knowledge of the Unix shell, R, Python, Git, and SQL prior to attending a Software Carpentry workshop. Not all workshops cover SQL.

Firstly, a breakdown of how much of the information presented was new to the respondents is provided below.
```{r}
# Code chunk of how much information presented at the workshop was new.
ordered_new_information <-
  c("None of it", 
    "Some of it", 
    "About half of it", 
    "Most of it", 
    "All of it")
 
data_new_information_tally <- 
data %>% 
  mutate(new_info_fct = fct_relevel(`New-Information`, 
                                   ordered_new_information)) %>% 
  tally_and_perc(new_info_fct,
                 na.rm = TRUE)

# How many learned new information?
perc_learned_new_info <- 
data_new_information_tally %>% 
  filter(new_info_fct == "Most of it") %>% 
  pull(`%`) %>% 
  round(0)

perc_learned_all_new_info <- 
data_new_information_tally %>% 
  filter(new_info_fct == "All of it") %>% 
  pull(`%`) %>% 
  round(0)

ggplot(data_new_information_tally, 
       aes(new_info_fct, 
           y = `%`,
           n)) +
  geom_bar(stat = "identity", 
           fill="darkcyan") +
  geom_text(aes(label=n), 
            size= 4,
            nudge_y = 3) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, 
                                                       width = 10, 
                                                       simplify = FALSE), 
                                               paste, collapse="\n")) +
  theme_classic() +
  xlab("How Much Information Was New?") +
  ylab("% Respondents") +
  ggtitle(paste(perc_learned_new_info, # don't hard-code values! use a stored value
                "% Respondents Learned Mostly New Information")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/new_information.png")
```
```{r include=FALSE}
# Code chunk to include data in markdown report
New_Information <- round(prop.table(table(data$`New-Information`)) * 100)
```

`r New_Information[1]`% of respondents said about half of the material they learned in a workshop was new to them, and `r New_Information[3]`% of respondents reported that most of the information they learned in the workshop they attended was new to them, while `r New_Information[2]`% reported that all of the information they learned was new. 

Taking a look at each tool more closely, the Likert plot below provides a breakdown of respondents' self-reported knowledge of the tools covered before attending a workshop. From the figure we see that more than half of respondents had little or no knowledge of the tools covered in their workshop.
```{r}
# Code chunk for Likert plot pre-workshop knowledge
# Code by Ben and Kari
ordered_little <-
  c("Little or no knowledge of topic",
    "Some knowledge of topic",        
    "Extensive knowledge of topic")  # yours doesn't match the data

likert_cols_little <- 
 data %>% 
   select(which(map_lgl(data, ~`%in%`("Little or no knowledge of topic", .x)))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_little))) %>% 
  filter_all(all_vars(!is.na(.))) 

# To relabel the y-axis, remove the '-Pre like this:"

names(likert_cols_little) <- gsub("-Pre", "", names(likert_cols_little) )

lc_little <- likert(data.frame(likert_cols_little))

plot(lc_little) +
  ggtitle("Self-Reported Knowledge of Tools Covered Pre-Workshop")

# Double check the plot with a table:
xx <- 
likert_cols_little %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_little,
              value))
ggsave("figures/pre_knowledge.png")
```
```{r include=FALSE}
# Code chunk to include data in markdown report
Knowledge_SQL <- round(prop.table(table(data$`SQL-Pre`)) * 100)
Knowledge_Git <- round(prop.table(table(data$`Git-Pre`)) * 100)
Knowledge_Git
Knowledge_R <- round(prop.table(table(data$`R-Pre`)) * 100)
Knowledge_Unix_Shell <- round(prop.table(table(data$`Unix-Shell-Pre`)) * 100)
Knowledge_Python <- round(prop.table(table(data$`Python-Pre`)) * 100)
```

An interesting result is the percentage of learners who had little or no knowledge of Git and SQL (`r Knowledge_Git[2]`% and `r Knowledge_SQL[2]`% respectively). However, `r Knowledge_R[3]`%, `r Knowledge_Unix_Shell[3]`%, and `r Knowledge_Python[3]`% of respondents already had some knowledge of R, the Unix shell, and/or Python, respectively.

Individuals who are new to computer programming tend to be intimidated for lack of familiarity with syntax and terms. As Software Carpentry learners have varying knowledge levels of the tools covered pre-workshop, we are interested in understanding learners self-reported feeling of intimidation with these tools. The Likert plot below provides a breakdown by tool (Git, SQL, etc.).

```{r}
# Code chunk for Likert plot perception of how intimidating the topics were
ordered_intim <-
  c("Not at all intimidating",
    "Not very intimidating",
    "Neither intimidating nor unintimidating",
    "Slightly intimidating to me",
    "Very intimidating to me",        
    "N/A or No opinion")  

likert_cols_intim <- 
 data %>% 
   select(which(map_lgl(data, ~`%in%`("Very intimidating to me", .x)))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_intim))) %>% 
  filter_all(all_vars(!is.na(.)))  %>% 
  # drop the "N/A or No opinion" rows
  filter_all(all_vars(. != "N/A or No opinion"))  %>% 
  mutate_all(funs(fct_drop(., "N/A or No opinion"))) 

names(likert_cols_intim) <- gsub(".Perception", "", names(likert_cols_intim))

lc_intim <- likert(data.frame(likert_cols_intim))

plot(lc_intim) +
  ggtitle("Self-Reported Feeling of Intimidation Pre-Workshop") 

# Double check the plot with a table:
xx <- 
likert_cols_intim %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_intim,
              value))
ggsave("figures/pre_intimidation.png")
```
```{r}
# Code chunk to include data in markdown report
Perception_SQL <- round(prop.table(table(data$`SQL-Perception`)) * 100)
#Perception_SQL
Perception_Git <- round(prop.table(table(data$`Git-Perception`)) * 100)
#Perception_Git
Perception_R <- round(prop.table(table(data$`R-Perception`)) * 100)
#Perception_R
Perception_Unix_Shell <- round(prop.table(table(data$`Unix-Shell-Perception`)) * 100)
#Perception_Unix_Shell
Perception_Python <- round(prop.table(table(data$`Python-Perception`)) * 100)
#Perception_Python
```

Taking a closer look at the responses by percentage in the table below, we see that at least 44.5% of respondents felt at least one of the tools covered in the workshop they attended was either slightly or very intimidating.
```{r}
kable(xx, row.names = FALSE, col.names = c("Perception", "Git", "Python", "R", "SQL", "Shell"))
```

### Self-Reported Knowledge Increase
Software Carpentry is not only interested in creating an atmosphere where learning programming becomes less intimidating, but we want for learners to leave with increased knowledge of the tools that were covered in their workshop. The Likert plot below provides a breakdown of respondents' self-reported knowledge increase.
```{r}
# Code chunk for knowledge increase post workshop
ordered_icre <-
  c("No increase in my knowledge",                
   "Knowledge increased a little",               
   "Knowledge increased slightly",               
   "Knowledge increased a great deal")

exclude <- 
  c(ordered_intim,
    "N/A - Not covered at this workshop",
    "No change - (Not less or more intimidating)",
    "Became much more intimidating",
    "Became slightly more intimidating",
    "Became slightly less intimidating",
    "Became much less intimating" ,
    "Became much more intimating" 
    )

likert_cols_incre <- 
 data %>% 
   select(contains("Knowledge-Increase")) %>%  # we can subset by colnames, no need to search in the col contents like we did previously 
   mutate_if(is.character, as.factor) %>% 
   filter_all(all_vars(!is.na(.))) %>% 
  # drop rows that are not about knowledge change
  filter_all(all_vars(!(. %in% exclude)))  %>% 
  mutate_all(funs(fct_drop(., as_factor(exclude)))) %>% 
  mutate_all(funs(fct_relevel(., ordered_icre))) 

names(likert_cols_incre) <- gsub(".Knowledge.Increase", "", names(likert_cols_incre) )

lc_incre <- likert(data.frame(likert_cols_incre))

# looks right!
plot(lc_incre) +
  ggtitle("Self-Reported Knowledge Increase Post-Workshop")

# let's double check the plot with a table:
xx <- 
likert_cols_incre %>% 
  gather(key, value) %>% 
  group_by(key, value) %>% 
  tally() %>% 
  mutate(perc = round(n / sum(n) * 100, 1)) %>% 
  select(-n) %>% 
  spread(key, perc) %>% 
  slice(match(ordered_icre,
              value))
ggsave("figures/knowledge_increase.png")
```
```{r}
# Code chunk to include data in markdown report
Knowledge_Increase_SQL <- round(prop.table(table(data$`SQL-Knowledge-Increase`)) * 100)
#Knowledge_Increase_SQL
Knowledge_Increase_Git <- round(prop.table(table(data$`Git-Knowledge-Increase`)) * 100)
#Knowledge_Increase_Git
Knowledge_Increase_R <- round(prop.table(table(data$`R-Knowledge-Increase`)) * 100)
#Knowledge_Increase_R
Knowledge_Increase_Unix_Shell <- round(prop.table(table(data$`Unix-Shell-Knowledge-Increase`)) * 100)
#Knowledge_Increase_Unix_Shell
Knowledge_Increase_Python <- round(prop.table(table(data$`Python-Knowledge-Increase`)) * 100)
#Knowledge_Increase_Python
```

One thing to note is that SQL is not covered in all workshops (`r Knowledge_Increase_SQL[4]`% of respondents said this was not covered). This explains the large portion of respondents that had no increase in their knowledge of SQL.

`r Knowledge_Increase_Git[4]`% of respondents said their knowledge of Git increased a great deal. This is great news, as `r Knowledge_Git[2]`% of respondents reported having little or no knowledge of Git before attending a Software Carpentry workshop!

### Self-Reported Knowledge Increase: Pre/Post Comparison
Now let's take another look at learners' prior knowledge with the tools covered in the workshop they attended, compared to after the workshop. The grid below provides the breakdown by tool   

```{r}
# Code chunk for Pre/Post plots for knowledge and perception of tools covered
# Major help from Ben: Because the pre- and post- columns are quite different, we
# cannot put them on the same plot. So let's do two plots then stack them up
# Use grid.arrange(), nest(), and map() to combine the pre/post plots
  
  knowledge_pre <-
    c(
    "Little or no knowledge of topic",
    "Some knowledge of topic",
    "Extensive knowledge of topic"
    )

knowledge_post <- 
  c("No increase in my knowledge", 
    "Knowledge increased slightly", 
    "Knowledge increased a little", 
    "Knowledge increased a great deal")

# Compute for all tools.

# Before the workshop
pre_knowledge <- 
data %>%
  select(contains("-Pre")) %>% 
  gather() %>% 
  filter(value %in% knowledge_pre) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value))) %>% 
  unnest(tallies) %>% 
  mutate(key = gsub("-Pre", "", key))

# After the workshop
post_knowledge <- 
data %>%
  select(contains("Knowledge-Increase")) %>% 
  gather() %>% 
  filter(value %in% knowledge_post) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value)))  %>% 
  unnest(tallies) %>% 
  mutate(key = gsub("-Knowledge-Increase", "", key))

# Plot before and after as two grouped bar plots, then combine.

tools_before <- 
   ggplot(pre_knowledge, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             knowledge_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Knowledge before workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())

tools_after <- 
   ggplot(post_knowledge, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (knowledge_pre))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Knowledge after workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
          
  
# put the two plots together
library(gridExtra)
grid.arrange(tools_before, 
             tools_after,
             ncol = 1)
ggsave("figures/prepost_knowledge.png")
```

### Motivation to Learn Post-Workshop
Another goal of Software Carpentry is for learners to leave the workshop motivated to continue their learning. From the figure below, we see that learners are more motivated to continue learning and improving upon the skills that were covered in their workshop.
```{r}
# Code chunk for motivation to learn post-workshop
# Same concept as previous chunk
ordered_motiv <- 
  c("Less motivated",
    "Slightly less motivated",
     "No change in motivation",
    "More motivated",
    "Much more motivated")

# Compute for all tools...

# Motivation after the workshop
post_motivation <- 
data %>%
  select(grep("-Motivation", names(.))) %>% 
  gather() %>% 
  filter(value %in% ordered_motiv) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value))) %>% 
  unnest(tallies)  %>% 
  mutate(key = gsub("After-|-Motivation", "", key))
  
# Plot

   ggplot(post_motivation, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             ordered_motiv))) +
    geom_col(position = "dodge") +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Motivation after workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) +
    guides(fill=guide_legend(nrow=2,
                             byrow=TRUE)) 
   ggsave("figures/post_motivation.png")
```

### Respondent Ability to Perform Computing Tasks
Motivation is important, but being confident in your ability to complete specific computing tasks is an equally important goal of Software Carpentry. The grid below shows respondents' self-reported ability to complete tasks including: 

* Using pipes to connect shell commands 
* Writing a 'for loop' to automate tasks   
* Initializing a repository with git 
* Writing a function 
* Importing a library or package in R or Python 
* Writing a unit test in Python or R 
* Writing an SQL query 

It also provides their self-reported level of confidence in being able to complete the tasks above after completing the workshop.
```{r}
# Code chunk for ability to perform various computing tasks
computing_pre <-
    c(
    "Yes",
    "No",
    "Maybe"
    )

computing_post <- 
  c("Confidence increased slightly", 
    "Confidence increased a bit", 
    "Confidence increased greatly", 
    "No change in confidence",
    "N/A - Not covered at workshop")

# Compute for all tools.

# Before the workshop
pre_computing <- 
data %>%
  select(contains("-Before-Workshop")) %>% 
  gather() %>% 
  filter(value %in% computing_pre) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value))) %>% 
  unnest(tallies) %>% 
  mutate(key = gsub("-Before-Workshop", "", key))

# After the workshop
post_computing <- 
data %>%
  select(contains("-After-Workshop")) %>% 
  gather() %>% 
  filter(value %in% computing_post) %>% 
  nest(-key) %>% 
  mutate(tallies = purrr::map(data, ~tally_and_perc(.x, value)))  %>% 
  unnest(tallies) %>% 
  mutate(key = gsub("-After-Workshop", "", key))

# Plot before and after as two grouped bar plots, then combine.

computing_before <- 
   ggplot(pre_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             computing_pre))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, 
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Respondent Ability Pre-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) 

computing_after <- 
   ggplot(post_computing, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (computing_pre))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Respondents") +
    ggtitle("Level of Confidence Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank())
          
  
# Put the two plots together
library(gridExtra)
grid.arrange(computing_before, 
             computing_after,
             ncol = 1)
ggsave("figures/prepost_confidence.png")
```

Let's take a closer look with a table. The data shows an increase in confidence for nearly all of the computing tasks outlined above.
```{r}
kable(pre_computing, col.names = c("Skill", "Ability Pre-Workshop", "n", "%"))
kable(post_computing, col.names = c("Skill", "Confidence Post-Workshop", "n", "%"))
# How could I make a table that is more clear to show ability pre vs. confidence post?
# Should I break it down by each computing task?
```

### Summary
Software Carpentry workshops improve learner skill, ability, and confidence in using computing tools like Python, Git, and the Unix shell. Additionally, respondents are satisfied with the caliber of workshop instructors and helpers. To close out this report, I offer a list of interesting questions that could be answered with this data, and encourage community members to get involved by using the data in this analysis to answer these questions:

* Are there differences in gender for intimidation, confidence, and/or motivation to use the tools post-workshop?
* Is there a relationship between respondent confidence and their motivation to use the tools post-workshop?
* Is there a relationship between respondent knowledge increase and their confidence and/or motivation post-workshop?
* Is there a relationship between respondent intimidation pre-workshop and their confidence and/or motivation to use the tools post-workshop?

What other questions can be answered from this data? Additionally, here are a few other questions that we can discuss as a community: 

* Why is SQL the least covered workshop topic?
* Has your confidence and/or motivation to use the tools we teach changed as a result of being a member of Software Carpentry's community? How? Why?