---
output:
  pdf_document: default
  html_document: default
---
## Analysis of the Carpentries Instructor Training Post-Workshop Survey Data
__Lead:__ [Kari L. Jordan](https://github.com/kariljordan)
__Published:__ September 10, 2018

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(likert)
library(NPS)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
opts_chunk$set(fig.path='instructor-training/figures/2018-') #puts all figures in figures folder
```


```{r include=FALSE}
# Load dataset
postdata <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/programmatic-assessment/instructor-training/data/20180908_post_clean.csv")
```

```{r}
# Function that makes a table of counts and percentages
# question_n is set by default to the number of trainees in the survey. This value may have to be set by question.
question_n <- nrow(postdata)

tally_and_perc <- function(df, colname, na.rm = FALSE, question_n){
  quo_colname <- enquo(colname)

  df %>%
    group_by(!!quo_colname) %>%
    tally() %>%
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>%
    mutate(`%` = round(n / question_n * 100, 1))
}

# function to compute number of non-NA responses to a question

n_responses_to_the_question <- function(df, from_colname, to_colname) {

  quo_from_colname <- enquo(from_colname)
  quo_to_colname <- enquo(to_colname)

  rowsums <-
df %>%
  select(UQ(quo_from_colname):UQ(quo_to_colname)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all behaviors
idx <- ifelse(rowsums == 0, FALSE, TRUE)
sum(idx)
}
```

This analysis of The Carpentries Instructor Training [post-workshop survey](https://github.com/carpentries/assessment/blob/2018-07-08-learners-pre-post-surveys.Rmd/programmatic-assessment/instructor-training/documents/instructor-training-post-survey-current.pdf) serves to offer recommendations for changes to curriculum and assessment of The Carpentries instructor training program.

There were a total XX trainees who completed this survey in between XX and XX.

### When are trainees completing the post instructor training survey?

```{r}
# When are you taking this survey?
when_taking = c("I have just completed the training, and am taking it at the event", "I have recently completed the training, and am taking it after I left the event")
when_taking = factor(when_taking)

postdata$WhenTaking = factor(postdata$WhenTaking, levels = when_taking)

postdata_when_taking_tally <-
  postdata %>%
  group_by(WhenTaking) %>%
  tally() %>%
  filter(!is.na(WhenTaking)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(postdata_when_taking_tally, format = 'markdown', row.names = NA, col.names = c("When are you taking the survey?", "n", "%"))
# Come back and fix table column headers
```

## Feedback about the overall training event.

We are interested to know how much of the information presented at Carpentries instructor training events is new. The following table shows that about XX of trainees fall into either some, about half, or most of the information being new to them.

```{r new_information}
# How much of the information presented at this training event was new to you?
newinfo = c("None of it", 
            "Some of it", 
            "About half of it", 
            "Most of it", 
            "Al of it")
newinfo = factor(newinfo)

postdata$NewInformation = factor(postdata$NewInformation, levels = newinfo)

postdata_newinfo_tally <-
  postdata %>%
  group_by(NewInformation) %>%
  tally() %>%
  filter(!is.na(NewInformation)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

#kable(postdata_newinfo_tally, format = 'markdown', col.names = c("How much information was new?", "n", "%"))
```

```{r new_information_presented}
ggplot(postdata_newinfo_tally,
       aes(NewInformation, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("New Information") +
  ylab("% Trainees") +
  ggtitle("New Information Trainees were Presented") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

Trainees were asked to rate their level of agreement about the following statements as it relates to the overall training event.

+ __Worth__: The training was worth my time.
+ __Recommend__: I would recommend this training to a friend/colleague.
+ __Material__: The material preented matched the description of the training event.
+ __LearnedSkills__: I learned skills that I will be able to use in my teaching.
+ __InformationReasonableTime__: The amount of information covered was reasonable for alloted time.
+ __AtmosphereWelcoming__: The overall atmosphere was welcoming.

```{r}
# Please give us some feedback about the overall training event.
# Subsetting a portion of the Likert items from InformationReasonableTime to Worth
myvars <- c("InformationReasonableTime", 
            "AtmosphereWelcoming", "LearnedSkills", "Material", "Recommend", "Worth") 
newdata <- postdata[myvars]            

cols_with_Agree <- map_lgl(newdata, ~`%in%`("Agree", .x))
newdata_agree <-  newdata[ , cols_with_Agree]

levels = c("Strongly Disagree",
   "Disagree",
   "Neither Agree nor Disagree",
   "Agree",
   "Strongly Agree")

 factorfunction <- function(newdata, factlevel){
  factor(newdata, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(newdata, 
              levels=factlevel)}

newdata_agree_likert <- likert(data.frame(lapply(newdata_agree, factor, levels, ordered=TRUE)))
```

```{r training_perception_heatmap}
#Heatmap
title <- "Perception of Instructor Training Impact"
plot(newdata_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
```

Trainees were asked how they perceived the pace of the training.

```{r}
# How did you perceive the pace of the training?
pace = c("Too slow", "Slightly slow", "Just right", "Slightly fast", "Too fast")
pace = factor(pace)

postdata$Pace = factor(postdata$Pace, levels = pace)

postdata_pace_tally <-
  postdata %>%
  group_by(Pace) %>%
  tally() %>%
  filter(!is.na(Pace)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

#kable(postdata_pace_tally, format = 'markdown', col.names = c("Training Pace", "n", "%"))
```

```{r training_pace}
ggplot(postdata_pace_tally,
       aes(Pace, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Pace") +
  ylab("% Trainees") +
  ggtitle("Trainees' Perception of Workshop Pace") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

Trainees were also asked to rate the balance of lecture to hands-on work.

```{r}
# How was the balance of lecture to hands-on work?
handson = c("Too much lecture", 
            "Slightly too much lecture", 
            "Balanced (lecture/hands-on)", 
            "Slightly too much hands-on", 
            "Too much hands-on")
handson = factor(handson)

postdata$HandsOn = factor(postdata$HandsOn, levels = handson)

postdata_handson_tally <-
  postdata %>%
  group_by(HandsOn) %>%
  tally() %>%
  filter(!is.na(HandsOn)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

#kable(postdata_handson_tally, format = 'markdown', col.names = c("Balance of Lecture to Hands-On", "n", "%"))
```

```{r training_balance_of_lecture}
ggplot(postdata_handson_tally,
       aes(HandsOn, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Balance of Lecture") +
  ylab("% Trainees") +
  ggtitle("Trainees' Perception of Workshop: \nBalance of Lecture vs. Hands-On") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

## About the Instructors and Helpers

Trainees were asked to select how they felt the instructor trainers(s) performed based on the following:

+ __Enthusiastic__: Instructor trainer(s) were enthusiastic.
+ __Considerate__: Instructor trainer(s) were considerate.
+ __Communicators__: Instructor trainer(s) were good communicators.
+ __ClearAnswers__: Instructor trainer(s) gave clear answers to your questions.

```{r}
# Please select how you felt the instructor trainers(s) performed.
# Code chunk for likert plot (perception of workshop instructors/helpers)
ordered_often <-
  c("Never", "Rarely", "Sometimes", "Often", "All of the time")

# Trainers
likert_cols_often_Train <- 
 postdata %>% 
   select(grep("Trainers", names(.))) %>% 
   mutate_if(is.character, as.factor) %>% 
   mutate_all(funs(fct_relevel(., ordered_often))) %>% 
   filter_all(all_vars(!is.na(.)))

names(likert_cols_often_Train) <- 
  gsub("Trainers", "", names(likert_cols_often_Train))
  
lc_often_train <- likert(data.frame(likert_cols_often_Train))
```

```{r perception_trainers_performance}
#Heatmap
title <- "Perception of How Instructor Trainers Performed"
plot(lc_often_train, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
```


Trainees were asked to describe their knowledge with the following topics after the training, and their change in motivation to learn these topics. The topics are as follows:

+ __Assessment__: Formative vs. summative assessment
+ __Carpentries__: What the Carpentries are and what they do
+ __CognitiveLoad__: Cognitive load
+ __Feedback__: Giving effective feedback
+ __Memory__: How human memory works
+ __Motivation__: Strategies to motivate learners
+ __Novice__: What makes someone a novice or expert

```{r}
knowledge <-
    c("Little or no knowledge of topic",
    "Some knowledge of topic",
    "Extensive knowledge of topic")

motivation <- 
  c("Less motivated", 
    "Slightly less motivated", 
    "No change in motication", 
    "More motivated",
    "Much more motivated")

# Compute for all tools.

# Knowledge
knowledge_post <- 
postdata %>%
  select(contains("Knowledge")) %>% 
  gather() %>%
  count(key, value) %>%
  group_by(key) %>%
  mutate(`%` = n/sum(n) * 100 ) %>%
  ungroup() %>% 
  filter(value %in% knowledge) %>% 
  mutate(key = gsub("Knowledge", "", key))


# Motivation
motivation_post <- 
postdata %>%
  select(contains("Motivation")) %>% 
  gather() %>%
  count(key, value) %>%
  group_by(key) %>%
  mutate(`%` = n/sum(n) * 100 ) %>%
  ungroup() %>%
  filter(value %in% motivation) %>% 
  mutate(key = gsub("Motivation", "", key))
```

```{r knowledge_plot}
# Plot as two grouped bar plots, then combine.
knowledge_post <- 
   ggplot(knowledge_post, 
         aes(x = key,
             y = `%`,
             fill = fct_relevel(value, 
                             knowledge))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Trainees") +
    ggtitle("Knowledge of topics after training") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) +
  guides(fill = guide_legend(nrow = 2)) # wraps legend
```

```{r motivation_plot}
# Plot as two grouped bar plots, then combine.
motivation_post <- 
   ggplot(knowledge_post, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (experience_pre))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Trainees") +
    ggtitle("Knowledge of topics after training") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) +
  guides(fill = guide_legend(nrow = 2)) # wraps legend
```

```{r knowledge_motivation_comparison}
# put the two plots together
library(gridExtra)
grid.arrange(knowledge_post, 
             motivation_post,
             ncol = 1)
```

## Ability to apply Carpentries teaching practices

Trainees were asked to describe their ability to do the following tasks:

+ __ConceptMaps__: Use a concept map for lesson planning 
+ __Learning Objectives__: Write effective learning objectives
+ __LiveCoding__: Teach using live coding  
+ __MCQ__: Write a multiple choice question with diagnostic power 
+ __Website__: Set up a workshop website  
 
These tasks are core to The Carpentries teaching practices, and were taught during instructor training.

```{r}
ability <-
    c("Not at all able",
    "Slightly able",
    "Neutral",
    "Moderately able",
    "Extremely able")


# Ability
task_ability <- 
postdata %>%
  select(contains("PostAbility")) %>% 
  gather() %>%
  count(key, value) %>%
  group_by(key) %>%
  mutate(`%` = n/sum(n) * 100 ) %>%
  ungroup() %>% 
  filter(value %in% ability) %>% 
  mutate(key = gsub("PostAbility", "", key))
```

```{r}
 ggplot(task_ability, 
         aes(x = key,
             y = `%`,
             fill = fct_rev(fct_relevel(value, 
                             (ability))))) +
    geom_col(position = "dodge") +
    geom_text(aes(label=n), 
              size= 4, vjust=-0.25,
              position=position_dodge(width=1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% Trainees") +
    ggtitle("Knowledge of topics after training") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14) +
    theme(legend.position = "bottom", 
          legend.title=element_blank()) +
  guides(fill = guide_legend(nrow = 2)) # wraps legend
```

Trainees were asked if they have a clear understanding of what needs to be done to complete instructor training.

```{r}
# Do you have a clearn understanding of what needs to be done to complete instructor training?
checkout_factor = c("No, not clear at all", 
            "Could use some more details", 
            "Yes, I understand", 
            "Other (please specify")
checkout_factor = factor(checkout_factor)

postdata$CompleteTraining = factor(postdata$CompleteTraining, levels = checkout_factor)

checkout_tally <-
  postdata %>%
  group_by(CompleteTraining) %>%
  tally() %>%
  filter(!is.na(CompleteTraining)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

#kable(checkout_tally, format = 'markdown', col.names = c("Clear on Checkout Process?", "n", "%"))
```

```{r understanding_of_checkout}
ggplot(checkout_tally,
       aes(CompleteTraining, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Understanding of Checkout Process") +
  ylab("% Trainees") +
  ggtitle("Trainees' Understanding of Checkout Process") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

## Recommending Carpentries' Instructor Training

Trainees were asked how likely they are to recommend a Software and/or Data Carpentry workshop to a friend or colleague using the [Net Promoter Score](https://en.wikipedia.org/wiki/Net_Promoter). The scoring for this question based on a 0 to 10 scale. Trainees scoring from 0 to 6.4 are labeled *Detractors*, and are believed to be less likely to recommend a workshop. Those who respond with a score of 8.5 to 10 are called *Promoters*, and are considered likely to recommend a workshop. Trainees between 6.5 and 8.4 are labeled *Passives*, and their behavior falls in the middle of Promoters and Detractors.

```{r}
nps <-
  postdata$LikelyToRecommend %>%
    npc(breaks = list(0:6, 7:8, 9:10)) %>%
    data.frame(category = .) %>%
    filter(!is.na(category)) %>%
    count(category) %>%
    mutate("%" = (n / sum(n))*100)

# kable(nps,format = 'markdown', colnames = c("Net Promoter Score", "n", "%"))
```

```{r}
data_recommend_tally <- 
  postdata %>% 
  group_by(LikelyToRecommend) %>% 
  tally() %>%
  filter(!is.na(LikelyToRecommend))
```

```{r likely_to_recommend}
ggplot(data_recommend_tally, 
       aes(`LikelyToRecommend`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="purple") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Likely to Recommend") +
  ylab("% Trainees") +
  ggtitle("Likely to Recommend") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```
