# Data Carpentry's Pilot Pre-Workshop Survey Summary Plots
__Author__: [Kari L. Jordan](https://github.com/kariljordan)   
__Revised__: October 2017

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(srvyr)
```
A [PDF](https://github.com/carpentries/assessment/blob/master/data-carpentry/preworkshop/2017-pilot/presurvey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the Data Carpentry [assessment](https://github.com/carpentries/assessment/tree/master/data-carpentry/preworkshop/2017-pilot) repo on GitHub. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.

```{r echo=FALSE}
data <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/data-carpentry/preworkshop/2017-pilot/20171020_data.csv")
```

```{r}
# Function that makes a table of counts and percentages
tally_and_perc <- function(df, colname, na.rm = FALSE){
  quo_colname <- enquo(colname)

  df %>% 
    group_by(!!quo_colname) %>% 
    tally() %>% 
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>% 
    mutate(`%` = round(n / sum(n) * 100, 1)) 
}
```

### Demographics
```{r}
# Code chunk for Status
status = c("Undergraduate student", "Graduate student", "Post-doc", "Faculty", "Industry", "Academic Research Staff", "Other (please specify)")
status = factor(status)

data$Status = factor(data$Status, levels = status)

data_status_tally <- 
  data %>% 
  group_by(Status) %>% 
  tally() %>% 
  filter(!is.na(Status)) 

ggplot(data_status_tally, 
       aes(Status, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Status") +
  ylab("% Respondents") +
  ggtitle("Majority of Respondents were Graduate Students") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/postworkshop_stats.png")

data %>% 
  tally_and_perc(`Status`, na.rm = TRUE) %>% 
  kable()
```

### Perception of Workshop Involvement & Practical Knowledge
```{r}
# Code chunk for Involvement
involvement = c("Somewhat involved", "Very involved", "Enthusiastically involved")
involvement = factor(involvement)

data$Involvement = factor(data$Involvement, levels = involvement)

data_involvement_tally <- 
  data %>% 
  group_by(Involvement) %>% 
  tally() %>% 
  filter(!is.na(Involvement)) 

ggplot(data_involvement_tally, 
       aes(Involvement, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Involvement") +
  ylab("% Respondents") +
  ggtitle("Majority of Respondents were very involved in the workshop") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/postworkshop_involvement.png")

data %>% 
  tally_and_perc(`Involvement`, na.rm = TRUE) %>% 
  kable()
```

```{r}
# Code chunk for Practical Knowledge
practical_knowledge = c("A great deal", "Some practical knowledge", "None")
practical_knowledge = factor(practical_knowledge)

data$`Practical-Knowledge` = factor(data$`Practical-Knowledge`, levels = practical_knowledge)

data_practical_knowledge_tally <- 
  data %>% 
  group_by(`Practical-Knowledge`) %>% 
  tally() %>% 
  filter(!is.na(`Practical-Knowledge`)) 

ggplot(data_practical_knowledge_tally, 
       aes(`Practical-Knowledge`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Practical Knowledge") +
  ylab("% Respondents") +
  ggtitle("Majority of Respondents learned a great deal") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/postworkshop_knowledge.png")

data %>% 
  tally_and_perc(`Practical-Knowledge`, na.rm = TRUE) %>% 
  kable()
```

### Perception of Post-Workshop Skills
```{r}
#Subsetting a portion of the Likert items from Organize-Data to Use-command-line
myvars <- c("Organize-Data", "Use-OpenRefine", "Import-Python", "Import-R", "Visualizations-in-Python", "Visualizations-in-R", "Construct-SQL", "Use-command-line")
newdata <- data[myvars]

cols_with_Agree <- map_lgl(newdata, ~`%in%`("Agree", .x))
newdata_agree <-  newdata[ , cols_with_Agree]

levels = c("Strongly disagree",
   "Disagree",
   "Neutral",
   "Agree",
   "Strongly Agree",
   "NA/Not covered at this workshop")

 factorfunction <- function(newdata, factlevel){
  factor(newdata, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(newdata, 
              levels=factlevel)}

newdata_agree_likert <- likert(data.frame(lapply(newdata_agree, factor, levels, ordered=TRUE)))

#Likert plot
title <- "Post-workshop: Better understanding of how to..."
 theme_update(plot.title = element_text(hjust = 0.5))
plot(newdata_agree_likert) + ggtitle(title) 
ggsave("figures/postworkshop_perception_likert.png")

#Heatmap
title <- "Perception of Workshop Impact"
plot(newdata_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
ggsave("figures/postworkshop_perception_heat.png")
```

### Perception of Workshop Overall
```{r}
#Subsetting a portion of the Likert items from Application to Recommend
newvars <- c("Application", "Worth-My-Time", "Material", "Recommend")
newdata2 <- data[newvars]

cols_with_Agree <- map_lgl(newdata2, ~`%in%`("Agree", .x))
newdata2_agree <-  newdata2[ , cols_with_Agree]

levels = c("Strongly disagree",
   "Disagree",
   "Neutral",
   "Agree",
   "Strongly Agree")

 factorfunction <- function(newdata2, factlevel){
  factor(newdata2, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(newdata2, 
              levels=factlevel)}

newdata2_agree_likert <- likert(data.frame(lapply(newdata2_agree, factor, levels, ordered=TRUE)))

#Likert plot
title <- "Perception of Workshop Overall"
 theme_update(plot.title = element_text(hjust = 0.5))
plot(newdata2_agree_likert) + ggtitle(title) 
ggsave("figures/postworkshop_overallperception_likert.png")

#Heatmap
title <- "Perception of Workshop Overall"
plot(newdata2_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
ggsave("figures/postworkshop_overallperception_heat.png")
```

### Perception of Workshop Instructors
```{r}
#Subsetting a portion of the Likert items from Instructors-Clear-Answers to Instructors-Enthusiastic
updatedvars <- c("Instructors-Clear-Answers", "Instructors-Considerate", "Instructors-Effective", "Instructors-Enthusiastic")
newdata3 <- data[updatedvars]

cols_with_Agree <- map_lgl(newdata3, ~`%in%`("Always", .x))
newdata3_agree <-  newdata3[ , cols_with_Agree]

levels = c("Never",
   "Sometimes",
   "Usually",
   "Most of the time",
   "Always")

 factorfunction <- function(newdata3, factlevel){
  factor(newdata3, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(newdata3, 
              levels=factlevel)}

newdata3_agree_likert <- likert(data.frame(lapply(newdata3_agree, factor, levels, ordered=TRUE)))

#Likert
title <- "Perception of Workshop Instructors"
 theme_update(plot.title = element_text(hjust = 0.5))
plot(newdata3_agree_likert) + ggtitle(title) 
ggsave("figures/postworkshop_instructors_likert.png")

#Heatmap
title <- "Perception of Workshop Instructors"
plot(newdata3_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
ggsave("figures/postworkshop_instructors_heat.png")
```