## Analysis of the Carpentries Instructor Training Post-Workshop Survey
__Lead:__ [Kari L. Jordan](https://github.com/kariljordan)

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(likert)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
opts_chunk$set(fig.path='figures/2018_') #puts all figures in figures folder
```


```{r include=FALSE}
# Load dataset
postdata <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/programmatic-assessment/instructor-training/analyses/post-workshop/2018/2018-03-01_data.csv")

```

```{r}
# Function that makes a table of counts and percentages
# question_n is set by default to the number of respondents in the survey. This value may have to be set by question.
question_n <- nrow(postdata)

tally_and_perc <- function(df, colname, na.rm = FALSE, question_n){
  quo_colname <- enquo(colname)

  df %>%
    group_by(!!quo_colname) %>%
    tally() %>%
    filter(if_else(rep(na.rm, nrow(.)),
                  !is.na(!!quo_colname),
                  as.logical(rep(1, nrow(.))))) %>%
    mutate(`%` = round(n / question_n * 100, 1))
}

# function to compute number of non-NA responses to a question

n_responses_to_the_question <- function(df, from_colname, to_colname) {

  quo_from_colname <- enquo(from_colname)
  quo_to_colname <- enquo(to_colname)

  rowsums <-
df %>%
  select(UQ(quo_from_colname):UQ(quo_to_colname)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all behaviors
idx <- ifelse(rowsums == 0, FALSE, TRUE)
sum(idx)
}
```

This analysis of The Carpentries Instructor Training [post-workshop survey](https://github.com/carpentries/assessment/blob/master/programmatic-assessment/instructor-training/surveys/current_survey.pdf) serves to offer recommendations for changes to curriculum and assessment of our instructor training program.

There were a total 573 trainees who completed this survey in between 2016 and 2018.

## When are respondents completing the post-workshop survey?

When are you taking this survey?

```{r}
# When are you taking this survey?
when_taking = c("I have just completed the training, and am taking it at the event", "I have recently completed the training, and am taking it after I left the event")
when_taking = factor(when_taking)

postdata$`When-Taking` = factor(postdata$`When-Taking`, levels = when_taking)

postdata_when_taking_tally <-
  postdata %>%
  group_by(`When-Taking`) %>%
  tally() %>%
  filter(!is.na(`When-Taking`)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(postdata_when_taking_tally)
```
### Demographics

__Respondents Position__

What is your current position?

```{r trainees_position}
# What is your current position?
position = c("Undergraduate Student", "Graduate Student", "Post-doctoral researcher", "Faculty", "Research staff (including research programmer", "Support staff (including technical support)", "Librarian/archivist", "Commercial software developer", "Other (please specify)")
position = factor(position)

postdata$Position = factor(postdata$Position, levels = position)

postdata_position_tally <-
  postdata %>%
  group_by(Position) %>%
  tally() %>%
  filter(!is.na(Position)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

ggplot(postdata_position_tally,
       aes(Position, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4, vjust=-0.25) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Respondents' Position") +
  ylab("% Respondents") +
  ggtitle("Breakdown of Instructor Trainees by Position") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

In the interest of improving diversity, we collect additional demographic information for U.S. participants. This information is completely voluntary.

__How would you describe yourself?__

```{r}
# How would you describe yourself?
race = c("American Indian or Alaska Native",
"Asian",
"Black or African American",
"Hispanic or Latino(a)",
"Native Hawaiian or Other Pacific Islander",
"White",
"Prefer not to say",
"Multiple ethnicity / Other (please specify)")
race = factor(race)

postdata$Race = factor(postdata$Race, levels = race)

postdata_race_tally <-
  postdata %>%
  group_by(Race) %>%
  tally() %>%
  filter(!is.na(Race)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(postdata_race_tally)
```

__What is your gender?__

```{r}
# What is your gender?
gender = c("Female", "Male", "Other", "Prefer not to say")
gender = factor(gender)

postdata$Gender = factor(postdata$Gender, levels = gender)

postdata_gender_tally <-
  postdata %>%
  group_by(Gender) %>%
  tally() %>%
  filter(!is.na(Gender)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(postdata_gender_tally)
```

__Domain of research/study__

What is your downain of research/study?

```{r}
# What is your downain of research/study? 
# Responses are in columns 'Domain' through 'Column63'

n_responses_to_domain_question <-
  n_responses_to_the_question(postdata,
                              from_colname = Domain,
                              to_colname = Column63)

domain_perc <-
postdata %>%
  select(Domain:Column63) %>%
  gather(col, domain_perc) %>%
  group_by(domain_perc) %>%
  tally_and_perc(domain_perc,
                 na.rm = TRUE,
                 question_n = n_responses_to_domain_question) %>%
  filter(!is.na(domain_perc)) %>%
  arrange(desc(n)) %>%
  rename(Domain = domain_perc)

kable(domain_perc,
      format = "markdown",
      digits = getOption("digits"),
      row.names = NA,
      col.names = NA,
    caption = NULL,
    escape = TRUE)
```

__Feedback about the overall training event.__
Respondents were asked to rate their level of agreement about the following:

+ The amount of information covered was reasonable for alloted time.
+ The overall atmosphere was welcoming.
+ I learned skills that I will be able to use in my teaching.
+ The material preented matched the description of the training event.
+ I would recommend this training to a friend/colleague.
+ The training was worth my time.

```{r training_perception}
# Please give us some feedback about the overall training event.
cols_with_Agree <- map_lgl(round2data, ~`%in%`("Agree", .x))
data_agree <-  round2data[ , cols_with_Agree]

levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

# Beth's tip to both order the factors based on levels and unify the factors
 factorfunction <- function(mydata, factlevel){
  factor(mydata,
         levels=factlevel,
         ordered = TRUE)
    fct_unify(mydata,
              levels=factlevel)}
 # End tip

 # Adjusting names of y axis labels
 names(data_agree) <-
  c("Coding",
    "Confidence",
    "Career",
    "Motivation",
    "Reproducible",
    "Productivity",
    "Recognition")

data_agree_likert <- likert(data.frame(lapply(data_agree, factor, levels, ordered=TRUE)))

agree_or_strongly_agree_improved_3_things <-
  data_agree %>%
  select(Coding, Reproducible, Productivity) %>%
  filter(Coding       %in% c("Agree", "Strongly agree") | # or
         Reproducible %in% c("Agree", "Strongly agree") |
         Productivity %in% c("Agree", "Strongly agree"))

perc_agree_or_strongly_agree_improved_3_things <-
  round(nrow(agree_or_strongly_agree_improved_3_things) / nrow(data_agree) * 100, 0)

received_professional_recognition <-
  data_agree_likert$results %>%
  filter(Item == "Recognition") %>%
  select(Agree, `Strongly agree`) %>%
  sum() %>%
  round(0)

title <- "Figure: Perception of Workshop Impact"
plot(data_agree_likert, type =c("heat"), panel.arrange = NULL, panel.strip.color = "red", legend.position = "bottom") + ggtitle(title)
```




```{r include=FALSE}
# Last Carpentries workshop attended
workshop_attended = c("Data Carpentry", "Library Carpentry", "Software Carpentry", "I don't know.")
workshop_attended = factor(workshop_attended)

round2data$WhichCarpentry = factor(round2data$WhichCarpentry, levels = workshop_attended)

 round2data_workshop_attended_tally <-
  round2data %>%
  group_by(`WhichCarpentry`) %>%
  tally() %>%
  filter(!is.na(`WhichCarpentry`)) %>%
  mutate(perc = round(n/sum(n) * 100, 0))

kable(round2data_workshop_attended_tally)
```

# Workshop Content

__What content was covered at the last Carpentries workshop you completed? Select all that apply.__
```{r}
# What content was covered
# Responses are in columns 'ContentCovered' through 'Column23'
# Ben's tip to use 'gather' to go from wide to long format
workshop_tools <-
 round2data %>%
 select(`ContentCovered`:Column23) %>%
 gather(col, workshop_tools) %>%
 group_by(workshop_tools) %>%
 tally() %>%
 filter(!is.na(workshop_tools)) %>%
 arrange(desc(n)) %>%
 rename(`ContentCovered` = workshop_tools)

# Use the line below to provide a table of the tools covered.
# Respondents were asked to check all that apply.
kable(workshop_tools, caption = "Tools Covered")

# Ben's tip to use in-line text
# This code produces results to use in the text of the report
Git <- workshop_tools[workshop_tools$Content == 'Git', ]$n
Python <- workshop_tools[workshop_tools$Content == 'Python', ]$n
Unix_Shell <- workshop_tools[workshop_tools$Content == 'Unix Shell', ]$n
R <- workshop_tools[workshop_tools$Content == 'R', ]$n
SQL <- workshop_tools[workshop_tools$Content == 'SQL', ]$n
OpenRefine <- workshop_tools[workshop_tools$Content == 'OpenRefine', ]$n
Spreadsheets <- workshop_tools[workshop_tools$Content == 'Spreadsheets', ]$n
Cloud_Computing <- workshop_tools[workshop_tools$Content == 'Cloud Computing', ]$n
MATLAB <-  workshop_tools[workshop_tools$Content == 'MATLAB', ]$n
Mercurial <-  workshop_tools[workshop_tools$Content == 'Mercurial', ]$n
```

__Combination of tools covered in respondents' workshops.__

```{r}
# The code segment below from Ben Marwick will show the most combinations of tools covered in our workshops.

n_responses_to_tools_question <-
  n_responses_to_the_question(round2data,
                              from_colname = ContentCovered,
                              to_colname = Column23)

tools_cols <-
round2data %>%
  select(ContentCovered:Column23)

list_of_tools_per_person <- list()
for(i in seq_len(nrow(tools_cols))) {
  ii <- quo(i)

  list_of_tools_per_person[[i]] <-
  tools_cols %>%
    slice(!!ii) %>%
          c(., recursive=TRUE) %>%
          unname %>%
    na.omit() %>%
    as.vector()
}

# The code segment below from Ben Marwick will get the tally of combinations of tools and produce a table.
tool_combs <-
purrr::map_chr(list_of_tools_per_person,
               ~paste0(.x, collapse = " "))

tool_combs_df <-
tool_combs %>%
  as_data_frame() %>%
  group_by(value) %>%
  tally() %>%
  mutate(`%` = round(n / sum(n) * 100, 1)) %>%
  arrange(desc(n)) %>%
  filter(value != "")

# Top combinations as entered by respondants
colnames <- c("Frequency of Tools Covered", "n", "%")
kable(tool_combs_df[1:10, ], row.names = NA, col.names = colnames, caption = "Combination of Tools Covered")
```

__Matrix of combinations of tools covered.__

```{r}
# The code segment below from Ben Marwick will give a matrix of the combinations of tools covered.
m <- as.matrix(tools_cols)
# The unique values in the matrix
vals <- sort(unique(as.vector(m)))

# Rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# Count the co-occurences of each value (diagonal is total number of rows with that value)
tool_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(tool_co_occurences, row.names = TRUE, caption = "Matrix of Common Tools Covered")
```

# Workshop Impact

__Behaviors Adopted__

Which of the following behaviors have you adopted as a result of completing a Carpentries workshop? Check all that apply.
```{r include = FALSE}
# Code for behaviors adopted
# Responses are in columns 'Behaviors-Adopted' through 'Column32'

# How many responses do we have to this question?

responses_to_behaviours <-
  n_responses_to_the_question(round2data,
                              from_colname = `Behaviors`,
                              to_colname = Column32)


# Use 'gather' to go from wide to long format
Behaviors_Adopted <-
round2data %>%
  select(`Behaviors`:Column32) %>%
  gather(col, Behaviors_Adopted) %>%
  group_by(Behaviors_Adopted) %>%
  tally_and_perc(Behaviors_Adopted,
                 na.rm = TRUE,
                 question_n = responses_to_behaviours) %>%
  filter(!is.na(Behaviors_Adopted)) %>%
  arrange(desc(n))

#  how many rate either of these three?
#- data management and project organization practices : Behaviors-Adopted
#- used programming languages for automation : Column28
#- used version control to manage code : Column30

relevant_cols <- c("Behaviors-Adopted", "Column28", "Column30")

rowsums <-
  round2data %>%
  select(one_of(relevant_cols)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# how many of these rows don't sum to zero?
idx <- ifelse(rowsums == 0, FALSE, TRUE)
number_that_adopted_any_of_those_three <- sum(idx)
```


```{r}
# Respondents were asked to check all that apply.
kable(Behaviors_Adopted,
      format = "markdown",
      digits = getOption("digits"),
      row.names = NA,
      col.names = NA,
      caption = NULL,
      format.args = list(),
      escape = TRUE)
```

## Behaviors by Group

```{r}
# Need the count of responses in each Status grouping in order to caluclate
# percentages in the next step
respondant_counts_by_group <- round2data %>%
  group_by(Status) %>%
  tally() %>%
  rename(group_sum = n)

# Calulate summary of numer of respondants selecting each bahavior by group
# Uses a join to the respondant_counts_by_group tibble in order to calulate
# persentages
behaviors_adopted_by_group <- round2data %>%
  select(Status, Behaviors:Column32) %>%
  gather(col, Behaviors_Adopted, -Status) %>%
  group_by(Behaviors_Adopted, Status) %>%
  select(-col) %>%
  na.omit() %>%
  table() %>%
  as_tibble() %>%
  left_join(respondant_counts_by_group) %>%
  mutate(Percent = (n / group_sum) * 100) %>%
  select(Status, Behaviors_Adopted, Percent)

# Make a table but remove "Other" column beacuse it's full of NAs
behaviors_adopted_by_group %>%
  spread(Status, Percent) %>%
  select(-(starts_with("Other"))) %>%
  kable(format = "markdown",
        digits = 1,
        row.names = NA,
        col.names = NA,
        caption = NULL,
        format.args = list(),
        escape = TRUE)
```

```{r, fig.height=6}
# Remove other column since it's full of NAs
# Might take this out of final report, but it helps visualize differences
behaviors_adopted_by_group %>%
  filter(!grepl("Other", Status)) %>%
  ggplot(aes(x = Behaviors_Adopted,
             y = Status,
             fill = Percent)) +
    geom_tile() +
    geom_text(aes(label = paste0(round(Percent, 1), "%"))) +
    scale_fill_gradient("Percent",
                        low = "white",
                        high = "blue",
                        limits = c(0, 100)) +
    ggtitle("Figure 4: Behaviors Adopted by Group (percent of respondants)") +
    theme(axis.text.x = element_text(angle = 45,
                                     hjust = 1),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_blank(),
          panel.background = element_blank())
```


# Programming Usage Pre- and Post-Workshop

__Before completing a Carpentries workshop, how often did you use programming languages (R, Python, etc.), databases (Access, SQL, etc.), version control software and/or the shell?__

```{r}
# The code below can be used to get a table and plot of the number of respondents for programming usage pre workshop
# Naupaka's tip so pre- and post-responses match
round2data_paired_plot <- round2data
levels(round2data$`ProgrammingBefore`)[2] <- "I have not been using tools like these."

# Programming Usage Pre-Carpentry Workshop [Absolute Plot]
programming = c("I had not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
programming = factor(programming)

  round2data_usage_tally <-
   round2data %>%
   group_by(`ProgrammingBefore`) %>%
   tally() %>%
   filter(!is.na(`ProgrammingBefore`))

  kable(round2data_usage_tally, caption = "")

  ggplot(round2data_usage_tally,
        aes(`ProgrammingBefore`, n)) +
   geom_bar(stat = "identity", fill="grey") +
   geom_text(aes(label=n), size= 4, vjust=-0.25) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Programming Usage Pre-Workshop [Absolute]") +
   ylab("# Respondents") +
   ggtitle("Figure 5: Programming Usage Pre-Workshop") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_classic(base_size = 14)
ggsave("figures/programming_usage_pre_absolute.png")
# Why aren't the levels showing in the correct order on the plot?
```


```{r}
# The code below is for pre-workshop programming usage reported as a percentage.
# Programming Pre-Carpentry Workshop [Percentage Plot]
 round2data %>%
  select(`ProgrammingBefore`) %>%
   group_by(`ProgrammingBefore`) %>%
   tally() %>%
   filter(!is.na(`ProgrammingBefore`)) %>%
   mutate(`ProgrammingBefore` =     factor(`ProgrammingBefore`, levels = programming)) %>%
   ggplot(aes(x = `ProgrammingBefore`, y = 100 * (n/sum(n)))) +
     geom_bar(stat = "identity", position = "dodge", fill = "grey") +
     geom_text(aes(label=n), size= 4, vjust=-0.25) +
     scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                          width = 10,
                                                          simplify = FALSE),
                                                  paste,
                                                  collapse = "\n")) +
     theme_classic() +
     xlab("Programming Usage Pre-Workshop [%]") +
     ylab("% respondents") +
     ggtitle("Figure 6: Programming Usage Pre-Workshop") +
     theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
ggsave("figures/programming_usage_pre_percent.png")
```

__Since completing a Carpentries workshop, how often do you currently use programming languages (R, Python, etc.), databases (Access, SQL, etc.), version control software and/or the shell?__

```{r}
# The code below is for post-workshop programming usage (count)
# Programming Usage Post-Carpentry Workshop [Absolute Plot]
  programming = c("I have not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
  programming = factor(programming)

 round2data$`ProgrammingSince` = factor(round2data$`ProgrammingSince`, levels = programming)

  round2data_usage_tally <-
   round2data %>%
   group_by(`ProgrammingSince`) %>%
   tally() %>%
   filter(!is.na(`ProgrammingSince`))

 kable(round2data_usage_tally)

  ggplot(round2data_usage_tally,
        aes(`ProgrammingSince`, n)) +
   geom_bar(stat = "identity", fill="grey") +
   geom_text(aes(label=n), size= 4, vjust=-0.25) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Programming Usage Post-Workshop [Absolute]") +
   ylab("# Respondents") +
   ggtitle("Figure 7: Programming Usage Post-Workshop") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_classic(base_size = 14)
ggsave("figures/programming_usage_post_absolute.png")
```

```{r}
# The code below is for post-workshop programming usage as a percent
#Programming Usage Post-Carpentry Workshop [Percentage Plot]
round2data %>%
select(`ProgrammingSince`) %>%
group_by(`ProgrammingSince`) %>%
tally() %>%
filter(!is.na(`ProgrammingSince`)) %>%
mutate(`ProgrammingSince` = factor(`ProgrammingSince`, levels = programming)) %>%
ggplot(aes(x = `ProgrammingSince`, y = 100 * (n/sum(n)))) +
geom_bar(stat = "identity", position = "dodge", fill = "grey", na.rm = TRUE ) +
geom_text(aes(label=n), size= 4, vjust=-0.25) + # Adds count to top of bar
scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("Programming Usage Post-Workshop") +
    ylab("% respondents") +
    ggtitle("Figure 8: Programming Usage Post-Workshop") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
ggsave("figures/programming_usage_post_percent.png")
```

__Comparing pre/post programming usage__

```{r}
# The code below is for Pre/Post plots of programming usage
# It includes tips from Ben and Naupaka
# Make the unique values the same
round2data$`ProgrammingBefore` <-
  gsub("I had not been using tools like these.",
       "I have not been using tools like these.",
       round2data$`ProgrammingBefore`)

round2data$`ProgrammingBefore` <-
  factor(round2data$`ProgrammingBefore`,
         levels = programming)

pre_and_post_usage <-
round2data %>%
  select(`ProgrammingBefore`,
          `ProgrammingSince`) %>%
  gather() %>%
  group_by(key, value) %>%
  tally() %>%
  mutate( perc = 100 * (n/sum(n))) %>%
  filter(!is.na(key),
         !is.na(value))

  ggplot(pre_and_post_usage,
         aes(x = factor(value,
                        levels = programming),
             y = perc,
             fill = key)) +
    geom_bar(stat = "identity",
             position = "dodge") +
    geom_text(aes(label=n), size= 4, vjust=-0.25, position = position_dodge(width = 1)) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("Figure 9: Respondents' Programming Usage Increased") +
    ylab("% Respondents") +
    scale_fill_discrete(name = "",
                        labels = c("Before Workshop", "After Workshop")) +
    ggtitle("") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
ggsave("figures/change_in_programming_usage.png")
```

## Pre-post programming usage by group

```{r, fig.height=14}
# The code below is for Pre/Post plots of programming usage
# It includes tips from Ben and Naupaka
# Make the unique values the same
pre_and_post_usage_by_group <-
  round2data %>%
  select(Status,
         ProgrammingBefore,
         ProgrammingSince) %>%
  gather(key = "when",
         value = "value",
         -Status) %>%
  group_by(Status, when, value) %>%
  tally() %>%
  mutate(percent = 100 * (n / sum(n))) %>%
  filter(!is.na(when),
         !is.na(value))

ggplot(pre_and_post_usage_by_group,
       aes(x = factor(value,
                      levels = programming),
           y = percent,
           fill = when)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  geom_text(aes(label = n),
            size = 4,
            vjust = -0.25,
            position = position_dodge(width = 1)) +
  ylim(c(0, 60)) +
  facet_wrap(~ Status, ncol = 1) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                       width = 10,
                                                       simplify = FALSE),
                                               paste,
                                               collapse = "\n")) +
  theme_classic() +
  xlab("Figure 10: Respondents' Programming Usage Increased (Grouped)") +
  ylab("% Respondents (actual counts above bars)") +
  scale_fill_discrete(name = "",
                      labels = c("Before Workshop", "After Workshop")) +
  ggtitle("Figure 10: Programming Usage Pre/Post by Status") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
ggsave("figures/change_in_programming_usage_by_group.png")
```




# Workshop Impact

__Change in Confidence__

How would you rate your change in confidence in the tools that were covered during your Carpentries workshops compared to before the workshop?

```{r}
# Code for change in confidence
confidence <-
  c("I'm less confident now.",
    "I'm equally confident now.",
    "I'm more confident now.")
confidence = factor(confidence)

round1data$`Change-In-Confidence` = factor(round1data$`Change-In-Confidence`, levels = confidence)

data_change.in.confidence_tally <-
  round1data %>%
  group_by(`Change-In-Confidence`) %>%
  tally() %>%
  filter(!is.na(`Change-In-Confidence`)) %>%
  mutate(perc = round(n / sum(n) * 100, 0 ))

# Use the code below for a table of the data.
# kable(data_change.in.confidence_tally, format = "markdown", row.names = FALSE, col.names = c("Change in Confidence", "%"))

ggplot(data_change.in.confidence_tally,
       aes(`Change-In-Confidence`, y = 100 * (n/sum(n)),
           n)) +
   geom_bar(stat = "identity", fill = "grey") +
   geom_text(aes(label=n), size= 4, vjust=-0.25) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Change in Confidence") +
   ylab("% Respondents") +
   ggtitle("Figure 12: Change in Confidence 6 Months Later") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_bw(base_size = 14)
ggsave("figures/change_in_confidence.png")
```

__Change in Confidence by Status__

```{r include=FALSE}
status <- unique(round1data$Position)
status <- factor(status[!is.na(status)])
```



```{r}
# What is your position?
status <- factor(status, levels(status)[c(7, 3, 6, 2, 1, 5, 4)])
# Display ordering.
print(levels(status))

round1data$Position <-
  factor(round1data$Position, levels = levels(status))

change_in_confidence_by_status <- round1data %>%
  group_by(`Change-In-Confidence`, Position) %>%
  tally() %>%
  filter(!is.na(`Change-In-Confidence`)) %>%
  group_by(Position) %>%
  mutate(n_status = sum(n)) %>%
  filter(!is.na(Position)) %>%
  mutate(perc = n / n_status * 100)

# Check that percentage total is 100 for each status (Position).
test_output <- change_in_confidence_by_status %>%
  group_by(Position) %>%
  summarize(total = sum(perc))
expect_equal(test_output$total, rep(100, length(status)))

ggplot(data = change_in_confidence_by_status,
       aes(x = `Change-In-Confidence`, y = Position)) +
  geom_tile(aes(fill = perc), colour = "white") +
  geom_text(aes(label = paste0(round(perc, 1), "%"))) +
  scale_fill_gradient("Percent",
                      low = "white",
                      high = "blue",
                      limits = c(0, 100)) +
  xlab("Change in Confidence") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_blank()
  )

ggsave("figures/change_in_confidence_by_status.png")
```


```{r}
# Focus on Engineering
change_in_conf_eng <- round1data %>%
  filter(grepl("Engineering", Column6)) %>%
  group_by(`Change-In-Confidence`) %>%
  tally() %>%
  filter(!is.na(`Change-In-Confidence`)) %>%
  mutate(perc = n / sum(n) * 100)

ggplot(change_in_conf_eng,
       aes(`Change-In-Confidence`, y = perc, n)) +
   geom_bar(stat = "identity", fill = "grey") +
   geom_text(aes(label=n), size= 4, vjust=-0.25) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10,
                                                        simplify = FALSE), paste,
                                                collapse="\n")) +
   theme_classic() +
   xlab("Change in Confidence (Engineering)") +
   ylab("% Respondents") +
   ggtitle("") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_bw(base_size = 14)
ggsave("figures/change_in_confidence_eng.png")
```

```{r include=FALSE}
# Breakdown by status.
change_in_conf_eng_by_status <- round1data %>%
  filter(grepl("Engineering", Column6)) %>%
  group_by(`Change-In-Confidence`, Position) %>%
  tally() %>%
  filter(!is.na(`Change-In-Confidence`)) %>%
  group_by(Position) %>%
  mutate(n_status = sum(n)) %>%
  filter(!is.na(Position)) %>%
  mutate(perc = n / n_status * 100)

# Check that percentage total is 100 for each status (Position).
test_output <- change_in_conf_eng_by_status %>%
  group_by(Position) %>%
  summarize(total = sum(perc))
expect_equal(test_output$total, rep(100, length(status)))

ggplot(data = change_in_conf_eng_by_status,
       aes(x = `Change-In-Confidence`, y = Position)) +
  geom_tile(aes(fill = perc), colour = "white") +
  geom_text(aes(label = n)) +
  scale_fill_gradient("Percent",
                      low = "white",
                      high = "blue",
                      limits = c(0, 100)) +
  xlab("Change in Confidence (Engineering)") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_blank()
  )
ggsave("figures/change_in_conf_eng_by_status.png")
```

# Usage of Tools for Research and/or Work
If you are using the tools you learned in a Carpentries workshop, how are they helping you? Check all that apply.

```{r}
# Data are in columns 'How-Tools-Learned-Help' through 'Column37'

# how many responses do we have to this question?

n_reponses_tools_learned_help <-
    n_responses_to_the_question(round2data,
                              from_colname = `HowToolsHelped`,
                              to_colname = Column37)

# How many responded to either of these?
# They are improving my overall efficienct : How.Tools.Learned.Helped
# They are improving my ability to analyze data. : Column34
# They are improving my ability to manage data. : Column35

relevant_cols <- c("HowToolsHelped", "Column34", "Column35")

rowsums <-
  round2data %>%
  select(one_of(relevant_cols)) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

idx <- ifelse(rowsums == 0, FALSE, TRUE)
number_that_tools_helped <- sum(idx)

how_help <-
round2data %>%
  select(`HowToolsHelped`:Column37) %>%
  gather(col, how_help) %>%
  group_by(how_help) %>%
  tally() %>%
  filter(!is.na(how_help)) %>%
  arrange(desc(n)) %>%
  rename(`HowToolsHelped` = how_help)

tools_helped <-
round2data %>%
  select(`HowToolsHelped`:Column37) %>%
  gather(col, tools_helped) %>%
  group_by(tools_helped) %>%
  tally_and_perc(tools_helped, na.rm = TRUE, question_n = n_reponses_tools_learned_help) %>%
  filter(!is.na(tools_helped)) %>%
  arrange(desc(n)) %>%
  rename(`How Tools Covered Have Helped` = tools_helped)
```

```{r}
kable(tools_helped,
      format = "markdown",
      row.names = FALSE,
      caption = "Self-Reported Perception of How Tools Help Respondents")
```

# Contributions to Academic Writing
Has completing a Carpentries workshop contributed to your writing of a research article, thesis, dissertation, or grant proposal?

```{r}
# Code chunk for contributions to academic writing

# how many responded to this question?
rowsums <-
round2data %>%
  select(`Writing`) %>%
  # check that each row has a value for at least one col
  # convert to numeric, if NA, then put a zero, otherwise 1
  map_df(., ~ifelse(is.na(.x), 0, 1)) %>%
  # sum to see if any rows have no reponses
  rowSums()

# for all writing responses
idx <- ifelse(rowsums == 0, FALSE, TRUE)
n_responsed_to_writing <-  sum(idx)

# table about writing
round2data %>%
  tally_and_perc(`Writing`,
                 na.rm = TRUE,
                 question_n = n_responsed_to_writing) %>%
  kable()


writing = c("No.", "Not sure.", "Yes.")
writing = factor(writing)

round2data$`Writing` = factor(round2data$`Writing`, levels = writing)
Contributed_Writing <- round(prop.table(table(round2data$`Writing`)) * 100)
```




# Breakdown of respondents by Country

__In what country was the workshop you attended held?__

```{r}
# Plot includes Ben's tip to add a percent column to the data_country_tally data frame
# before it goes into the ggplot() function to use reorder on that column name in the ggplot() function
# This plot uses round1data because we asked what Country they attended a workshop in that version of the
# survey
round1data_country_tally <-
round1data %>%
  group_by(Country) %>%
  tally(sort = TRUE) %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(Country)) %>%
  arrange(desc(n))

ggplot(round1data_country_tally,
       aes(reorder(Country, perc),
           perc)) +
  geom_bar(stat = "identity", fill = "grey") +
  theme_classic() +
  xlab("") +
  ylab("Figure X: Breakdown of Respondents by Country") +
  coord_flip() +
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw(base_size = 14)
ggsave("figures/percent_by_country.png")
```

# Respondent Demographics







```{r}
# Table of number of workshops that participants have attended
round2data %>% 
  filter(!is.na(NumWorkshops)) %>%
  select(NumWorkshops) %>%
  group_by(NumWorkshops) %>%
  tally() %>%
  kable(col.names = c("Number of Workshops Attended",
                      "n"), 
        caption = "Number of workshops attended (Post-survey)")
```

```{r}
# Table of time since workshop attendance
round2data %>% 
  filter(!is.na(TimeSinceWorkshop)) %>%
  select(TimeSinceWorkshop) %>%
  group_by(TimeSinceWorkshop) %>%
  tally() %>%
  kable(col.names = c("Time Since Last Attending Workshop",
                      "n"), 
        caption = "Time since workshop attendence (Post-survey)")
```

```{r}
table_of_status_by_field <- round2data %>%
  select(Status, Field:FieldOther) %>%
  gather(key = "Field",
         value = "value",
         -Status,
         na.rm = TRUE) %>%
  select(-Field) %>%
  table() %>%
  t()

top_12_fields <- table_of_status_by_field  %>%
  as_tibble() %>%
  group_by(value) %>%
  summarize(sum_by_field = sum(n)) %>%
  arrange(desc(sum_by_field)) %>%
  head(12) %>%
  pull(value)

# table of participant counts in each category (multiple selection was possible)
table_of_status_by_field %>%
  as_tibble() %>%
  filter(value %in% top_12_fields) %>%
  spread(Status, n) %>%
  kable()

# plot of the same
table_of_status_by_field %>%
  as_tibble() %>%
  filter(value %in% top_12_fields) %>%
  ggplot(aes(x = Status,
             y = value,
             fill = n)) +
    geom_tile() +
    geom_text(aes(label = round(n, 0))) +
    scale_fill_gradient("n",
                        low = "white",
                        high = "blue") +
    labs(title = "Number of Respondants by Field (top 12 most common) and Career Stage",
         subtitle = "Note: Multiple selections possible per person",
         y = "Field",
         x = "Career Stage/Status") +
    theme(axis.text.x = element_text(angle = 45,
                                     hjust = 1),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_blank(),
          panel.background = element_blank())

```


# Involvement in the Carpentries

Please indicate your involvement in the Carpentry community since completing a Carpentry workshop. Check all that apply.
```{r}
# Code for involvement (rows Involvement through Column57)
# I want to use the tally_and_perc function, but don't know where to put the question_n
Carpentry_Involvement <-
round2data %>%
  select(`Involvement`:Column57) %>%
  gather(col, Carpentry_Involvement) %>%
  group_by(Carpentry_Involvement) %>%
  tally() %>%
  filter(!is.na(Carpentry_Involvement)) %>%
  arrange(desc(n)) %>%
  rename(`Involvement Since Attending a Carpentry Workshop` = Carpentry_Involvement)
kable(Carpentry_Involvement)
```

__Matrix of involvement__

```{r}
# Code for matrix of involvement (thanks Ben for the tip!)
# Combinations of tools for individual
involvement_cols <-
round2data %>%
  select(`Involvement`:Column57)

# Matrix tool-by-tool

m <- as.matrix(involvement_cols)
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
involvement_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(involvement_co_occurences,
      row.names = TRUE,
      caption = "Matrix of Common Involvement")
```

# Continuous Learning

Which of the following learning activities (for data management and analysis) have you participated in since completing a Carpentry workshop? Check all that apply.
```{r}
# Code chunk for continuous learning

Learning_Activities <-
round2data %>%
  select(`ContinuousLearning`:Column63) %>%
  gather(col, Learning_Activities) %>%
  group_by(Learning_Activities) %>%
  tally() %>%
  filter(!is.na(Learning_Activities)) %>%
  mutate(`%` =round(n / sum(n) * 100, 0) ) %>%
  arrange(desc(n)) %>%
  rename(`Continuous Learning Post-Workshop` = Learning_Activities)

# Code chunk for table of continuous learning activities
kable(Learning_Activities,
      format = "markdown",
      row.names = FALSE,
      col.names = c("Continuous Learning", "n", "%"),
      caption = "Respondents Self-Reported Continuous Learning Activities")
```

__Matrix of continuous learning activities__
```{r}
# Code for matrix of continuous learning (thanks Ben for the tip!)
# Combinations of involvement for individual
learning_cols <-
round2data %>%
  select(`ContinuousLearning`:Column63)

# Matrix
m <- as.matrix(learning_cols)
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
learning_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(learning_co_occurences, row.names = TRUE, caption = "Matrix of Common Post-Workshop Learning Activities")
```

# Recommending Carpentries Workshops

__Have you recommended a Carpentry workshop to a friend or colleague?__
```{r}
# Code chunk for whether respondents recommended a workshop
recommended <-
round2data %>%
  select(Recommended) %>%
  gather(col, Recommended) %>%
  group_by(Recommended) %>%
  tally() %>%
  filter(!is.na(Recommended)) %>%
  mutate(`%` =round(n / sum(n) * 100, 0) ) %>%
  arrange(desc(n)) %>%
  rename(`Recommended a Workshop?` = Recommended)

# Table for responses of recommendations
kable(recommended)
```

# Other
```{r include=FALSE}
# If interested in seeing the open-ended responses for Position: Other, run this code.
round2data_field_other_tally <-
  round2data %>%
  group_by(`FieldOther`) %>%
  tally() %>%
  filter(!is.na(`FieldOther`))
kable(round2data_field_other_tally, format = "markdown", row.names = FALSE, col.names = c("Field-Other", "# Respondents"))
```

```{r include=FALSE}
# If interested in seeing the open-ended responses for Status: Other, run this code.
round2data_status_other_tally <-
  round2data %>%
  group_by(`StatusOther`) %>%
  tally() %>%
  filter(!is.na(`StatusOther`))
kable(round2data_status_other_tally, format = "markdown", row.names = FALSE, col.names = c("Status-Other", "# Respondents"))
```
