# Analysis of Carpentry Long-Term Feedback Survey
__Author__: [Kari L. Jordan](https://github.com/kariljordan)
__Published__: April 2017

THIS IS JUST A DRAFT

A [PDF](https://github.com/carpentries/public-survey-info/blob/master/documents/surveys/2017-04-17-carpentry-long-term-feedback-survey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the [public-survey-info](https://github.com/carpentries/public-survey-info) repo on GitHub. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.

```{r include=FALSE}
# install.packages("ggmap", type = "source")
# install.packages("likert")
# install.packages("purrr")
# install.packages("mapproj")
# install.packages("ggmap")
# install.packages("dplyr")
# install.packages("knitr")
library(dplyr)
library(likert)
library(purrr)
library(ggmap)
library(mapproj)
library(ggplot2)
library(knitr)
library(RColorBrewer)
display.brewer.all()
update.packages(repos = "https://cloud.r-project.org")
```
```{r echo=FALSE, purl=TRUE}
download.file("https://raw.githubusercontent.com/carpentries/public-survey-info/master/documents/reports/Carpentry-Reports/Long-Term-Feedback-Survey-Report/2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", "2017-04-17-carpentry-long-term-assessment-survey-data-public.csv")

data <- read.csv("2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", na.strings = "")
```
### Learner Demographics

```{r echo=FALSE}
table(data$Country)
```
```{r echo=FALSE}
data_country_tally <- 
  data %>% 
  group_by(Country) %>% 
  tally() %>% 
  filter(!is.na(Country)) %>% 
  arrange(desc(n))
# How do I change the color of just the South Africa bar?
ggplot(data_country_tally, 
       aes(reorder(Country, n),
           n)) +
  geom_bar(stat = "identity", fill = "orange") +
  theme_classic() +
  xlab("") +
  ylab("") +
  coord_flip() + 
  ggtitle("Carpentry Workshop Respondents by Country") +
  theme(plot.title = element_text(hjust = 0.5))
  theme_bw(base_size = 14)

# Naupaka said I can use ggplot(iris)+geom_bar(aes(Species,Petal.Width,fill=Species),stat="summary",fun.y="mean")# +scale_fill_manual(values=c("green","blue","blue")) to change the color of just one
#bar on the plot, but I can't figure out how right now.
```
A large portion of Carpentry learners responding to the survey attended a workshop in the United States.

What is the status of those responding?
```{r echo=FALSE}
table(data$Position)
```
```{r echo=FALSE}
data_position_tally <-
  data %>% 
  group_by(Position) %>% 
  tally() %>% 
  filter(!is.na(Position)) %>% 
  arrange(desc(n))

  ggplot(data_position_tally, 
       aes(reorder(Position, n),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("") +
  ylab("") +
  ggtitle("Self-Reported Status of Carpentry Learners") +
  theme(plot.title = element_text(hjust = 0.5))
  theme_classic(base_size = 14)
```
Majority graduate students.
```{r echo=FALSE}
table(data$Position.Other)
```
How many workshops have respondents attended?
```{r echo=FALSE}
table(data$How.Many.Workshops)
```
Behaviors Adopted Since Attending a Carpentry Workshop
```{r include=FALSE}
table(data$Behaviors.Adopted)
table(data$Column25)
table(data$Column26)
table(data$Column27)
table(data$Column28)
table(data$Column29)
table(data$Column30)
table(data$Column31)
table(data$Column32)
```

```{r echo=FALSE}
# This is an attempt to make a table of the count of behaviors adopted.
behaviors <- matrix(c(198,74,119,111,260,169,185,119,122),ncol=1,byrow=TRUE)
colnames(behaviors) <-("Behaviors Adopted Since Attending a Carpentry Workshop")
rownames(behaviors) <-c("Improving data management and project organization.",
                        "Developing a data management and analysis plan.",
                        "Using databases, scripts and queries to manage large data sets.",
                        "Transforming step-by-step workflows into scripts or functions.",
                        "Using programming languages like R or Python, or the command line to automate repetitive tasks.",
                        "Reusing code.",
                        "Using version control to manage code.",
                        "Using version control to collaborate online (in public or private repositories).",
                        "Sharing code or data publicly on places like GitHub or FigShare.")
behaviors <- as.table(behaviors)
behaviors
```
Programming Usage before a Carpentry Workshop
```{r echo=FALSE}
data_programming.usage.before.workshop_tally <- 
  data %>% 
  group_by(Programming.Usage.Before.Workshop) %>% 
  tally() %>% 
  filter(!is.na(Programming.Usage.Before.Workshop)) %>% 
  arrange(desc(n))

ggplot(data_programming.usage.before.workshop_tally, 
       aes(reorder(Programming.Usage.Before.Workshop, n),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("") +
  ylab("") +
  ggtitle("Learner's Programming Usage Before Attending a Carpentry Workshop") +
  theme(plot.title = element_text(hjust = 0.5))
  theme_bw(base_size = 14)
```
```{r echo=FALSE}
data_programming.usage.since.workshop_tally <- 
  data %>% 
  group_by(Programming.Usage.Since.Workshop) %>% 
  tally() %>% 
  filter(!is.na(Programming.Usage.Since.Workshop)) %>% 
  arrange(desc(n))

ggplot(data_programming.usage.since.workshop_tally, 
       aes(reorder(Programming.Usage.Since.Workshop, n),
           n)) +
  geom_bar(stat = "identity", fill = "orange") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("") +
  ylab("") +
  ggtitle("Learner's Programming Usage Since Attending a Carpentry Workshop") +
  theme(plot.title = element_text(hjust = 0.5))
  theme_bw(base_size = 14)
```
```{r echo=FALSE}
table(data$Change.In.Confidence)
data_change.in.confidence_tally <- 
  data %>% 
  group_by(Change.In.Confidence) %>% 
  tally() %>% 
  filter(!is.na(Change.In.Confidence)) %>% 
  arrange(desc(n))

ggplot(data_change.in.confidence_tally, 
       aes(reorder(Change.In.Confidence, n),
           n)) +
  geom_bar(stat = "identity", fill = "orange") +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("") +
  ylab("") +
  ggtitle("Learner's Change in Confidence")+
  theme(plot.title = element_text(hjust = 0.5))
  theme_bw(base_size = 14)
```
How have the tools covered in Carpentry workhops helped learners in their research or work?
```{r include=FALSE}
table(data$How.Tools.Learned.Help)
table(data$Column34)
table(data$Column34)
table(data$Column35)
table(data$Column36)
table(data$Column37)
```
```{r echo=FALSE}
career <- matrix(c(245,217,217,203,28,61),ncol=1,byrow=TRUE)
colnames(career) <-("How Have the Tools Covered Helped Your Work?")
rownames(career) <-c("They are improving my overall efficiency.",
                        "They are improving my ability to analyze data.",
                        "They are improving my ability to analyze data.",
                        "They are improving my ability to manage data.",
                        "The tools I learned have not helped me with my work.",
                        "I am not using the tools I learned.")
career <- as.table(career)
career
```

Has participating in a Carpentry workshop contributed to academic writing?
```{r echo=FALSE}
table(data$Contributed.To.Writing)
```
How have learners been involved with the Carpentries since attending a workshop?
```{r include=FALSE}
table(data$Carpentry.Involvement)
table(data$Column45)
table(data$Column46)
table(data$Column47)
table(data$Column48)
table(data$Column49)
table(data$Column50)
table(data$Column51)
```
```{r echo=FALSE}
involvement <- matrix(c(120,18,31,26,6,12,11,18),ncol=1,byrow=TRUE)
colnames(involvement) <-("Involvement Since Attending a Carpentry Workshop")
rownames(involvement) <-c("Subscribed to the newsletter.",
                        "Attended at least one community call.",
                        "Became a workshop helper.",
                        "Became a Carpentry instructor.",
                        "Joined a committee.",
                        "Joined a mentoring group.",
                        "Participated in a Twitter chat.",
                        "Contributed to a Carpentry lesson.")
involvement <- as.table(involvement)
involvement
```
Have learners recommended Carpentry workshops?
```{r echo=FALSE}
table(data$Recommended)
```
### Likert Items

Using the [Likert](http://jason.bryer.org/likert/) package, the following chart is an analysis of learner responses to the statements above. The code chunk is shown once here, and hidden for all subsequent plots.

```{r}
cols_with_Agree <- map_lgl(data, ~`%in%`("Agree", .x))
data_agree <-  data[ , cols_with_Agree]

data_agree <- map_if(data_agree, 
                     is.character, 
                     as.factor)

title <- "Learner Perception of Carpentry Workshops"
data_agree_likert <-  likert(as.data.frame(data_agree))
theme_update(plot.title = element_text(hjust = 0.5))

plot(data_agree_likert) + ggtitle(title) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
# In what country did you attend a Carpentry workshop? 
#map <- get_map(location = 'Europe', zoom = 4)
#ggmap(map)
```
