# Analysis of Carpentry Long-Term Feedback Survey
__Author__: [Kari L. Jordan](https://github.com/kariljordan)
__Published__: April 2017

THIS IS JUST A DRAFT

A [PDF](https://github.com/carpentries/public-survey-info/blob/master/documents/surveys/2017-04-17-carpentry-long-term-feedback-survey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the [public-survey-info](https://github.com/carpentries/public-survey-info) repo on GitHub. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.

```{r echo=FALSE}
# install.packages("ggmap", type = "source")
# install.packages("likert")
# install.packages("purrr")
# install.packages("mapproj")
# install.packages("ggmap")
# install.packages("dplyr")
# install.packages("knitr")
library(dplyr)
library(likert)
library(purrr)
library(ggmap)
library(mapproj)
library(ggplot2)
library(knitr)
update.packages(repos = "https://cloud.r-project.org")
```
```{r echo=FALSE, purl=TRUE}
download.file("https://raw.githubusercontent.com/carpentries/public-survey-info/master/documents/reports/Carpentry-Reports/Long-Term-Feedback-Survey-Report/2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", "2017-04-17-carpentry-long-term-assessment-survey-data-public.csv")

data <- read.csv("2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", na.strings = "")
```
### Learner Demographics

```{r echo=FALSE}
table(data$Country)
```
```{r echo=FALSE}
data_country_tally <- 
  data %>% 
  group_by(Country) %>% 
  tally() %>% 
  filter(!is.na(Country)) %>% 
  arrange(desc(n))
# How do I change the color of just the South Africa bar?
ggplot(data_country_tally, 
       aes(reorder(Country, n),
           n)) +
  geom_col() +
  xlab("") +
  ylab("") +
  coord_flip() +
  ggtitle("")
  theme_bw(base_size = 14)
```
A large portion of Carpentry learners responding to the survey attended a workshop in the United States.
```{r echo=FALSE}
table(data$Position)
```
```{r echo=FALSE}
data_position_tally <- 
  data %>% 
  group_by(Position) %>% 
  tally() %>% 
  filter(!is.na(Position)) %>% 
  arrange(desc(n))

ggplot(data_position_tally, 
       aes(reorder(Position, n),
           n)) +
  geom_col() +
  xlab("") +
  ylab("") +
  ggtitle("Self-Reported Status of Carpentry Learners")
  theme_bw(base_size = 14)
```
Majority graduate students.
```{r echo=FALSE}
table(data$Position.Other)
```
```{r echo=FALSE}
table(data$How.Many.Workshops)
```
Behaviors Adopted Since Attending a Carpentry Workshop
```{r echo=FALSE}
table(data$Behaviors.Adopted)
table(data$Column25)
table(data$Column26)
table(data$Column27)
table(data$Column28)
table(data$Column29)
table(data$Column30)
table(data$Column31)
table(data$Column32)
```

```{r echo=FALSE}
# This is an attempt to make a table of the count of behaviors adopted.
behaviors <- matrix(c(198,74,119,111,260,169,185,119,122),ncol=1,byrow=TRUE)
colnames(behaviors) <-("Behaviors Adopted Since Attending a Carpentry Workshop")
rownames(behaviors) <-c("Improving data management and project organization.",
                        "Developing a data management and analysis plan.",
                        "Using databases, scripts and queries to manage large data sets.",
                        "Transforming step-by-step workflows into scripts or functions.",
                        "Using programming languages like R or Python, or the command line to automate repetitive tasks.",
                        "Reusing code.",
                        "Using version control to manage code.",
                        "Using version control to collaborate online (in public or private repositories).",
                        "Sharing code or data publicly on places like GitHub or FigShare.")
behaviors <- as.table(behaviors)
behaviors
```
Programming Usage before a Carpentry Workshop
```{r echo=FALSE}
table(data$Programming.Usage.Before.Workshop)
```
```{r echo=FALSE}
table(data$Programming.Usage.Since.Workshop)
```
```{r echo=FALSE}
table(data$Change.In.Confidence)
data_change.in.confidence_tally <- 
  data %>% 
  group_by(Change.In.Confidence) %>% 
  tally() %>% 
  filter(!is.na(Change.In.Confidence)) %>% 
  arrange(desc(n))

ggplot(data_change.in.confidence_tally, 
       aes(reorder(Change.In.Confidence, n),
           n)) +
  geom_col() +
  xlab("") +
  ylab("") +
  ggtitle("Learner's Change in Confidence")
  theme_bw(base_size = 14)
```
```{r echo=FALSE}
table(data$How.Tools.Learned.Help)
```
```{r echo=FALSE}
table(data$Column34)
```
```{r echo=FALSE}
table(data$Column34)
```
```{r echo=FALSE}
table(data$Column35)
```
```{r echo=FALSE}
table(data$Column36)
```
```{r echo=FALSE}
table(data$Column37)
```
```{r echo=FALSE}
table(data$Contributed.To.Writing)
```

```{r echo=FALSE}
table(data$Carpentry.Involvement)
```
```{r echo=FALSE}
table(data$Column45)
```
```{r echo=FALSE}
table(data$Column46)
```
```{r echo=FALSE}
table(data$Column47)
```
```{r echo=FALSE}
table(data$Column48)
```
```{r echo=FALSE}
table(data$Column49)
```
```{r echo=FALSE}
table(data$Column50)
```
```{r echo=FALSE}
table(data$Column51)
```

```{r echo=FALSE}
table(data$Recommended)
```
### Likert Items

Using the [Likert](http://jason.bryer.org/likert/) package, the following chart is an analysis of learner responses to the statements above. The code chunk is shown once here, and hidden for all subsequent plots.

```{r}
cols_with_Agree <- map_lgl(data, ~`%in%`("Agree", .x))
data_agree <-  data[ , cols_with_Agree]

data_agree <- map_if(data_agree, 
                     is.character, 
                     as.factor)
# This code worked yesterday to order the likert items and now it's not working.
#for(i in seq_along(data_agree)) {
#                data_agree[[i]] <- factor(data_agree[[i]], levels=order)
#}

title <- "Learner Perception of Carpentry Workshops"
data_agree_likert <-  likert(as.data.frame(data_agree))
theme_update(plot.title = element_text(hjust = 0.5))

plot(data_agree_likert) + ggtitle(title)
```

```{r}
# In what country did you attend a Carpentry workshop? 
#map <- get_map(location = 'Europe', zoom = 4)
#ggmap(map)
```
