# Analysis of Carpentry Long-Term Feedback Survey
__Author__: [Kari L. Jordan](https://github.com/kariljordan)
__Published__: April 2017

THIS IS JUST A DRAFT

A [PDF](https://github.com/carpentries/public-survey-info/blob/master/documents/surveys/2017-04-17-carpentry-long-term-feedback-survey.pdf) of the survey questions, the data used in this analysis, and full R code are located on the [public-survey-info](https://github.com/carpentries/public-survey-info) repo on GitHub. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings.
```{r}
library(likert)
library(purrr)
```
```{r echo=FALSE, purl=TRUE}
download.file("https://raw.githubusercontent.com/carpentries/public-survey-info/master/data/public_data/2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", "2017-04-17-carpentry-long-term-assessment-survey-data-public.csv")

data <- read.csv("2017-04-17-carpentry-long-term-assessment-survey-data-public.csv", na.strings = "")
```
### Learner Demographics

```{r echo=FALSE}
table(data$Country)
```

A large portion of Carpentry learners responding to the survey attended a workshop in the United States.
```{r echo=FALSE}
table(data$Position)
```
Majority graduate students.
```{r echo=FALSE}
table(data$Position.Other)
```
```{r echo=FALSE}
table(data$How.Many.Workshops)
```
```{r echo=FALSE}
table(data$Behaviors.Adopted)
```
```{r echo=FALSE}
table(data$Column25)
```
```{r echo=FALSE}
table(data$Column26)
```
```{r echo=FALSE}
table(data$Column27)
```
```{r echo=FALSE}
table(data$Column28)
```
```{r echo=FALSE}
table(data$Column29)
```
```{r echo=FALSE}
table(data$Column30)
```
```{r echo=FALSE}
table(data$Column31)
```
```{r echo=FALSE}
table(data$Column32)
```
```{r echo=FALSE}
table(data$Programming.Usage.Before.Workshop)
```
```{r echo=FALSE}
table(data$Programming.Usage.Since.Workshop)
```
```{r echo=FALSE}
table(data$Change.In.Confidence)
```
```{r echo=FALSE}
table(data$How.Tools.Learned.Help)
```
```{r echo=FALSE}
table(data$Column34)
```
```{r echo=FALSE}
table(data$Column34)
```
```{r echo=FALSE}
table(data$Column35)
```
```{r echo=FALSE}
table(data$Column36)
```
```{r echo=FALSE}
table(data$Column37)
```
```{r echo=FALSE}
table(data$Contributed.To.Writing)
```
```{r echo=FALSE}
table(data$Column34)
```

```{r echo=FALSE}
table(data$Carpentry.Involvement)
```
```{r echo=FALSE}
table(data$Column45)
```
```{r echo=FALSE}
table(data$Column46)
```
```{r echo=FALSE}
table(data$Column47)
```
```{r echo=FALSE}
table(data$Column48)
```
```{r echo=FALSE}
table(data$Column49)
```
```{r echo=FALSE}
table(data$Column50)
```
```{r echo=FALSE}
table(data$Column51)
```

```{r echo=FALSE}
table(data$Recommended)
```

### Likert Items

Using the [Likert](http://jason.bryer.org/likert/) package, the following chart is an analysis of learner responses to the statements above. The code chunk is shown once here, and hidden for all subsequent plots.
```{r echo=FALSE}
library(likert)
library(purrr)
```
```{r}
cols_with_Agree <- map_lgl(data, ~`%in%`("Agree", .x))
data_agree <-  data[ , cols_with_Agree]

data_agree <- map_if(data_agree, 
                     is.character, 
                     as.factor)
title <- "xxxxx"
data_agree_likert <-  likert(as.data.frame(data_agree))
theme_update(plot.title = element_text(hjust = 0.5))
plot(data_agree_likert) + ggtitle(title)
```

