# Analysis of the Carpentry's Long-Term Feedback Survey
[Kari L. Jordan](https://github.com/kariljordan)  
__June 2017__

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               message = FALSE,
               warning = FALSE)
library(tidyverse)
library(DBI)
library(ggmap)
library(likert)
library(mapproj)
library(RColorBrewer)
library(srvyr)
```

# Introduction
Data and Software Carpentry launched a [long-term assessment survey](https://www.surveymonkey.com/r/carpentrieslongtermassessment) in March 2017. The goal of this survey was to hear from our learners about what has transpired in their work and career since completing a Carpentry workshop. Read our about our long-term assessment strategy on our [blog](http://www.datacarpentry.org/blog/long-term-assessment-strategy/) and see how the community was involved with the development of this survey.

A [PDF](https://github.com/carpentries/public-survey-info/blob/master/documents/surveys/2017-04-17-carpentry-long-term-feedback-survey.pdf) of the survey questions and the data used in this analysis are located in the [long-term feedback survey report](https://github.com/carpentries/public-survey-info/tree/master/documents/reports/Carpentry-Reports/Long-Term-Feedback-Survey-Report) folder on GitHub. We have already received several pull requests from community members interested in this data. Feel free to use the data and [tell us](mailto: kariljordan@carpentries.org) about your findings. 

This analysis includes 476 observations. Not all respondents answered each of the 26 questions.

```{r include=FALSE}
data <- readr::read_csv("https://raw.githubusercontent.com/carpentries/assessment/master/public-survey-info/documents/reports/Carpentry-Reports/Long-Term-Feedback-Survey-Report/2017-04-17-carpentry-long-term-assessment-survey-data-public.csv")
```

```{r include=FALSE}
# Kari's code for highlights in the data
# Use prop.table() to calculate percentages on a single column.

#Change in Confidence
Confidence_Change <- round(prop.table(table(data$`Change-In-Confidence`)) * 100)
Confidence_Change[3]

#Programming Usage Before Workshop
Programming_Usage_Before <- round(prop.table(table(data$`Programming-Usage-Before-Workshop`)) * 100)
Programming_Usage_Before[6]

#Programming Usage Since Workshop
Programming_Usage_Since <- round(prop.table(table(data$`Programming-Usage-Since-Workshop`)) * 100)
Programming_Usage_Since[6]

#Motivated to Seek Knowledge
Motivated_Seek_Knowledge <- round(prop.table(table(data$`Motivated-Seek-Knowledge`))* 100)
Motivated_Seek_Knowledge

#Made Analyses Reproducible
Made_Analyses_Reproducible <- round(prop.table(table(data$`Made-Analyses-Reproducible`))* 100)
Made_Analyses_Reproducible

#Improved Coding Practices
Improved_Coding_Practices <- round(prop.table(table(data$`Improved Coding Practices`))* 100)
Improved_Coding_Practices

#Gained Confidence with Data
Gained_Confidence_Data <- round(prop.table(table(data$`Gained-Confidence-With-Data`))* 100)
Gained_Confidence_Data

#Recommend our Workshops
Recommended <- round(prop.table(table(data$Recommended))* 100)
Recommended
```
# Highlights
Provided below are a few highlights from the data.

+ `r Confidence_Change[3]`% of our respondents reported being more confident in the tools that were covered during their Carpentry workshop compared to before the workshop. 
+ Respondents daily programming usage increased from `r Programming_Usage_Before[6]`% to `r Programming_Usage_Since[6]`% post-Carpentry workshop.
+ `r Motivated_Seek_Knowledge[1] + Motivated_Seek_Knowledge[4]`% of our respondents were motivated to seek more knowledge about the tools they learned in their Carpentry workshop.
+ `r Made_Analyses_Reproducible[1] + Made_Analyses_Reproducible[4]`% of our respondents have made their analyses more reproducible as a result of completing a Carpentry workshop.
+ `r Improved_Coding_Practices[1] + Improved_Coding_Practices[4]`% of our respondents have improved their coding practices as a result of participating in a Carpentry workshop.
+ `r Gained_Confidence_Data[1] + Gained_Confidence_Data[4]`% of our respondents have gained confidence in working with data as a result of completing the workshop.
+ `r Recommended[3]`% of our respondents have recommended our workshops to a friend or colleague.

# Respondent Demographics
Carpentry learners represent a wide range of disciplines ranging from the sciences to engineering. Respondents were asked to indicate their field of research, work, or study by checking all that apply from a list of various disciplines. A breakdown of their responses is provided in the table below. Many of the respondents work in Life Sciences.
```{r}
# Ben's tip to use 'gather' to go from wide to long format
# Responses are in columns 'Field' through 'Column12'
respondent_field <- 
data %>%
  select(`Field`:Column12) %>% 
  gather(col, respondent_field) %>% 
  group_by(respondent_field) %>% 
  tally() %>% 
  filter(!is.na(respondent_field)) %>% 
  arrange(desc(n)) %>%
  rename(`Field` = respondent_field)
kable(respondent_field, format = "markdown", row.names = FALSE, col.names = c("Field", "n"), caption = "Table 1: Breakdown of Respondents by Field")
#The caption isn't showing
```

Respondents were also asked to indicate their position. A breakdown of respondents by position is provided below.

```{r}
# Code for Status of Respondents
position = c("Undergraduate Student", "Graduate Student", "Postdoc", "Faculty", "Industry", "Academic Research Staff", "Other Academic Staff", "Other (please specify)")
position = factor(position)

data$Position = factor(data$Position, levels = position)

data_position_tally <- 
  data %>% 
  group_by(Position) %>% 
  tally() %>% 
  filter(!is.na(Position)) 

# Use the line below to include a table

#kable(data_position_tally, format = "markdown", row.names = FALSE, col.names = c("Position", "n"))

ggplot(data_position_tally, 
       aes(Position, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Status") +
  ylab("% Respondents") +
  ggtitle("Majority of Respondents were Graduate Students") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

```{r include=FALSE}
# Use code below for in-line text.
# Graduate_Student<- data_position_tally[data_position_tally$Position == 'Graduate Student', ]$n
Graduate_Student <- round(prop.table(table(data$Position))* 100)
Graduate_Student
```

Carpentry workshops are open to individuals from all backgrounds and fields. Attendees vary from students (undergraduate and graduate) and faculty to staff and persons working in industry. `r Graduate_Student[2]`% of our respondents were graduate students. 

Provided is a breakdown of our respondents by the Country where they attended a Carpentry workshop.
 
```{r}
# Plot includes Ben's tip to add a percent column to the data_country_tally data frame 
# before it goes into the ggplot() function. Then you should be able to use reorder on that column name in the ggplot() function
data_country_tally <-
data %>%
  group_by(Country) %>%
  tally() %>%
  mutate(perc = round(100 * (n/sum(n)), 1)) %>% # add the % col
  filter(!is.na(Country)) %>%
  arrange(desc(n))

ggplot(data_country_tally,
       aes(reorder(Country, perc),
           perc)) +
  geom_bar(stat = "identity", fill = "orange") +
  theme_classic() +
  xlab("") +
  ylab("Percentage of all participants") +
  coord_flip() +
  ggtitle("Carpentry Workshop Respondents by Country") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw(base_size = 14)

#Use code below for in-line text.
USA <- data_country_tally[data_country_tally$Country == 'USA', ]$n
Canada <- data_country_tally[data_country_tally$Country == 'Canada', ]$n
UK <- data_country_tally[data_country_tally$Country == 'UK', ]$n
Australia <- data_country_tally[data_country_tally$Country == 'Australia', ]$n

# kable(data_country_tally, format = "markdown", row.names = FALSE, col.names = c("Country", "# Respondents"))

# Naupaka's tip for changing colors of one bar on the plot 
# country_colors <- rep("orange", length(levels(data$Country)))
# country_colors[levels(data$Country) == "South Africa"] <- "blue"

# ggplot(data_country_tally, 
#       aes(reorder(Country, n), 
#           n)) + 
#  geom_bar(aes(fill = Country),
#           stat = "summary", 
#           fun.y = "mean") + 
#           theme_classic() +
#           xlab("") +
#           ylab("") +
#           coord_flip() +
#  ggtitle("Carpentry Workshop Respondents by Country") +
#  theme(plot.title = element_text(hjust = 0.5)) +
#  theme_bw(base_size = 14) +
#  scale_fill_manual(values = country_colors, guide = FALSE)
```

```{r include=FALSE}
# Use code below for in-line text.
# Country<- data_country_tally[data_country_tally$Country == 'Country', ]$n
Country <- round(prop.table(table(data$Country))* 100)
Country
```

A large portion of Carpentry learners responding to the survey attended a workshop in the United States (`r Country[22]`%), followed by Canada (`r Country[3]`%) the UK (`r Country[21]`%), and Australia (`r Country[1]`%).

```{r include=FALSE}
# If interested in seeing the open-ended responses for Position: Other, run this code.
data_position_other_tally <- 
  data %>% 
  group_by(`Position-Other`) %>% 
  tally() %>% 
  filter(!is.na(`Position-Other`))
kable(data_position_other_tally, format = "markdown", row.names = FALSE, col.names = c("Position", "# Respondents"))
```

The Carpentries continue to endeavor to improve our workshop content and operations. We were therefore interested in knowing how many workshops respondents attended, and how long it has been since respondents completed a workshop. If there are spikes in the trends of our data, knowing when respondents completed a workshop will help us pinpoint whether or not our workshop operations, changes in policies, etc., are related to learner responses in the data.

```{r include=FALSE}
#Code for in-line text
#How long ago did respondents attend a workshop?
How_Long_Ago <- round(prop.table(table(data$`How-Long-Ago`))* 100)
How_Long_Ago

#How many workshops have respondents attended?
How_Many_Workshops <- round(prop.table(table(data$`How-Many-Workshops`))* 100)
How_Many_Workshops
```
`r How_Long_Ago[3]`% of respondents participated in a Carpentry workshop more than one year ago, and `r How_Many_Workshops[1]`% of respondents have attended only one Carpentry workshop. 

```{r include=FALSE}
Carpentry_Involvement <- 
data %>%
  select(`Carpentry-Involvement`:Column51) %>% 
  gather(col, Carpentry_Involvement) %>% 
  group_by(Carpentry_Involvement) %>% 
  tally() %>% 
  filter(!is.na(Carpentry_Involvement)) %>% 
  arrange(desc(n)) %>% 
  rename(`Involvement Since Attending a Carpentry Workshop` = Carpentry_Involvement)

Carpentry_Involvement[1,2]
```

The majority of respondents attending a workshop more than one year ago speaks to their level of involvement with the Carpentries (`r Carpentry_Involvement[1,2]` people responded having subscribed to the Carpentries newsletter). It can be difficult, in survey research, to collect responses from participants a year after you interacted with them. It is great to see that learners are still receptive to our e-mail communication and have taken time to complete our survey.

```{r}
 data_howlong_tally <- 
  data %>% 
  group_by(`How-Long-Ago`) %>% 
  tally() %>% 
  filter(!is.na(`How-Long-Ago`)) 

# Use the code below to include a table of how long ago respondents attended a workshop
# kable(data_howlong_tally, format = "markdown", row.names = FALSE, col.names = c("Time", "n"), caption = "How Recently Did Respondents Complete a Workshop?")

ggplot(data_howlong_tally, 
       aes(`How-Long-Ago`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("Time Since Attending Carpentry Workshop") +
  ylab("% Respondents") +
  ggtitle("Majority Attended Workshop Over a Year Ago") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```
```{r}
data_workshops_tally <- 
  data %>% 
  group_by(`How-Many-Workshops`) %>% 
  tally() %>% 
  filter(!is.na(`How-Many-Workshops`))

# Use the code below to include a table of the number of workshops respondents attended
#kable(data_workshops_tally, format = "markdown", row.names = FALSE, col.names = c("# Wrkshps", "n"), caption = "Number of Workshops Attended")

ggplot(data_workshops_tally, 
       aes(`How-Many-Workshops`, y = 100 * (n/sum(n)),
           n)) +
  geom_bar(stat = "identity", fill="orange") +
  geom_text(aes(label=n), size= 4) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
  theme_classic() +
  xlab("# Workshops Attended") +
  ylab("% Respondents") +
  ggtitle("Majority Attended One Carpentry Workshop") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14)
```

### Workshop Content
Data Carpentry's [lessons](http://www.datacarpentry.org/lessons/) include data organization in Spreadsheets, data cleaning with OpenRefine, data management with SQL, and data analysis and visualization in R and Python.

Software Carpentry's [lessons](https://software-carpentry.org) include the Unix Shell, version control with Git and Mercurial, programming with Python, R, and MATLAB, databases with SQL, and Automation and Make. Provided below is a breakdown of the tools respondents identified being covered in the workshop they attended.
```{r}
# Responses are in columns 'Content' through 'Column22'
# Ben's tip to use 'gather' to go from wide to long format
workshop_tools <- 
 data %>%
 select(`Content`:Column22) %>% 
 gather(col, workshop_tools) %>% 
 group_by(workshop_tools) %>% 
 tally() %>% 
 filter(!is.na(workshop_tools)) %>% 
 arrange(desc(n)) %>%
 rename(`Content` = workshop_tools)

# Use the line below to provide a table of the tools covered. 
# Respondents were asked to check all that apply.
# kable(workshop_tools, caption = "Tools Covered") 

# Ben's tip to use in-line text
# This code produces results to use in the text of the report
Git <- workshop_tools[workshop_tools$Content == 'Git', ]$n
Python <- workshop_tools[workshop_tools$Content == 'Python', ]$n
Unix_Shell <- workshop_tools[workshop_tools$Content == 'Unix Shell', ]$n
R <- workshop_tools[workshop_tools$Content == 'R', ]$n
SQL <- workshop_tools[workshop_tools$Content == 'SQL', ]$n
OpenRefine <- workshop_tools[workshop_tools$Content == 'OpenRefine', ]$n
Spreadsheets <- workshop_tools[workshop_tools$Content == 'Spreadsheets', ]$n
Cloud_Computing <- workshop_tools[workshop_tools$Content == 'Cloud Computing', ]$n
MATLAB <-  workshop_tools[workshop_tools$Content == 'MATLAB', ]$n
Mercurial <-  workshop_tools[workshop_tools$Content == 'Mercurial', ]$n
```

The table below provides insight into the combination of tools that was covered the most frequently in our respondent's workshops. Nearly 20% of respondents learned Git (n = `r Git`), Python (n = `r Python`), and the Unix Shell (n = `r Unix_Shell`) during their workshop. On the low end were Spreadsheets (n = `r Spreadsheets`), Cloud Computing (n = `r Cloud_Computing`), MATLAB (n = `r MATLAB`), and Mercurial (n = `r Mercurial`). 

```{r}
# The code segment below from Ben Marwick will show the most combinations of tools 
# covered in our workshops.
tools_cols <- 
data %>%
  select(Content:Column22)

list_of_tools_per_person <- list()
for(i in seq_len(nrow(tools_cols))) {
  ii <- quo(i)
  
  list_of_tools_per_person[[i]] <- 
  tools_cols %>% 
    slice(!!ii) %>% 
          c(., recursive=TRUE) %>%
          unname %>% 
    na.omit() %>% 
    as.vector()
}

# The code segment below from Ben Marwick will get the tally of combinations of tools and produce a table.
tool_combs <- 
purrr::map_chr(list_of_tools_per_person,
               ~paste0(.x, collapse = " "))

tool_combs_df <- 
tool_combs %>% 
  as_data_frame() %>% 
  group_by(value) %>% 
  tally() %>% 
  mutate(`%` = round(n / sum(n) * 100, 1)) %>% 
  arrange(desc(n)) %>% 
  filter(value != "")

# Top combinations as entered by respondants
colnames <- c("Tools", "n", "%")
kable(tool_combs_df[1:10, ], row.names = NA, col.names = colnames, caption = "Combination of Tools Covered")
```

Taking a look at which combinations of tools covered stood out in the data, we see from the matrix below that Git was frequently covered alongside Python, R, and/or the Unix Shell. Additionally, SQL was often covered with Git and/or the Unix Shell. OpenRefine, Spreadsheets, and Cloud Computing being on the low end is an indicator that the majority of our respondents attended a Software Carpentry workshop. This makes sense as Software Carpentry has offered more workshops than Data Carpentry.

```{r}
# The code segment below from Ben Marwick will give a matrix of the combinations of tools used.
m <- as.matrix(tools_cols) 
# The unique values in the matrix
vals <- sort(unique(as.vector(m)))

# Rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# Count the co-occurences of each value (diagonal is total number of rows with that value)
tool_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(tool_co_occurences, format = "markdown", row.names = TRUE, caption = "Table 3: Matrix of Common Tools Covered")
# The caption isn't showing.
```

```{r include=FALSE}
# Data for in-line text on programming usage
Programming_Usage_Before <- round(prop.table(table(data$`Programming-Usage-Before-Workshop`)) * 100)
Programming_Usage_Before

#Programming Usage Since Workshop
Programming_Usage_Since <- round(prop.table(table(data$`Programming-Usage-Since-Workshop`)) * 100)
Programming_Usage_Since
```
### Programming Usage Pre- and Post Workshop
A goal for this assessment is to understand respondents' programming usage before attending a Carpentry workshop compared to after. Our hope is that the workshop they attended influenced their usage of the programming tools they learned.

`r Programming_Usage_Before[2]`% of the learners who responded to our survey had not been using the tools covered in their Carpentry workshop before completing. This decreased to `r Programming_Usage_Since[2]`% post-Carpentry workshop.

The plot below is a comparison of respondents' usage of the tools covered in their workshop before completing the workshop versus after.

```{r include=FALSE}
# The code below can be used to get a table and plot of the number of respondents for programming usage
# pre workshop
# Naupaka's tip so pre- and post-responses match
data_paired_plot <- data
levels(data$`Programming-Usage-Before-Workshop`)[2] <- "I have not been using tools like these."
 
# Programming Usage Pre-Carpentry Workshop [Absolute Plot]
programming = c("I had not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
programming = factor(programming)
 
# Do not include the next line when you take the comments out.
# data$Programming.Usage.Before.Workshop = factor(data$Programming.Usage.Before.Workshop, levels = programming)
 
  data_usage_tally <- 
   data %>% 
   group_by(`Programming-Usage-Before-Workshop`) %>% 
   tally() %>% 
   filter(!is.na(`Programming-Usage-Before-Workshop`)) # %>%
   #rename(`Programming Usage Before Workshop` = `Programming-Usage-Before-Workshop`) #Ben's tip to change column name
 
  kable(data_usage_tally, caption = "Prior Programming of Respondents")
 
  ggplot(data_usage_tally, 
        aes(`Programming-Usage-Before-Workshop`, n)) +
   geom_bar(stat = "identity", fill="orange") +
   geom_text(aes(label=n), size= 4) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Programming Usage") +
   ylab("# Respondents") +
   ggtitle("Programming Usage Pre-Workshop Varies") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_classic(base_size = 14)
```
```{r include=FALSE}
# The code below is for pre-workshop programming usage reported as a percentage.
# Programming Pre-Carpentry Workshop [Percentage Plot]
 data %>%
  select(`Programming-Usage-Before-Workshop`) %>%
   group_by(`Programming-Usage-Before-Workshop`) %>%
   tally() %>%
   filter(!is.na(`Programming-Usage-Before-Workshop`)) %>%
   mutate(`Programming-Usage-Before-Workshop` = factor(`Programming-Usage-Before-Workshop`, levels = programming)) %>%
   ggplot(aes(x = `Programming-Usage-Before-Workshop`, y = 100 * (n/sum(n)))) +
     geom_bar(stat = "identity", position = "dodge", fill = "orange") +
     geom_text(aes(label=n), size= 4) +
     scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                          width = 10,
                                                          simplify = FALSE),
                                                  paste,
                                                  collapse = "\n")) +
     theme_classic() +
     xlab("Programming Usage") +
     ylab("% respondents") +
     ggtitle("Programming Usage Pre-Workshop Varies") +
     theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
```    

```{r include=FALSE}
# The code below is for post-workshop programming usage (count)
# Programming Usage Post-Carpentry Workshop [Absolute Plot]
  programming = c("I have not been using tools like these.", "Less than once per year.", "Several times per year.", "Monthly.", "Weekly.", "Daily.")
  programming = factor(programming)
 
 data$`Programming-Usage-Since-Workshop` = factor(data$`Programming-Usage-Since-Workshop`, levels = programming)
 
  data_usage_tally <- 
   data %>% 
   group_by(`Programming-Usage-Since-Workshop`) %>% 
   tally() %>% 
   filter(!is.na(`Programming-Usage-Since-Workshop`)) 
 
 kable(data_usage_tally)
 
  ggplot(data_usage_tally, 
        aes(`Programming-Usage-Since-Workshop`, n)) +
   geom_bar(stat = "identity", fill="orange") +
   geom_text(aes(label=n), size= 4) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Programming Usage") +
   ylab("# Respondents") +
   ggtitle("Respondents' Programming Usage Increased") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_classic(base_size = 14)
```
```{r include=FALSE}
# The code below is for post-workshop programming usage as a percent
#Programming Usage Post-Carpentry Workshop [Percentage Plot]
data %>%
select(`Programming-Usage-Since-Workshop`) %>%
group_by(`Programming-Usage-Since-Workshop`) %>%
tally() %>%
filter(!is.na(`Programming-Usage-Since-Workshop`)) %>%
mutate(`Programming-Usage-Since-Workshop` = factor(`Programming-Usage-Since-Workshop`, levels = programming)) %>%
ggplot(aes(x = `Programming-Usage-Since-Workshop`, y = 100 * (n/sum(n)))) +
geom_bar(stat = "identity", position = "dodge", fill = "orange", na.rm = TRUE ) +
geom_text(aes(label=n), size= 4) + # Adds count to top of bar
scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("") +
    ylab("% respondents") +
    ggtitle("Respondents' Programming Usage Increased") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
```

```{r}
# The code below is for Pre/Post plots of programming usage
# It includes tips from Ben and Naupaka 
# Make the unique values the same
data$`Programming-Usage-Before-Workshop` <- 
  gsub("I had not been using tools like these.",
       "I have not been using tools like these.", 
       data$`Programming-Usage-Before-Workshop`)

data$`Programming-Usage-Before-Workshop` <- 
  factor(data$`Programming-Usage-Before-Workshop`, 
         levels = programming)

pre_and_post_usage <- 
data %>%
  select(`Programming-Usage-Before-Workshop`, 
          `Programming-Usage-Since-Workshop`) %>%
  gather() %>%
  group_by(key, value) %>%
  tally() %>%
  mutate( perc = 100 * (n/sum(n))) %>%
  filter(!is.na(key),
         !is.na(value)) 

  ggplot(pre_and_post_usage, 
         aes(x = factor(value, 
                        levels = programming), 
             y = perc, 
             fill = key)) +
    geom_bar(stat = "identity", 
             position = "dodge") +
    geom_text(aes(label=n), size= 4) +
    scale_x_discrete(labels = function(x) lapply(strwrap(x,
                                                         width = 10,
                                                         simplify = FALSE),
                                                 paste,
                                                 collapse = "\n")) +
    theme_classic() +
    xlab("Programming Usage") +
    ylab("% Respondents") +
    scale_fill_discrete(name = "",
                        labels = c("Before Workshop", "After Workshop")) +
    ggtitle("Respondents' Programming Usage Increased") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme_classic(base_size = 14)
  
# Get some % change values to use in the text
delta_pre_have_not_been_using <- 
  pre_and_post_usage %>% 
  filter(grepl("have", value)) %>% 
  spread(key, value) 

delta_pre_have_not_been_using <- 
round(delta_pre_have_not_been_using$perc[2] - 
  delta_pre_have_not_been_using$perc[1], 1)

delta_pre_daily_using <- 
  pre_and_post_usage %>% 
  filter(grepl("Daily", value)) %>% 
  spread(key, value) 

delta_pre_daily_using <- 
round(delta_pre_daily_using$perc[2] - 
  delta_pre_daily_using$perc[1], 1)
```

The most compelling change in responses was a decline in the percentage of respondents that 'have not been using these tools' (`r -delta_pre_have_not_been_using`%), and an increase in the percentage of those who now use the tools on daily basis (`r delta_pre_daily_using`%).
```{r}
# The code below from Ben provides a chi-square plot of the pre/post residuals
pre_and_post_test <- 
pre_and_post_usage %>% 
  select(-perc) %>% 
  spread(value, n) %>% 
  ungroup()  

# chi-sq test
pre_and_post_test_result <- 
  chisq.test(pre_and_post_test[ , !names(pre_and_post_test) == 'key'])

# standardised residuals
stdres <- data.frame(t(pre_and_post_test_result$stdres))
names(stdres) <- pre_and_post_test$key
stdres$freq <- row.names(stdres)

# just show post-workshop
stdres <- stdres[, c(2,3)]

names(stdres) <- rev(c("Frequency", "Residual"))

# large positive residuals means there were more xxx than the hypothesis of independence predicts. Where are our large +ve residuals?

# Contribution in percentage (%)
# The contribution (in %) of a given cell to the total Chi-square score is calculated as follows:
contrib <- 100 * pre_and_post_test_result$residuals^2 / pre_and_post_test_result$statistic
# scale 0 to 1 to use as alpha
range0to1 <- function(x){(x-min(x))/(max(x)-min(x))}
# reorder to match order of programming factor
contrib_0_to_1 <- as.vector(range0to1(contrib))[c(3,5,9,7,11,1)]

# colour +ve and -ve values
# http://stackoverflow.com/a/12910865/1036500
stdres$sign = ifelse(stdres$Residual >= 0, 
                          "positive", 
                          "negative")

# get the categories in a sensible order
ggplot(stdres,
       aes(factor(Frequency, 
                  levels = programming),
           Residual,
           fill = sign)) +
  geom_col(position = "dodge", 
           aes(alpha = contrib_0_to_1)) +
  xlab("") +
  ylab("Chi-square standardized residuals of\npost-workshop frequencies") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse = "\n")) +
  scale_fill_manual(name = "",
                      values = c("negative" = "red", 
                                 "positive" = "blue"),
                      labels = c("Fewer respondents than \nexpected assuming no effect", 
                                 "More respondents than \nexpected assuming no effect")) +
  ggtitle("Workshops result in respondents \nprogramming significantly more often") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic(base_size = 14) +
  scale_alpha_continuous("Contribution to \nchi-square value") +
   guides(fill=guide_legend(
                 keywidth = 0.1,
                 keyheight = 0.4,
                 default.unit = "inch")
      )
```

A chi-square test indicates that there is a significant difference in the frequencies of the pre- and post-workshop responses about #programming use. The chi-squared standardized residuals for the post-workshop values show that significantly more respondents do #programming daily after the workshop than expected if the workshop had no effect. Similarly, significantly fewer respondents program #less than once per year after the workshop.

# Workshop Impact
Respondents were asked to reflect on ways in which completing a Carpentry workshop may have impacted them by rating their level of agreement (1-Strongly disagree to 5-Strongly agree) with the following statements: 

+ I have used skills I learned at the workshop to advance my career.    
+ I have been motivated to seek more knowledge about the tools I learned at the workshop.   
+ I have made my analyses more reproducible as a result of completing the workshop.   
+ I have received professional recognition for my work as a result of using the tools I learned at the workshop.   
+ I have improved my coding practices as a result of completing the workshop.   
+ My research productivity has improved as a result of completing the workshop.   
+ I have gained confidence in working with data as a result of completing the workshop.   

The following plot was created using the [Likert](http://jason.bryer.org/likert/) package, and presents an analysis of learner responses to the statements above. We see an overwhelmingly positive indication that respondents left their workshop feeling motivated to seek more knowledge and having gained confidence in working with data. Additionally, more than 80% of respondents improved their coding practices, made their analyses reproducible, improved their research productivity, and believe the skills they learned helped them advance their career. Forty percent of our respondents have received professional recognition as a result of using the tools they learned in a Carpentry workshop.

```{r echo=FALSE}
# Jonah's fix to include the correct levels. Variable was renamed to 'levels' #because 'order' is the name of a function in R.
# I am still not sure if this plot is 100% correct -KLJ

cols_with_Agree <- map_lgl(data, ~`%in%`("Agree", .x))
data_agree <-  data[ , cols_with_Agree]

levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")

# Beth's tip to both order the factors based on levels and unify the factors
 factorfunction <- function(mydata, factlevel){
  factor(mydata, 
         levels=factlevel, 
         ordered = TRUE)
    fct_unify(mydata, 
              levels=factlevel)}
# End tip 
 
data_agree_likert <- likert(data.frame(lapply(data_agree, factor, levels, ordered=TRUE)))
# Elizabeth's tip on factors
 #for(i in seq_along(data_agree)) {
                #data_agree[[i]] <- factor(data_agree[[i]], levels=order)}

#print(levels(data_agree))
 
title <- "Workshops are Welcoming & Useful"
 theme_update(plot.title = element_text(hjust = 0.5))
plot(data_agree_likert) + ggtitle(title) 

#print(class(data_agree))
 data_agree <- map_if(data_agree,
                     is.character,
                     as.factor)
```

### Behaviors Adopted
```{r}
# Code for behaviors adopted
# Responses are in columns 'Behaviors-Adopted' through 'Column32'
# Use 'gather' to go from wide to long format
Behaviors <- 
data %>%
  select(`Behaviors-Adopted`:Column32) %>% 
  gather(col, Behaviors) %>% 
  group_by(Behaviors) %>% 
  tally() %>% 
  filter(!is.na(Behaviors)) %>% 
  arrange(desc(n))

# how many rate either of these?
#- data management and project organization practices : Behaviors-Adopted
#- used programming languages for automation : Column28
#- used version control to manage code : Column30

Behaviors_Adopted <-   select(data, `Behaviors-Adopted`:Column32)
Behaviors_Adopted <- data.frame(apply(Behaviors_Adopted, 2, function(x) ifelse(x == "NA", 0, 1)))
relevant_cols <- c("Behaviors.Adopted", "Column28", "Column30")
Behaviors_Adopted <- Behaviors_Adopted[, names(Behaviors_Adopted) %in% relevant_cols]
number_that_adopted_any_of_those_three <- sum(ifelse(rowSums(Behaviors_Adopted, na.rm = TRUE) >= 1, 1, 0))
```

We asked respondents to identify the behaviors they adopted as a result of completing a Carpentry workshop. We are happy to report that more than half of the respondents who answered this question (n= `r number_that_adopted_any_of_those_three`) have improved their data management and project organization practices, used programming languages for automation, and used version control to manage code. Additionally, respondents are __more confident__ now in using the tools than before they completed a Carpentry workshop.
```{r}
kable(Behaviors, format = "markdown", row.names = FALSE, caption = "Table 4: Behaviors Adopted by Respondents")
```
The matrix below shows a count of the highest combinations of behaviors adopted. It was interesting to see that 102 respondents who reported improving their data management and project organization also use version control to manage code.
```{r}
# Code for matrix of behaviors (thanks Ben for the tip!)
# Combinations of behaviors adopted for individuals
behaviors_cols <- 
data %>%
  select(`Behaviors-Adopted`:Column32)

list_of_behaviors_per_person <- list()
for(i in seq_len(nrow(behaviors_cols))) {
  ii <- quo(i)
  
  list_of_behaviors_per_person[[i]] <- 
  behaviors_cols %>% 
    slice(!!ii) %>% 
          c(., recursive=TRUE) %>%
          unname %>% 
    na.omit() %>% 
    as.vector()
}

# Tally of combinations of behaviors adopted 
behaviors_combs <- 
purrr::map_chr(list_of_behaviors_per_person,
               ~paste0(.x, collapse = " "))

behaviors_combs_df <- 
behaviors_combs %>% 
  as_data_frame() %>% 
  group_by(value) %>% 
  tally() %>% 
  mutate(`%` = round(n / sum(n) * 100, 1)) %>% 
  arrange(desc(n)) %>% 
  filter(value != "")

# Matrix 
m <- as.matrix(behaviors_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
behaviors_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(behaviors_co_occurences, row.names = TRUE, caption = "Matrix of Common Behaviors Adopted Post-Workshop")
```


### Change in Confidence 
Our goal is for learners to leave a workshop having an increase in their confidence to use the tools they learned. More than 75% of the respondents are more confident now in using the tools they learned than they were before attending a Carpentry workshop.
```{r}
# Code for change in confidence
confidence = c("I'm less confident now.", "I'm equally confident now.", "I'm more confident now.")
confidence = factor(confidence)

data$`Change-In-Confidence` = factor(data$`Change-In-Confidence`, levels = confidence)

data_change.in.confidence_tally <- 
  data %>% 
  group_by(`Change-In-Confidence`) %>% 
  tally() %>% 
  filter(!is.na(`Change-In-Confidence`))

# Use the code below for a table of the data.
# kable(data_change.in.confidence_tally, format = "markdown", row.names = FALSE, col.names = c("Change in Confidence", "%"))

ggplot(data_change.in.confidence_tally, 
       aes(`Change-In-Confidence`, y = 100 * (n/sum(n)),
           n)) +
   geom_bar(stat = "identity", fill = "orange") +
   geom_text(aes(label=n), size= 4) +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) +
   theme_classic() +
   xlab("Change in Confidence") +
   ylab("% Respondents") +
   ggtitle("Respondents are More Confident Post-Workshop") +
   theme(plot.title = element_text(hjust = 0.5)) +
   theme_bw(base_size = 14)
```

### Usage of Tools for Research and/or Work
We identified specific outcomes that learners may experience after completing a Carpentry workshop that are directly related to their research and/or work. Respondents have identified that the tools they learned improved their overall efficiency, and ability to manage and analyze data.  

```{r}
# Data are in columns 'How.Tools.Learned.Help' through 'Column37'
# Ben's tip to use 'gather' to go from wide to long format
# I want to present this data as a percentage as opposed to count. Tips?

# How many responded to either of these?
# They are improving my overall efficienct : How.Tools.Learned.Helped
# They are improving my ability to analyze data. : Column34
# They are improving my ability to manage data. : Column35

Tools_Learned <-   select(data, `How-Tools-Learned-Help`:Column35)
Tools_Learned <- data.frame(apply(Tools_Learned, 2, function(x) ifelse(x == "NA", 0, 1)))
relevant_cols <- c("How.Tools.Learned.Help", "Column34", "Column35")
Tools_Learned <- Tools_Learned[, names(Tools_Learned) %in% 
                                 relevant_cols]
number_that_tools_helped <- sum(ifelse(rowSums(Tools_Learned, na.rm = TRUE) >= 1, 1, 0))

how_help <- 
data %>%
  select(`How-Tools-Learned-Help`:Column37) %>% 
  gather(col, how_help) %>% 
  group_by(how_help) %>% 
  tally() %>% 
  filter(!is.na(how_help)) %>% 
  arrange(desc(n)) %>% 
  rename(`How-Tools-Learned-Help` = how_help)

# Data to use in-line
no_help <- table(data$`Column36`)
no_use <- table(data$`Column37`)

tools_helped <- 
data %>%
  select(`How-Tools-Learned-Help`:Column37) %>% 
  gather(col, tools_helped) %>% 
  group_by(tools_helped) %>% 
  tally() %>% 
  filter(!is.na(tools_helped)) %>% 
  arrange(desc(n)) %>%
  rename(`How Tools Covered Have Helped` = tools_helped)

kable(tools_helped, format = "markdown", row.names = FALSE, caption = "Table 5: Self-Reported Perception of How Tools Help Respondents")
```

Only `r no_help` respondents said the tools they learned have not helped them, and `r no_use` respondents have not been using the tools that were covered in their workshop.

### Contributions to Academic Writing
Another possible outcome of attending a Carpentry workshop is that the tools learned may contribute to academic writing (i.e. grant proposal, journal article). 
```{r}
# Code chunk for contributions to academic writing
writing = c("No.", "Not sure.", "Yes.")
writing = factor(writing)

data$Contributed.To.Writing = factor(data$`Contributed-To-Writing`, levels = writing)

Contributed_Writing <- round(prop.table(table(data$`Contributed-To-Writing`)) * 100)

 data_writing_tally <- 
   data %>% 
   group_by(Contributed.To.Writing) %>% 
   tally() %>% 
   filter(!is.na(Contributed.To.Writing)) %>% 
   arrange(desc(n))

# Use the code below for a table of the count of responses.
#kable(data_writing_tally, format = "markdown", row.names = FALSE, col.names = c("Response?", "n"), caption = "Table 6: Respondents Perception of How Tools Contributed to Academic Writing")

kable(Contributed_Writing, format = "markdown", row.names = FALSE, col.names = c("Response", "n"), caption = "Table 6: Respondents Perception of How Tools Contributed to Academic Writing")
```

`r Contributed_Writing[1]` of our respondents said that the tools they learned contributed to their academic writing.

### Continuous Learning
```{r}
# Code chunk for continuous learning 
Learning_Activities <- 
data %>%
  select(`Activities`:Column57) %>% 
  gather(col, Learning_Activities) %>% 
  group_by(Learning_Activities) %>% 
  tally() %>% 
  filter(!is.na(Learning_Activities)) %>% 
  arrange(desc(n)) %>% 
  rename(`Continuous Learning Post-Workshop` = Learning_Activities)

# To use code for Carpentry self-guided material in-line
#carpentry_self_guided <- Learning_Activities %>% filter(`Learning_Activities` == "Used self-guided Carpentry lesson material.") %>% 
#  collect() %>% 
#  .[["n"]]
carpentry_self_guided <- table(data$Column56)
```
One of our primary outcomes is that learners continue on in their learning once they've completed a workshop. This can take many forms including participating in short-courses (in-person and online) and using self-guided material. We asked respondents to tell us which learning activities they've participated in since completing a Carpentry workshop. The majority of respondents have used non-Carpentry self-guided material, though `r carpentry_self_guided` responded having used Carpentry self-guided material. Additionally, we see participation in meetups and in-person short courses, as outlined in the table below.
```{r}
# Code chunk for table of continuous learning activities
kable(Learning_Activities, format = "markdown", row.names = FALSE, col.names = c("Continuous Learning", "n"), caption = "Table 7: Respondents Self-Reported Continuous Learning Activities")
```
The matrix below provides a breakdown of the combination of continuous learning activities respondents participated in. For example, 35 respondents have used both Carpentry and non-Carpentry self-guided material since attending a workshop.
```{r}
# Code for matrix of continuous learning (thanks Ben for the tip!)
# Combinations of continuous learning for individual
learning_cols <- 
data %>%
  select(`Activities`:Column57)

list_of_learning_per_person <- list()
for(i in seq_len(nrow(learning_cols))) {
  ii <- quo(i)
  
  list_of_learning_per_person[[i]] <- 
  learning_cols %>% 
    slice(!!ii) %>% 
          c(., recursive=TRUE) %>%
          unname %>% 
    na.omit() %>% 
    as.vector()
}

# Tally of combinations of continuous learning 
learning_combs <- 
purrr::map_chr(list_of_learning_per_person,
               ~paste0(.x, collapse = " "))

learning_combs_df <- 
learning_combs %>% 
  as_data_frame() %>% 
  group_by(value) %>% 
  tally() %>% 
  mutate(`%` = round(n / sum(n) * 100, 1)) %>% 
  arrange(desc(n)) %>% 
  filter(value != "")

# Matrix 
m <- as.matrix(learning_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
learning_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(learning_co_occurences, row.names = TRUE, caption = "Matrix of Common Continuous Learning Activities")
```

## Involvement in the Carpentries 
Another outcome of attending a Carpentry workshop is that learners become involved with Software and/or Data Carpentry by way of joining a mentoring group, becoming a workshop helper, or even becoming an instructor. The table provided below shows how respondents have been involved with the Carpentries since completing a workshop. Respondents were asked to check all that apply.

```{r}
# Code chunk for involvement with the Carpentries
# Data in columns 'Carpentry.Involvement through Column51
Carpentry_Involvement <- 
data %>%
  select(`Carpentry-Involvement`:Column51) %>% 
  gather(col, Carpentry_Involvement) %>% 
  group_by(Carpentry_Involvement) %>% 
  tally() %>% 
  filter(!is.na(Carpentry_Involvement)) %>% 
  arrange(desc(n)) %>% 
  rename(`Involvement Post-Workshop` = Carpentry_Involvement)

kable(Carpentry_Involvement, row.names = FALSE, caption = "Respondents Self-Reported Inolvement in the Carpentries Post-Workshop")
```

The matrix below is a look at the frequent combinations of involvement. For example, 16 of the respondents who became Carpentry instructors have attended at least one community call.
```{r}
# Code for matrix of involvement (thanks Ben for the tip!)
# Combinations of tools for individual
involvement_cols <- 
data %>%
  select(`Carpentry-Involvement`:Column51)

list_of_involvement_per_person <- list()
for(i in seq_len(nrow(involvement_cols))) {
  ii <- quo(i)
  
  list_of_involvement_per_person[[i]] <- 
  involvement_cols %>% 
    slice(!!ii) %>% 
          c(., recursive=TRUE) %>%
          unname %>% 
    na.omit() %>% 
    as.vector()
}

# Tally of combinations of tools 
involvement_combs <- 
purrr::map_chr(list_of_involvement_per_person,
               ~paste0(.x, collapse = " "))

involvement_combs_df <- 
involvement_combs %>% 
  as_data_frame() %>% 
  group_by(value) %>% 
  tally() %>% 
  mutate(`%` = round(n / sum(n) * 100, 1)) %>% 
  arrange(desc(n)) %>% 
  filter(value != "")

# Matrix tool-by-tool

m <- as.matrix(involvement_cols) 
# the unique values in the matrix
vals <- sort(unique(as.vector(m)))

# rearrange the data so that each value is a column
bigm <- t(apply(m, 1, function(row) match(vals, row, nomatch=0)))
colnames(bigm) <- vals

# count the co-occurences of each value (diagonal is total number of rows with that value)
involvement_co_occurences  <- as.data.frame(crossprod(bigm>0))
kable(involvement_co_occurences, row.names = TRUE, caption = "Matrix of Common Involvement")
```

```{r include=FALSE}
# Code chunk for whether respondents recommended a workshop
data_recommended_tally <-
  data %>% 
  group_by(Recommended) %>% 
  tally() %>% 
  filter(!is.na(Recommended)) %>% 
  arrange(desc(n))

# Code chunk for in-line text
said_yes <- data_recommended_tally[data_recommended_tally$Recommended == "Yes.", ]$n

# Table for responses of recommendations
# kable(data_recommended_tally)
```

```{r include=FALSE}
# Code chunk for likelihood of recommmending a Carpentry workshop
data_likelyrecommend_tally <-
  data %>% 
  group_by(`Likely-To-Recommend`) %>% 
  tally() %>% 
  filter(!is.na(`Likely-To-Recommend`)) %>% 
  arrange(desc(n))

# Table for responses
# kable(data_likelyrecommend_tally)
```

# Summary
We value our learners because when they have successful experiences in our workshops, they share their experience with others. We asked respondents if they had already recommended our workshop, and `r Recommended[3]`% said yes!

This initial look at how Carpentry workshops have impacted learners long-term has been extremely insightful. In general, our workshops are helping learners improve their efficiency with managing and analyzing data. Learners are taking advantage of online resources to improve their skills, and becoming involved with our community.

We will take another look at this data to compare responses of learners having taken a workshop more than a year ago versus those having taken a workshop 0 to 6 months ago and 6 months to 1 year ago. Additionally, every 6 months we will collect data using this survey from new learners to see how they're doing.


